### 2017-07-31 paper.tex
Initial import.

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

% Document-specific packages
\usepackage{epigraph}

% Document-specific definitions
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA} 
%\acmYear{1997}
%\copyrightyear{2016}

%\acmPrice{15.00}

\begin{document}
\title{Network Structure, Efficiency, and Performance in WikiProjects}

\author{Edward L. Platt}
\affiliation{%
  \institution{University of Michigan}
  \city{Ann Arbor} 
  \state{Michigan} 
}
\email{elplatt@umich.edu}

% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}
TODO
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle

\section{Introduction}
\epigraph
{The problem with Wikipedia is that it only works in practice. In theory, it can never work.}
{Miikka Ryokas\cite{latest_cohen_2007}}

Wikipedia successful decentralized.

Efficiency Performance

Coeditor network

NK Simulations

Contributions

\section{Related Work}
TODO

\section{Methods}

\subsection{Data}

Our analysis combines multiple datasets from the English-language Wikipedia.
For information about edit history, we used a publicly-available dataset containing
metadata about all edits between TODO.
To get the rating history of each article,
we wrote a script to scrape the daily logs produced by WPBot1.0 for each WikiProject
between TODO.
Finally, we used a publicly-available log of page events (including rename events)
to reconstruct the unique identifier for each article title mentioned in the rating history logs.

\subsection{Quantifying Performance and Efficiency}

To model the relationship between performance, efficiency, and network structure,
we must have a way to quantify performance and efficiency.
We define these quantities on a per-WikiProject basis to enable comparisons across different
projects.
Our definitions are inpsired by work modeling collective problem-solving as an optimization
problem \cite{}.
The effieincy quantifies how quikly a solution is reached,
while the performance quantifies how good the eventual solution is.

For a WikiProject, efficiency quantifies how quickly project participants can improve the
assessed quality of an article.
Quality assessments are made through consensus of the project participants themselves,
so different projects can have different standards and practices for assessing article quality.
So the efficiency is not a measure of how quickly some objective measure of quality improves,
but rather of how quickly the project participants can reach consensus on the improvments that
need to be made and make those improvements.
Because our definition relies on assessment transitions, we define efficiency variables for
each of the project-level quality assessments: A, B, and C.
If $T(W,G)$ is the set of transitions in project $W$ from below grade $G$ to grade $G$ (or higher),
then we quantify the efficiency $E(W,G)$ as:
\beq
E(W,G) &=& \sum_{t \in W(P,G)} \left[ \frac{r(t)}{g(t)} \right]^{-1},
\eeq
where $r(t)$ is the number of revisions since the previous grade transition,
and $g(t)$ is the number of grade levels crossed by transition $t$.
The $g(t)$ term is added because an assessments often raise article quality by several
grades, in which case the revisions are divided evenly between all grade levels achieved.
It is also worth noting that we measure efficiency in terms of revisions made,
rather than time passed.
We focus on revisions because the amount of work done on an article varies widely from day to day.

For performance, we wish to quantify how good articles tend to be when they reach a stable state.
Measuring performance is difficult for several reasons:
there is no objective meaasure of article quality avaialbe,
and articles are always changing, making it difficult to know which articles should be considered
complete or stable.
We use an extremely simple performance measure that gives surprisingly consistent results.
In addition to per-project quality assessment, articles can be given ``featured article'' or
``good article'' status.
The criteria for these statuses are consistent across all of Wikipedia,
and any editor can participate in the discussion and decision to award good or featured
status.
In other words, the good and featured statuses are more objective than per-project assessments.
Our performance measure $P(W)$ is just the percentage of articles in project $W$ which have reached
good or featured status:
\beq
P(W) &=& \frac{f(W) + g(W)}{n(W)},
\eeq
where $f(W)$ and $g(W)$ are the numbered of featured and good articles respectively,
and $n(W)$ is the total number of articles
\subsection{Coeditor Networks}

Construction

Degree

Path length

Min-cut

\subsection{Model}

OLS

\subsection{Numerical Simulation}

TODO

\section{Results}
TODO

\section{Discussion}
TODO

\section{Conclusion}
TODO

\section{Acknowledgements}
TODO

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

\end{document}

### 2017-08-02 paper.tex
More outline and citations.

@@
 {The problem with Wikipedia is that it only works in practice. In theory, it can never work.}
-{Miikka Ryokas\cite{latest_cohen_2007}}
+{Miikka Ryokas \cite{cohen_latest_2007}}
 
@@
 
-\section{Methods}
+\section{Empirical Methods}
 
@@
 where $f(W)$ and $g(W)$ are the numbered of featured and good articles respectively,
-and $n(W)$ is the total number of articles
+and $n(W)$ is the total number of articles.
+
 \subsection{Coeditor Networks}
@@
 
-\subsection{Numerical Simulation}
+\subsection{Empirical Results}
 
@@
 
-\section{Results}
+\section{Numerical Simulation}
+
+Intro
+
+\subsection{Learning Strategies}
+
+Individual learning
+
+Social learning and iteration
+
+Best neighbor
+
+Conformity
+
+Consensus
+
+\subsection{Network family}
+
+TODO
+
+Base network
+
+Duplication and rewiring
+
+\subsection{Simulation results}
+
 TODO

### 2017-08-02 paper.tex
Add content, switch to article documentclass.

@@
-\documentclass[sigconf]{acmart}
+% ACM
+%\documentclass[sigconf]{acmart}
+
+% Manuscript
+\documentclass[10pt,twocolumn]{article}
+\usepackage{natbib}
 
@@
 
-\author{Edward L. Platt}
-\affiliation{%
-  \institution{University of Michigan}
-  \city{Ann Arbor} 
-  \state{Michigan} 
-}
-\email{elplatt@umich.edu}
+% ACM
+%\author{Edward L. Platt}
+%\affiliation{%
+%  \institution{University of Michigan}
+%  \city{Ann Arbor} 
+%  \state{Michigan} 
+%}
+%\email{elplatt@umich.edu}
+
+% Manuscript
+\author{Edward L. Platt \\ University of Michigan \\ Ann Arbor, Michigan \\ elplatt@umich.edu}
 
@@
 %\renewcommand{\shortauthors}{B. Trovato et al.}
+
+% ACM
+% The code below should be generated by the tool at
+% http://dl.acm.org/ccs.cfm
+% Please copy and paste the code instead of the example below. 
+%
+%\begin{CCSXML}
+%\end{CCSXML}
+
+% ACM
+%\ccsdesc[500]{Computer systems organization~Embedded systems}
+%\ccsdesc[300]{Computer systems organization~Redundancy}
+%\ccsdesc{Computer systems organization~Robotics}
+%\ccsdesc[100]{Networks~Network reliability}
+
+% ACM
+% \keywords{collaboration, peer production, wikipedia}
+
+\maketitle
 
@@
 
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>  
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-
-\keywords{ACM proceedings, \LaTeX, text tagging}
-
-\maketitle
-
 \section{Introduction}
@@
 {The problem with Wikipedia is that it only works in practice. In theory, it can never work.}
-{Miikka Ryokas \cite{cohen_latest_2007}}
+{Miikka Ryokas \cite{cohen_latest_2007} }
 
@@
 
-\section{Related Work}
+\section{Background and Related Work}
+
 TODO
@@
 
-\subsection{Quantifying Performance and Efficiency}
+\subsection{Efficiency and Performance}
 
@@
 
-Construction
+For each WikiProject, we compare the efficiency and performance measures to the structural
+properties of its coeditor network.
+The {\em coeditor network} of a WikiProject consists of nodes representing editors.
+Two editors are connected when they have both edited the same article or talk page.
+The edges are directed, with the direction representing the direction of
+{\em plausible information flow};
+an edge from editor A to editor B exists if A edited an article and then B edited the same article at
+a later time.
+Edges can exist in both directions e.g., if an article was edited first by A, then by B, and again by A.
+For simplicity, we assign all edges unit weight.
+We focus on three structural properties: degree, characteristic path length, and min-cut.
 
-Degree
+The node degree distribution is the simplest structural property we analyze for WikiProject
+coeditor networks.
+The in-degree (out-degree) of a node is the number of edges to (from) that node.
+Taking the average of either in-degree or out-degree gives the same value:
+the {\em mean degree} of the network.
+In our context, the mean degree represents how many others a given editor has collaborated with.
+We also consider the {\em skewness} of the in-degree and out-degree distributions.
+A large positive degree skewness value for a WikiProject coeditor network
+implies that a small number of editors have a very large number of collaborators,
+while a small positive value implies that the editors having the most collaborators
+don't have too many more than a typical editor.
 
@@
 
-\bibliographystyle{ACM-Reference-Format}
+% ACM
+%\bibliographystyle{ACM-Reference-Format}
+
+% Manuscript
+\bibliographystyle{acm}
+
 \bibliography{paper}

### 2017-08-05 paper.tex
More content.

@@
 while a small positive value implies that the editors having the most collaborators
-don't have too many more than a typical editor.
+don't have many more than a typical editor.
 
-Path length
+We also calculate the characteristic path length for each WikiProject coeditor network.
+The {\em distance} from editor A to editor B is the length of the shortest path from A to B.
+The {\em characteristic path length} is the mean distance between all editor pairs.
+If no path exists between two editors, we exclude that pair from the mean.
+For brevity, we will simply refer to this quantity as the {\em path length}.
+The path length represents how quickly information can move through the network.
+Networks with longer paths require more interactions for information to propagate through
+the network.
 
-Min-cut
+Our final network measure quantifies the connectivy of a project's coeditor network using
+min-cut size.
+The minimum $st$-cut between nodes $s$ and $t$ is the set of edges that must be removed in order that
+no path exists from $s$ to $t$.
+The minimum cut (min-cut) of a graph is the smallest minimum $st$-cut over all node pairs $st$. 
+The size of the graph min-cut quantifies the connectivity of a graph,
+but only incorporates information about edges lying on paths crossing the min-cut.
+Instead, we use the mean size of all minimum $st$-cuts, which we refer to as the
+{\em mean min-cut}.
+This measure quantifies the number of redundant paths information can take through the network.
+Networks with higher redundancy are more resilient to errors on one path \cite{}
+and allow innovation to propagate through complex contagion,
+in which innovations are only adopted after multiple exposures thorugh different sources
+\cite{}.
 
@@
 
-OLS
+OLS, controls
 
@@
 \section{Acknowledgements}
-TODO
+Daniel Romero.
+Danielle Livneh, Karthik Ramanathan.
+Yan Chen, Tanya Rosenblat.
+MIT Center for Civic Media.
+Cooperation Working Group at the Harvard Berkman-Klein Center.
+School of Information.
 

### 2017-08-06 paper.tex
Add regression table.

@@
 \newcommand{\eeq}{\end{eqnarray}}
+\newcommand{\+}{\phantom{-}}
 
@@
 
-OLS, controls
+We model performance and efficiency in WikiProjects using ordinary least-squares linear regression.
+Each WikiProject is taken as a single observation.
+The models include each project's coeditor network properties as independent variables.
+We also include several project-level variables to control for confounding factors.
+Some variables are log-transformed to reduce heteroscedasticity.
 
-\subsection{Empirical Results}
+Our models are summarized in Table \ref{tab:model}.
+Mean min-cut was found to be highly correlated with degree (see Figure \ref{fig:degree-mincut}),
+so we exclude min-cut to prevent collinearity.
+The high correlation between mean degree and min-cut implies that in most cases
+the minimum $st$-cut is simply the either set of edges from $s$ or the set of edges to $t$.
+The rarity of non-trivial min-cuts suggests that WikiProject coeditor networks have very few central
+bottlenecks and are thus highly decentralized.
 
+\begin{figure}
+\caption{
 TODO
+\label{fig:degree-mincut}
+}
+\end{figure}
+
+\begin{table*}
+\begin{tabular}{llc}
+ & Performance$^\dagger$ & Performance$^\dagger$ \\
+\hline
+Mean Degree$^\dagger$          &  -0.8$^{***}$  & \\
+In-Degree Skewness$^\dagger$   &  -0.6$^{***}$  & \\
+Out-Degree Skewness$^\dagger$  &               & \\
+Mean Path$^\dagger$            &  -0.36$^{***}$ & \\
+C-Eff$^\dagger$                &  -0.08$^{**}$  & \\
+Connectivity                   & \+0.02         & \\
+Mean Editors/Article$^\dagger$ & \+0.4$^{***}$  & \\
+Article Count$^\dagger$        &  -0.3          & \\
+Editor Count$^\dagger$         & \+0.7$^{*}$    & \\
+Revision Count$^\dagger$       & \+0.4          & \\
+First Assessment               & \+0.03         & \\
+Mean Article Age               &  -0.04         & \\
+\hline
+DoF                            & 1278           & \\
+R$^2$(adj)                       & 0.37           & \\
+\end{tabular}
+\caption{
+\label{tab:model}
+}
+\end{table*}
 

### 2017-08-07 paper.tex
More regression results.

@@
 bottlenecks and are thus highly decentralized.
+In-degree and out-degree skewness were also highly correlated, so each dependent variable was modelled twice:
+once with in-degree skewness and once with out-degree skewness.
 
@@
 \begin{table*}
-\begin{tabular}{llc}
- & Performance$^\dagger$ & Performance$^\dagger$ \\
+\small
+\begin{tabular}{lllllllll}
+                               & Perf$^\dagger$ & Perf$^\dagger$ & A-Eff$^\dagger$ & A-Eff$^\dagger$ & B-Eff$^\dagger$ & B-Eff$^\dagger$ & C-Eff$^\dagger$ & C-Eff$^\dagger$ \\
 \hline
-Mean Degree$^\dagger$          &  -0.8$^{***}$  & \\
-In-Degree Skewness$^\dagger$   &  -0.6$^{***}$  & \\
-Out-Degree Skewness$^\dagger$  &               & \\
-Mean Path$^\dagger$            &  -0.36$^{***}$ & \\
-C-Eff$^\dagger$                &  -0.08$^{**}$  & \\
-Connectivity                   & \+0.02         & \\
-Mean Editors/Article$^\dagger$ & \+0.4$^{***}$  & \\
-Article Count$^\dagger$        &  -0.3          & \\
-Editor Count$^\dagger$         & \+0.7$^{*}$    & \\
-Revision Count$^\dagger$       & \+0.4          & \\
-First Assessment               & \+0.03         & \\
-Mean Article Age               &  -0.04         & \\
+Mean degree$^\dagger$          &  -0.8$^{***}$  &  -0.8$^{***}$
+                               &  -0.6$^{**}$   &  -0.8$^{***}$
+                               &  &
+                               &  & \\
+In-degree skewness$^\dagger$   &  -0.6$^{***}$  & \+ ---      
+                               &  -0.4$^{**}$   & \+ ---      
+                               &  & \+ ---      
+                               &  & \+ ---      \\
+Out-degree skewness$^\dagger$  &  \+ ---        & -0.5$^{***}$  
+                               &  \+ ---        & -0.6$^{***}$
+                               &  \+ ---        &
+                               &  \+ ---        & \\
+Mean path$^\dagger$            &  -0.36$^{***}$ & -0.36$^{***}$ 
+                               &  -0.03         & -0.10
+                               &  &
+                               &  & \\
+C-eff$^\dagger$                &  -0.08$^{**}$  & -0.08$^{**}$  
+                               &  \+ ---        & \+ ---      
+                               &  \+ ---        & \+ ---      
+                               &  \+ ---        & \+ --- \\
+Connectivity                   & \+0.02         & \+0.02        
+                               &  \+0.08        & \+0.09
+                               &  &
+                               &  & \\
+Mean editors/article$^\dagger$ & \+0.4$^{***}$  & \+0.4$^{***}$ 
+                               & \+0.2          & \+0.3
+                               &  &
+                               &  & \\
+Article count$^\dagger$        &  -0.3          & -0.3          
+                               & \+0.6${^*}$    & \+0.7${^*}$ 
+                               &  &
+                               &  & \\
+Editor count$^\dagger$         & \+0.7$^{*}$    & \+0.5         
+                               & \+0.7$^{*}$    & \+1.0$^{**}$
+                               &  &
+                               &  & \\
+Revision count$^\dagger$       & \+0.4          & \+0.4         
+                               &  -0.8$^{**}$   & -0.9$^{**}$
+                               &  &
+                               &  & \\
+First assessment               & \+0.03         & \+0.06        
+                               & \+0.09$^{*}$   & \+0.10$^{**}$
+                               &  &
+                               &  & \\
+Mean article age               &  -0.04         & -0.03         
+                               &  -0.04         & -0.04
+                               &  &
+                               &  & \\
 \hline
-DoF                            & 1278           & \\
-R$^2$(adj)                       & 0.37           & \\
+DoF                            & 1278           & 1278          
+                               & 1048           & 1048
+                               &  &
+                               &  & \\
+R$^2_{adj}$                    & 0.37           & 0.37          
+                               & 0.15           & 0.16
+                               &  &
+                               &  & \\
 \end{tabular}

### 2017-08-07 paper.tex
Add regression data.

--- 2017-08-06 paper.tex
@@
 \begin{table*}
-\begin{tabular}{llc}
- & Performance$^\dagger$ & Performance$^\dagger$ \\
+\small
+\begin{tabular}{lllllllll}
+                               & Perf$^\dagger$ & Perf$^\dagger$ & A-Eff$^\dagger$ & A-Eff$^\dagger$ & B-Eff$^\dagger$ & B-Eff$^\dagger$ & C-Eff$^\dagger$ & C-Eff$^\dagger$ \\
 \hline
-Mean Degree$^\dagger$          &  -0.8$^{***}$  & \\
-In-Degree Skewness$^\dagger$   &  -0.6$^{***}$  & \\
-Out-Degree Skewness$^\dagger$  &               & \\
-Mean Path$^\dagger$            &  -0.36$^{***}$ & \\
-C-Eff$^\dagger$                &  -0.08$^{**}$  & \\
-Connectivity                   & \+0.02         & \\
-Mean Editors/Article$^\dagger$ & \+0.4$^{***}$  & \\
-Article Count$^\dagger$        &  -0.3          & \\
-Editor Count$^\dagger$         & \+0.7$^{*}$    & \\
-Revision Count$^\dagger$       & \+0.4          & \\
-First Assessment               & \+0.03         & \\
-Mean Article Age               &  -0.04         & \\
+Mean degree$^\dagger$          &  -0.84$^{***}$  &  -0.78$^{***}$
+                               &  -0.61$^{**}$   &  -0.84$^{***}$
+                               &  -0.50$^{***}$  &  -0.61$^{***}$
+                               &  -0.34$^{**}$   & \\
+In-degree skewness$^\dagger$   &  -0.58$^{***}$  & \+ ---      
+                               &  -0.43$^{**}$   & \+ ---      
+                               &  -0.19          & \+ ---      
+                               &  -0.1           & \+ ---      \\
+Out-degree skewness$^\dagger$  &  \+ ---         &  -0.48$^{***}$  
+                               &  \+ ---         &  -0.57$^{***}$
+                               &  \+ ---         &  -0.26$^{*}
+                               &  \+ ---         & \\
+Mean path$^\dagger$            &  -0.357$^{***}$ &  -0.356$^{***}$ 
+                               &  -0.026         &  -0.096
+                               &  -0.020         &  -0.045
+                               &  -0.092$^{**}$  & \\
+C-eff$^\dagger$                &  -0.083$^{**}$  & -0.085$^{**}$  
+                               &  \+ ---         & \+ ---      
+                               &  \+ ---         & \+ ---      
+                               &  \+ ---         & \+ --- \\
+Connectivity                   & \+0.018         & \+0.016        
+                               & \+0.081         & \+0.088
+                               & \+0.126$^{***}  & \+0.142$^{***}$
+                               & \+0.080$^{**}   & \\
+Mean editors/article$^\dagger$ & \+0.37$^{***}$  & \+0.40$^{***}$ 
+                               & \+0.22          & \+0.27
+                               & \+0.20          & \+0.22$^{*}
+                               & \+0.076         & \\
+Article count$^\dagger$        &  -0.32          & -0.27          
+                               & \+0.63${^*}$    & \+0.70${^*}$ 
+                               & \+0.76$^{**}$   & \+0.78$^{**}$
+                               & \+0.67$^{***}$  & \\
+Editor count$^\dagger$         & \+0.68$^{*}$    & \+0.48         
+                               & \+0.74$^{*}$    & \+0.97$^{**}$
+                               & \+0.60$^{*}     & \+0.72$^{**}$
+                               & \+0.52$^{*}     & \\
+Revision count$^\dagger$       & \+0.37          & \+0.39         
+                               &  -0.84$^{**}$   & -0.88$^{**}$
+                               &  -1.05$^{***}$  & -1.05$^{***}$
+                               &  -1.00$^{***}$  & \\
+First assessment               & \+0.028         & \+0.058        
+                               & \+0.086$^{*}$   & \+0.101$^{**}$
+                               & \+0.309$^{***}  & \+0.321$^{***}$
+                               & \+0.456$^{***}$ & \\
+Mean article age               &  -0.040         & -0.029         
+                               &  -0.049         & -0.037
+                               &  -0.019         & -0.014
+                               &  -0.046$^{*}$   & \\
 \hline
-DoF                            & 1278           & \\
-R$^2$(adj)                       & 0.37           & \\
+DoF                            & 1278            & 1278          
+                               & 1048            & 1048
+                               & 1371            & 1371
+                               & 1540            & \\
+R$^2_{adj}$                    & 0.37            & 0.37          
+                               & 0.15            & 0.16
+                               & 0.30            & 0.30
+                               & 0.43            & \\
 \end{tabular}

### 2017-08-07 paper.tex
Finish adding regression output.

--- 2017-08-06 paper.tex
@@
 \begin{table*}
-\begin{tabular}{llc}
- & Performance$^\dagger$ & Performance$^\dagger$ \\
+\small
+\begin{tabular}{lllllllll}
+                               & Perf$^\dagger$ & Perf$^\dagger$ & A-Eff$^\dagger$ & A-Eff$^\dagger$ & B-Eff$^\dagger$ & B-Eff$^\dagger$ & C-Eff$^\dagger$ & C-Eff$^\dagger$ \\
 \hline
-Mean Degree$^\dagger$          &  -0.8$^{***}$  & \\
-In-Degree Skewness$^\dagger$   &  -0.6$^{***}$  & \\
-Out-Degree Skewness$^\dagger$  &               & \\
-Mean Path$^\dagger$            &  -0.36$^{***}$ & \\
-C-Eff$^\dagger$                &  -0.08$^{**}$  & \\
-Connectivity                   & \+0.02         & \\
-Mean Editors/Article$^\dagger$ & \+0.4$^{***}$  & \\
-Article Count$^\dagger$        &  -0.3          & \\
-Editor Count$^\dagger$         & \+0.7$^{*}$    & \\
-Revision Count$^\dagger$       & \+0.4          & \\
-First Assessment               & \+0.03         & \\
-Mean Article Age               &  -0.04         & \\
+Mean degree$^\dagger$          &  -0.84$^{***}$  &  -0.78$^{***}$
+                               &  -0.61$^{**}$   &  -0.84$^{***}$
+                               &  -0.50$^{***}$  &  -0.61$^{***}$
+                               &  -0.34$^{**}$   &  -0.31$^{*}$ \\
+In-degree skewness$^\dagger$   &  -0.58$^{***}$  & \+ ---      
+                               &  -0.43$^{**}$   & \+ ---      
+                               &  -0.19          & \+ ---      
+                               &  -0.1           & \+ ---      \\
+Out-degree skewness$^\dagger$  &  \+ ---         &  -0.48$^{***}$  
+                               &  \+ ---         &  -0.57$^{***}$
+                               &  \+ ---         &  -0.26$^{*}$
+                               &  \+ ---         &  -0.066 \\
+Mean path$^\dagger$            &  -0.357$^{***}$ &  -0.356$^{***}$ 
+                               &  -0.026         &  -0.096
+                               &  -0.020         &  -0.045
+                               &  -0.092$^{**}$  &  -0.086 \\
+C-eff$^\dagger$                &  -0.083$^{**}$  & -0.085$^{**}$  
+                               &  \+ ---         & \+ ---      
+                               &  \+ ---         & \+ ---      
+                               &  \+ ---         & \+ --- \\
+Connectivity                   & \+0.018         & \+0.016        
+                               & \+0.081         & \+0.088
+                               & \+0.126$^{***}$ & \+0.142$^{***}$
+                               & \+0.080$^{**}$  & \+0.081$^{**}$ \\
+Mean editors/article$^\dagger$ & \+0.37$^{***}$  & \+0.40$^{***}$ 
+                               & \+0.22          & \+0.27
+                               & \+0.20          & \+0.22$^{*}$
+                               & \+0.076         & \+0.075 \\
+Article count$^\dagger$        &  -0.32          & -0.27          
+                               & \+0.63${^*}$    & \+0.70${^*}$ 
+                               & \+0.76$^{**}$   & \+0.78$^{**}$
+                               & \+0.67$^{***}$  & \+0.67$^{***}$ \\
+Editor count$^\dagger$         & \+0.68$^{*}$    & \+0.48         
+                               & \+0.74$^{*}$    & \+0.97$^{**}$
+                               & \+0.60$^{*}$    & \+0.72$^{**}$
+                               & \+0.52$^{*}$    & \+0.46$^{*}$ \\
+Revision count$^\dagger$       & \+0.37          & \+0.39         
+                               &  -0.84$^{**}$   & -0.88$^{**}$
+                               &  -1.05$^{***}$  & -1.05$^{***}$
+                               &  -1.00$^{***}$  & -1.00$^{***}$ \\
+First assessment               & \+0.028         & \+0.058        
+                               & \+0.086$^{*}$   & \+0.101$^{**}$
+                               & \+0.309$^{***}$ & \+0.321$^{***}$
+                               & \+0.456$^{***}$ & \+0.460$^{***}$ \\
+Mean article age               &  -0.040         & -0.029         
+                               &  -0.049         & -0.037
+                               &  -0.019         & -0.014
+                               &  -0.046$^{*}$   & -0.045$^{*}$ \\
 \hline
-DoF                            & 1278           & \\
-R$^2$(adj)                       & 0.37           & \\
+DoF                            & 1278            & 1278          
+                               & 1048            & 1048
+                               & 1371            & 1371
+                               & 1540            & 1540 \\
+R$^2_{adj}$                    & 0.37            & 0.37          
+                               & 0.15            & 0.16
+                               & 0.30            & 0.30
+                               & 0.43            & 0.43 \\
 \end{tabular}

### 2017-08-07 paper.tex
Acknowledgements.

--- 2017-08-07 paper.tex
@@
 \documentclass[10pt,twocolumn]{article}
-\usepackage{natbib}
+\usepackage[numbers]{natbib}
 
@@
 \usepackage{epigraph}
+\usepackage[flushleft]{threeparttable}
 
@@
 problem \cite{}.
-The effieincy quantifies how quikly a solution is reached,
+The efficiency quantifies how quikly a solution is reached,
 while the performance quantifies how good the eventual solution is.
@@
 \hline
-Mean degree$^\dagger$          &  -0.8$^{***}$  &  -0.8$^{***}$
-                               &  -0.6$^{**}$   &  -0.8$^{***}$
-                               &  &
-                               &  & \\
-In-degree skewness$^\dagger$   &  -0.6$^{***}$  & \+ ---      
-                               &  -0.4$^{**}$   & \+ ---      
-                               &  & \+ ---      
-                               &  & \+ ---      \\
-Out-degree skewness$^\dagger$  &  \+ ---        & -0.5$^{***}$  
-                               &  \+ ---        & -0.6$^{***}$
-                               &  \+ ---        &
-                               &  \+ ---        & \\
-Mean path$^\dagger$            &  -0.36$^{***}$ & -0.36$^{***}$ 
-                               &  -0.03         & -0.10
-                               &  &
-                               &  & \\
-C-eff$^\dagger$                &  -0.08$^{**}$  & -0.08$^{**}$  
+Mean degree$^\dagger$          &  -0.84$^{***}$  &  -0.78$^{***}$
+                               &  -0.61$^{**}$   &  -0.84$^{***}$
+                               &  -0.50$^{***}$  &  -0.61$^{***}$
+                               &  -0.34$^{**}$   &  -0.31$^{*}$ \\
+In-degree skewness$^\dagger$   &  -0.58$^{***}$  & \+ ---      
+                               &  -0.43$^{**}$   & \+ ---      
+                               &  -0.19          & \+ ---      
+                               &  -0.1           & \+ ---      \\
+Out-degree skewness$^\dagger$  &  \+ ---         &  -0.48$^{***}$  
+                               &  \+ ---         &  -0.57$^{***}$
+                               &  \+ ---         &  -0.26$^{*}$
+                               &  \+ ---         &  -0.066 \\
+Mean path$^\dagger$            &  -0.357$^{***}$ &  -0.356$^{***}$ 
+                               &  -0.026         &  -0.096
+                               &  -0.020         &  -0.045
+                               &  -0.092$^{**}$  &  -0.086 \\
+C-eff$^\dagger$                &  -0.083$^{**}$  & -0.085$^{**}$  
                                &  \+ ---         & \+ ---      
@@
                                &  \+ ---         & \+ --- \\
-Connectivity                   & \+0.02         & \+0.02        
-                               &  \+0.08        & \+0.09
-                               &  &
-                               &  & \\
-Mean editors/article$^\dagger$ & \+0.4$^{***}$  & \+0.4$^{***}$ 
-                               & \+0.2          & \+0.3
-                               &  &
-                               &  & \\
-Article count$^\dagger$        &  -0.3          & -0.3          
-                               & \+0.6${^*}$    & \+0.7${^*}$ 
-                               &  &
-                               &  & \\
-Editor count$^\dagger$         & \+0.7$^{*}$    & \+0.5         
-                               & \+0.7$^{*}$    & \+1.0$^{**}$
-                               &  &
-                               &  & \\
-Revision count$^\dagger$       & \+0.4          & \+0.4         
-                               &  -0.8$^{**}$   & -0.9$^{**}$
-                               &  &
-                               &  & \\
-First assessment               & \+0.03         & \+0.06        
-                               & \+0.09$^{*}$   & \+0.10$^{**}$
-                               &  &
-                               &  & \\
-Mean article age               &  -0.04         & -0.03         
-                               &  -0.04         & -0.04
-                               &  &
-                               &  & \\
+Connectivity                   & \+0.018         & \+0.016        
+                               & \+0.081         & \+0.088
+                               & \+0.126$^{***}$ & \+0.142$^{***}$
+                               & \+0.080$^{**}$  & \+0.081$^{**}$ \\
+Mean editors/article$^\dagger$ & \+0.37$^{***}$  & \+0.40$^{***}$ 
+                               & \+0.22          & \+0.27
+                               & \+0.20          & \+0.22$^{*}$
+                               & \+0.076         & \+0.075 \\
+Article count$^\dagger$        &  -0.32          & -0.27          
+                               & \+0.63${^*}$    & \+0.70${^*}$ 
+                               & \+0.76$^{**}$   & \+0.78$^{**}$
+                               & \+0.67$^{***}$  & \+0.67$^{***}$ \\
+Editor count$^\dagger$         & \+0.68$^{*}$    & \+0.48         
+                               & \+0.74$^{*}$    & \+0.97$^{**}$
+                               & \+0.60$^{*}$    & \+0.72$^{**}$
+                               & \+0.52$^{*}$    & \+0.46$^{*}$ \\
+Revision count$^\dagger$       & \+0.37          & \+0.39         
+                               &  -0.84$^{**}$   & -0.88$^{**}$
+                               &  -1.05$^{***}$  & -1.05$^{***}$
+                               &  -1.00$^{***}$  & -1.00$^{***}$ \\
+First assessment               & \+0.028         & \+0.058        
+                               & \+0.086$^{*}$   & \+0.101$^{**}$
+                               & \+0.309$^{***}$ & \+0.321$^{***}$
+                               & \+0.456$^{***}$ & \+0.460$^{***}$ \\
+Mean article age               &  -0.040         & -0.029         
+                               &  -0.049         & -0.037
+                               &  -0.019         & -0.014
+                               &  -0.046$^{*}$   & -0.045$^{*}$ \\
 \hline
@@
                                & 1048            & 1048
-                               &  &
-                               &  & \\
+                               & 1371            & 1371
+                               & 1540            & 1540 \\
 R$^2_{adj}$                    & 0.37            & 0.37          
                                & 0.15            & 0.16
-                               &  &
-                               &  & \\
+                               & 0.30            & 0.30
+                               & 0.43            & 0.43 \\
 \end{tabular}
-\caption{
+\caption{Standardized coefficients for OLS models.
 \label{tab:model}
 }
+\begin{tablenotes}
+\item $\dagger$ Log-transformed. * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
+\end{tablenotes}
 \end{table*}
@@
 \section{Acknowledgements}
-Daniel Romero.
-Danielle Livneh, Karthik Ramanathan.
-Yan Chen, Tanya Rosenblat.
-MIT Center for Civic Media.
-Cooperation Working Group at the Harvard Berkman-Klein Center.
-School of Information.
+I would like to thank Daniel Romero for valuable guidance and feedback;
+Danielle Livneh and Karthik Ramanathan for help collecting the data sets;
+Yan Chen and Tanya Rosenblat for feedback on the methodology;
+and the atendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
+the Berkman-Klein Center's Cooperation Working Group for helpful feedback on
+preliminary results.
+This research was funded by the University of Michigan School of Information.
 

### 2017-08-07 paper.tex
Add references.

@@
 To get the rating history of each article,
-we wrote a script to scrape the daily logs produced by WPBot1.0 for each WikiProject
+we wrote a script to scrape the daily logs produced by WP 1.0 Bot for each WikiProject
 between TODO.
@@
 Our definitions are inpsired by work modeling collective problem-solving as an optimization
-problem \cite{}.
+problem \cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, grim_scientific_2013, barkoczi_social_2016}.
 The efficiency quantifies how quikly a solution is reached,

### 2017-08-07 paper.tex
Add references and start interpreting regression.

@@
 Networks with longer paths require more interactions for information to propagate through
-the network.
+the network,
+which has been shown to reduce efficiency in some settings
+\cite{mason_propagation_2008,barkoczi_social_2016}.
 
@@
 This measure quantifies the number of redundant paths information can take through the network.
-Networks with higher redundancy are more resilient to errors on one path \cite{}
-and allow innovation to propagate through complex contagion,
+Networks with higher redundancy are more resilient to errors on one path \cite{albert_error_2000}
+and allow innovations to propagate through complex contagion,
 in which innovations are only adopted after multiple exposures thorugh different sources
-\cite{}.
+\cite{centola_complex_2007}.
+
+The mean path and min-cut network measures are computationally intensive,
+requiring distance and minimum $st$-cut calculations for each all node pairs.
+For larger projects, these calculations are impractical.
+When coeditor networks were large, we employed sampling to determine mean path length and mean
+min-cut.
+For mean path length, source nodes were sampled, and path length was calculated to all destination nodes
+from each of these.
+For min-cut, node pairs were sampled.
+In both cases, stratification was used to ensure the same number of nodes were were sampled from each of
+12 node degree quantiles.
+We estimated the error due to sampling by determining true values for a medium-sized project,
+and calculating error as a function of sample-size.
+Sample sizes were chosen such that relative error was below 10\%.
+Even with sampling, however, it was impractical to calculate these properties for the largest projects,
+so we exclude them from the analysis.
+To control for bias in project size, we include several size-related variables in our models.
 
@@
 We also include several project-level variables to control for confounding factors.
+The C-efficiency is included in the model for performance to control for the presence of articles
+that are actively being improved.
+Projects with lower efficiency will have more works-in-progress and could have an artifically low
+performance without controlling for efficiency.
 Some variables are log-transformed to reduce heteroscedasticity.
@@
 once with in-degree skewness and once with out-degree skewness.
+
+The regression results are consistent whether in-degree or out-degree skewness is used,
+although the out-degree models are slightly more significant when modelling efficiency.
 

### 2017-08-07 paper.tex
Add interpretation of regression results.

@@
 
-\section{Empirical Methods}
+\section{WikiProjects}
 
@@
 Our definitions are inpsired by work modeling collective problem-solving as an optimization
-problem \cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, grim_scientific_2013, barkoczi_social_2016}.
+problem \cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012,
+grim_scientific_2013, barkoczi_social_2016}.
 The efficiency quantifies how quikly a solution is reached,
@@
 although the out-degree models are slightly more significant when modelling efficiency.
+We also see that B-efficiency and C-efficiency have very similar models, but that A-efficiency behaves
+differently in its dependence on degree skewness and connectivity.
+The different behavior of A-efficiency is likely explained by the observation that the A-Class quality is
+infrequently used in practice, meaning that the quality level is usually achieved when an article is rated
+as a good or featured article, which involves a different consensus process than lower ratings.
+
+The negative dependence of performance on C-efficiency suggests there is generally a tradeoff between
+performance and efficiency.
+However, low degree is correlated with both higher efficiency and higher performance,
+suggesting that it is sometimes possible to improve both simultaneously.
+Much of the existing numerical work on networked social learning focuses on path length rather than degree,
+so we explore this result further using simulations in the next section.
+
+For path length, we find that longer lengths correspond to lower performance, contrary to the conjecture
+that longer path lengths allow more exploration \cite{mason_propagation_2008}
+but consistent with a conformity-based social learning strategy \cite{barkoczi_social_2016}.
+
+We also observe that high degree skewness is correlated with lower performance and lower A-efficiency,
+suggesting that articles in projects with decentralized coeditor networks reach featured or good status
+more efficiently, and reach higher quality ratings in general.
 
@@
 
-\section{Numerical Simulation}
+\section{Numerical Simulations}
 

### 2017-08-07 paper.tex
Add to simulation content.

@@
 
-Intro
+We use numerical simulations to determine whether simple models can reproduce the behavior we
+observe in WikiProject coeditor networks.
+Following existing numerical work on networked social learning
+\cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, barkoczi_social_2016},
+we use the NK model \cite{kauffman_towards_1987} to create NP-hard, nonlinear optimization problems
+and evaluate the effects of network structure and learning strategy on a group's ability to
+find solution to those problems.
+We are particularly interested in the effect of degree on the efficiency and performance of a group
+of networked problem-solving agents.
+
+In the NK model, N loci each have a binary state and value determined by a random lookup table mapping its state
+and the state of another K loci to a real number in $[0,1]$.
+Solutions thus take the form of an N-bit string, and the value of the solution is the mean over all loci values.
+
+For a particular problem-solving trial, agents each store their current favored solution and
+apply learning strategies to iteratively improve those solutions. We define their
+efficiency and performance in terms of the mean solution values for each time step.
+We define the performance to be the mean solution value after the process has converged,
+while the efficiency is the reciprocal of the number of steps required to converge.
+We measure the time to convergence as the number of steps required to reach 99\% of the maximum
+mean solution value.
 
@@
 
-Individual learning
+Agents can engage in individual learning by applying a hill-climbing algorithm to their current solution.
+In each iteration, one bit of the NK solution string is flipped to maximize the solution value.
+If no change improves the value, the original solution is kept.
+Agents can also incorporate information from any other agents they are connected to by a network edge.
+While individual learning always converges to the local maximum relative to the starting point,
+social learning strategies allow agents to ``jump'' to drastically different solutions with higher local maxima.
 
-Social learning and iteration
+We use both the conformity and best-neighbor strategy from \cite{barkoczi_social_2016}.
+In the best-neighbor strategy, each agent compares its solution to the those of all its
+neighbors, and chooses the solution with the highest value.
+In the conformity strategy, agents simply choose the most common solution among their neighbors
+(ties are broken uniformly at random).
+In both cases, a single iteration of individual learning is performed after each social learning
+iteration.
 
-Best neighbor
-
-Conformity
-
-Consensus
+We also introduce a new strategy, which we call the consensus strategy.
+In consensus, agents first apply individual learning.
+Next, a consensus solution is constructed from each agent's solution by setting
+each NK locus's state to its most common value among the agent's individual solutions.
+The result of this process is that agents accept a single consensus solution at each iteration,
+which forms the basis for future individual learning.
+We include this strategy because of its similarity to the editing process of Wikipedia:
+at any given time, a Wikipedia article has a single state, determined by consensus,
+but editors may have differing opinions on how to improve that article.
 

### 2017-08-08 paper.tex
Add network section.

@@
 
-\subsection{Model}
+\subsection{Regression Models}
 
@@
 and the state of another K loci to a real number in $[0,1]$.
+We report results for the case $N=250$, $K=7$.
 Solutions thus take the form of an N-bit string, and the value of the solution is the mean over all loci values.
@@
 We use both the conformity and best-neighbor strategy from \cite{barkoczi_social_2016}.
-In the best-neighbor strategy, each agent compares its solution to the those of all its
+In the {\em best-neighbor} strategy, each agent compares its solution to the those of all its
 neighbors, and chooses the solution with the highest value.
-In the conformity strategy, agents simply choose the most common solution among their neighbors
+In the {\em conformity} strategy, agents simply choose the most common solution among their neighbors
 (ties are broken uniformly at random).
@@
 
-We also introduce a new strategy, which we call the consensus strategy.
-In consensus, agents first apply individual learning.
-Next, a consensus solution is constructed from each agent's solution by setting
+We introduce a new strategy, which we call the consensus strategy.
+In {\em consensus}, agents first apply individual learning.
+Next, a consensus solution is constructed from each agent's individual solution by setting
 each NK locus's state to its most common value among the agent's individual solutions.
@@
 
+We also introduce local variants of these strategies.
+The local variants are meant to reflect a more realistic collaboration setting where
+individual agents focus on sub-problems.
+In these variants, individual learning takes place on a subset of NK loci.
+Each agent is associated with an NK locus and the loci its value depends on.
+These loci are the agent's {\em concern},
+and are the only ones used for individual learning.
+Similarly, in the consensus strategy, an NK locus's value is determined only by the agents
+concerned with that locus, rather than all agents.
+
 \subsection{Network family}
 
-TODO
+The agent networks used in our simulations vary from those in previous work in two important ways:
+they reflect the structure of the NK model being optimized,
+and they allow the degree to be tuned with minimal change to the mean path length.
 
-Base network
+Our networks are generated by first creating an agent node for each NK locus.
+Each node is assigned a concern consisting of its associated locus and all loci its value depends on,
+as in the local learning strategies.
+This procedure forms an agent-locus affiliation network.
+Next, an agent-agent co-affiliation network is created by connecting two agents if they share at least
+one locus in their concerns.
+This process is exactly analagous to our definition of a WikiProject coeditor network,
+with agents playing the role of editors and NK loci playing the role of Wikipedia articles.
 
-Duplication and rewiring
+To create a tunable degree, we duplicate each node and its node-locus edges and then
+randomly rewire those edges before creating the agent-agent netowork.
+The duplication process creates a high overlap between agent concerns,
+meaning that most agent-locus edges are redundant and do not create additional agent-agent edges,
+resulting in a low average degree.
+By randomly rewiring the agent-locus edges, the redundancy is reduced and the average degree of
+the agent-agent network is increased.
 

### 2017-08-08 paper.tex
Add outline and old background.

@@
 
-TODO
+Collaboration as learning
+
+Collaboration as decision-making
+
+Collaboration as consensus
+
+Collaboration as community
+
+Collaboration and social capital
+
+Networked collaboration: theory
+
+Networked collaboration: experiment
+
+This project
+
+Wikipedia
+
+Social learning on networks has been studied extensively
+\cite{mobius_social_2014},
+focusing on how networked agents can aggregate noisy measurements of
+a ``true'' value.
+In this setting, a naive Bayesian approach converges to the true value when
+certain conditions on degree distribution are met,
+with the speed of convergence depending on the network's {\em spectral gap},
+the gap between the largest two eigenvalues of its adjacency matrix
+\cite{golub_naive_2010}.
+In other settings, collaboration is better modeled as a problem
+of finding the global maximum of a multi-peaked payoff function.
+In this case, lab experiments have shown a complex relationship between
+convergence time, solution quality, with the efficacy of different
+network types (fully-connected, ring, small-world, etc.)
+varying depending on the parameters of the payoff function
+\cite{mason_propagation_2008}.
+
+Collaboration has also been studied extensively through the lens of collective
+decision-making and voting theory.
+The Condorcet jury theorem and its extensions \cite{list_epistemic_2001}
+describe how individuals can use majority voting to improve their
+decision-making ability.
+The process of decision-making is sometimes divided into
+``talking'' and ``voting'' stages.
+While heirarchical representative democracy sometimes improves the outcome
+of ``talk,'' it weakens the result of the Condoret jury theorem for voting
+\cite{list_epistemic_2001}.
+Robert Michels proposed the ``iron law of oligarchy,''
+\cite{michels_political_1999} which states that
+the earlier members of a group will, over time, gain disproportionate
+decision-making power and act increasingly out of self-interest rather than
+the good of the group.
+Shaw and Hill found that behavior in online wiki communities is consistent
+with the iron law \cite{shaw_laboratories_2014}.
+
+A number of studies, summarized in \cite{gentry_consensus_1982},
+have examined consensus-based decision-making procedures, used extensively by
+the Quakers and later by activist communities.
+The hallmark of consensus is the equal and active participation by all members
+of a group.
+Key findings include the tradeoff between speed and quality of decisions,
+the importance of expressing conflict early in the process,
+and the willingness to recognize when one's own views are counter to the
+existing consensus.
+The details of why this tradeoff occurs remain an open question.
+De Tar created InterTwinkles \cite{detar_intertwinkles:_2013},
+an online suite of tools to facilitate consensus decision-making
+in small cooperatives.
+With a better understanding of how large-scale network structure influences
+decision-making, such tools could be extended to large collaborations.
+
+Research on digital communities has also examined some non-network factors
+influcencing the quality of decisions and collaborative work.
+Using a simulation model, Hong and Page \cite{hong_groups_2004} found that
+diverse groups can outperform groups composed of the best individual
+problem-solvers.
+A similar result was observed on Wikipedia by
+Robert and Romero, who found that
+larger group sizes yield higher article ratings
+(as determined by editor peer-review)
+when the groups are diverse and experienced
+\cite{robert_when_2015}.
+Also on Wikipedia,
+Kittur and Kraut found that different types of coordination have a complex
+effect on the quality of Wikipedia articles \cite{kittur_harnessing_2008}.
+Both explicit and implicit coordination result in higher quality articles,
+with explicit coordination being especially central in the early life of an
+article.
+
+A number of theoretical and lab experiments have evaluated the role of networks
+in collective decision-making.
+Some studies focus on how network structure influences individual tendency
+towards altruistic decisions, rather than on decisions made by an entire
+group \cite{eshel_altruists_1998}.
+Grim et al. \cite{grim_scientific_2013} simulated the performance of decision-makers
+seeking to maximize an objective function by communicating their values on a
+number of network structures, observing another tradeoff between speed (for the
+fully-connected network) and quality (for a ring network).
+Grim et al. also found that speed correlated with the characteristic path length
+when running their simulations on parameterized small-world networks
+\cite{watts_collective_1998}.
+
+Lab-based experiments suggest a complex interaction between network topology
+and other factors.
+While groups of networked human subjects reliably perform very well on
+difficult graph-coloring tasks, the best performing network architectures
+(e.g., fully-connected vs. small-world) vary
+from task to task \cite{kearns_experiments_2012}.
+The same studies found that while human subjects tend to perform very well on
+a number of networks, they perform worst on collaboratively self-organized
+networks, highlighting the importance of intentionality
+in constructing communication channels for collective decision-making.
+Similarly, some network topologies are able to reach faster decisions in the
+presence of more information, while others show the opposite effect
+\cite{kearns_experimental_2006}.
+Based on lab experiments, Fowler and Christakis \cite{fowler_cooperative_2010}
+suggest that individual decisions towards altruism are conditional on their
+neighbor's behavior and ``contagious'' up to three degrees away.
+Later experiments by Suri and Watts \cite{suri_cooperation_2011} confirmed the
+existence of conditional altruism,
+but disconfirmed the three-degree hypothesis and conlcuded that altruistic
+behavior only influences first-degree neighbors.
+
+In sociology and anthropology, it has often been observed that an individual's
+position within a social network can result in privilege or power relative to
+others.
+For example, powerful individuals are often ``brokers''
+who act as exclusive intermediaries between disconnected portions of the
+social network \mbox{\cite{silverman_patronage_1965}}.
+Similarly, successful innovation in organizations often occurs in ``structural
+holes'' between groups \mbox{\cite{granovetter_strength_1973}}.
+Thus, the structure of a social network might encode meaningful information
+about the distribution of power and social capital within a group.
+This \mbox{\em strucural (in)equality} might have important consequences for the
+ability of a group to collaborate.
+There is some evidence that groups with high structural inequality,
+as evidenced by highly-skewed degree distributions,
+perform worse on colaborative tasks \mbox{\cite{kearns_experiments_2012}}.
+
+Across the broad range of work on collaboration and related topics,
+a few key themes emerge.
+The efficiency and performance of collaborations are important considerations
+and vary between different networks and problem types.
+While social learning predicts no relationship between the two,
+contagion-style innovation models predict a tradeoff.
+Such a tradeoff has been observed in networked problem-solving and in
+different forms of group decision-making.
+
+In this project, I will investigate several gaps in the existing literature.
+In most cases, degree distribution seems to correlate to performance.
+But aside from the naive Bayes case in social learning, it is unkown whether
+the correlation is explained best by degree or by another structural property
+correlated with degree.
+The characteristic path length and min-cut studied here are candidates for such
+degree-correlated factors.
+While existing work has focused on families of artificial networks,
+this project examines a large number of naturally-occuring networks.
+Unlike artificial networks, the structural properties of these naturally-occuring
+networks can vary independently, making it easier to isolate individual
+network properties that correlate with outcome variables.
+This project will also test whether the detrimental effects of skewed
+distributions of network properties that have been observed in lab experiments
+\mbox{\cite{kearns_experiments_2012}}
+can be observed in large-scale, naturally-occuring data.
 

### 2017-08-08 paper.tex
Updates to background.

@@
 
-Collaboration as learning
+In the field of social learning,
+much research has been done to understand how groups of agents
+can solve problems collaboratively.
+In {\em networked social learning}, agents are represented by nodes on a network
+and can only interact with their neighbors.
+Social learning tasks can be divided into cases where agents have {\em generated signals}
+(independently noisy estimates of a true value)
+and those where agents have {\em interpreted signals}
+(solutions based on different internal models of available data)
+\cite{hong_interpreted_2009}.
+For generated signals,
+a naive Bayesian approach converges to the truth when conditions
+on the network's degree distribution,
+while the speed of convergence depends on the {\em spectral gap}
+between the two largest eigenvalues of the network's adjacency matrix
+\cite{golub_naive_2010}.
+Complex social learning tasks can also be modeled as the problem
+of maximizing an objective function with many local maxima,
+referred to as a {\em rugged landscape}
+\cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, grim_scientific_2013, barkoczi_social_2016}.
+Numerical simulations have shown ttht efficient networks (those with short paths between nodes)
+can allow less exploration of possible solutions,
+resulting in a fast convergence to a non-optimal solution \cite{mason_propagation_2008, grim_scientific_2013}.
+However, when conformity-based social learning strategies are used, efficient networks can outperform
+inefficient ones \cite{barkoczi_social_2016}.
+
+Lab-based experiments on networked collaboration
+suggest a complex interaction between network topology,
+and other factors.
+While groups of networked human subjects reliably perform very well on
+difficult graph-coloring tasks, the best performing network architectures
+(e.g., fully-connected vs. small-world) vary
+from task to task \cite{kearns_experiments_2012}.
+The same studies found that while human subjects tend to perform very well on
+a number of networks, they perform worst on collaboratively self-organized
+networks, highlighting the importance of intentionality
+in constructing communication channels for collective decision-making.
+Similarly, some network topologies are able to reach faster decisions in the
+presence of more information, while others show the opposite effect
+\cite{kearns_experimental_2006}.
+Based on lab experiments, Fowler and Christakis \cite{fowler_cooperative_2010}
+suggest that individual decisions towards altruism are conditional on their
+neighbor's behavior and ``contagious'' up to three degrees away.
+Later experiments by Suri and Watts \cite{suri_cooperation_2011} confirmed the
+existence of conditional altruism,
+but conlcuded that altruistic
+behavior only influences first-degree neighbors.
 
 Collaboration as decision-making
-
 Collaboration as consensus
@@
 Collaboration as community
-
 Collaboration and social capital
 
-Networked collaboration: theory
-
-Networked collaboration: experiment
+Collaboration on Wikipedia
 
@@
 
-Social learning on networks has been studied extensively
-\cite{mobius_social_2014},
-focusing on how networked agents can aggregate noisy measurements of
-a ``true'' value.
-In this setting, a naive Bayesian approach converges to the true value when
-certain conditions on degree distribution are met,
-with the speed of convergence depending on the network's {\em spectral gap},
-the gap between the largest two eigenvalues of its adjacency matrix
-\cite{golub_naive_2010}.
-In other settings, collaboration is better modeled as a problem
-of finding the global maximum of a multi-peaked payoff function.
-In this case, lab experiments have shown a complex relationship between
-convergence time, solution quality, with the efficacy of different
-network types (fully-connected, ring, small-world, etc.)
-varying depending on the parameters of the payoff function
-\cite{mason_propagation_2008}.
+OLD STUFF BELOW HERE
 
@@
 article.
-
-A number of theoretical and lab experiments have evaluated the role of networks
-in collective decision-making.
-Some studies focus on how network structure influences individual tendency
-towards altruistic decisions, rather than on decisions made by an entire
-group \cite{eshel_altruists_1998}.
-Grim et al. \cite{grim_scientific_2013} simulated the performance of decision-makers
-seeking to maximize an objective function by communicating their values on a
-number of network structures, observing another tradeoff between speed (for the
-fully-connected network) and quality (for a ring network).
-Grim et al. also found that speed correlated with the characteristic path length
-when running their simulations on parameterized small-world networks
-\cite{watts_collective_1998}.
-
-Lab-based experiments suggest a complex interaction between network topology
-and other factors.
-While groups of networked human subjects reliably perform very well on
-difficult graph-coloring tasks, the best performing network architectures
-(e.g., fully-connected vs. small-world) vary
-from task to task \cite{kearns_experiments_2012}.
-The same studies found that while human subjects tend to perform very well on
-a number of networks, they perform worst on collaboratively self-organized
-networks, highlighting the importance of intentionality
-in constructing communication channels for collective decision-making.
-Similarly, some network topologies are able to reach faster decisions in the
-presence of more information, while others show the opposite effect
-\cite{kearns_experimental_2006}.
-Based on lab experiments, Fowler and Christakis \cite{fowler_cooperative_2010}
-suggest that individual decisions towards altruism are conditional on their
-neighbor's behavior and ``contagious'' up to three degrees away.
-Later experiments by Suri and Watts \cite{suri_cooperation_2011} confirmed the
-existence of conditional altruism,
-but disconfirmed the three-degree hypothesis and conlcuded that altruistic
-behavior only influences first-degree neighbors.
 
@@
 
-We also introduce local variants of these strategies.
+We also introduce local variants of the above strategies.
 The local variants are meant to reflect a more realistic collaboration setting where

### 2017-08-08 paper.tex
Add value over time figure.

@@
 \usepackage[flushleft]{threeparttable}
+\usepackage{graphicx}
 
@@
 \small
+\caption{Standardized coefficients for OLS models.
+\label{tab:model}
+}
+\bigskip
 \begin{tabular}{lllllllll}
+\hline
                                & Perf$^\dagger$ & Perf$^\dagger$ & A-Eff$^\dagger$ & A-Eff$^\dagger$ & B-Eff$^\dagger$ & B-Eff$^\dagger$ & C-Eff$^\dagger$ & C-Eff$^\dagger$ \\
@@
                                & 0.43            & 0.43 \\
+\hline
 \end{tabular}
-\caption{Standardized coefficients for OLS models.
-\label{tab:model}
-}
 \begin{tablenotes}
@@
 
+\begin{figure}
+\includegraphics[width=3.33in,height=1.67in]{fig-val-iter.pdf}
+\caption{
+Mean agent solution value over time, averaged over 100 trials.
+The left and right figures show results for agent networks with the probability of
+rewiring set to 0 and 1, respectively.
+In both, local strategies are less efficient and more performant than nonlocal.
+The consensus strategy is both more efficient and more performant than others,
+with its performance increasing with higher rewiring.
+\label{fig:val-iter}
+}
+\end{figure}
+
 \section{Discussion}

### 2017-08-08 paper.tex
Add figures, table formatting, related work.

@@
 \usepackage{epigraph}
-\usepackage[flushleft]{threeparttable}
+\usepackage[normal]{threeparttable}
 \usepackage{graphicx}
@@
 behavior only influences first-degree neighbors.
+While theories of networked social learning have been tested in small-scale lab experiments,
+there is a need to study real-world, large-scale collaborations,
+as we do in the present paper.
 
-Collaboration as decision-making
-Collaboration as consensus
-
-Collaboration as community
-Collaboration and social capital
-
-Collaboration on Wikipedia
-
-This project
-
-Wikipedia
-
-OLD STUFF BELOW HERE
-
-Collaboration has also been studied extensively through the lens of collective
-decision-making and voting theory.
+In addition to learning, decision-making is a crucial component of collaboration.
 The Condorcet jury theorem and its extensions \cite{list_epistemic_2001}
@@
 with the iron law \cite{shaw_laboratories_2014}.
-
 A number of studies, summarized in \cite{gentry_consensus_1982},
@@
 existing consensus.
-The details of why this tradeoff occurs remain an open question.
 De Tar created InterTwinkles \cite{detar_intertwinkles:_2013},
@@
 in small cooperatives.
-With a better understanding of how large-scale network structure influences
-decision-making, such tools could be extended to large collaborations.
+Consensus decision making is notoriously difficult to apply in large groups.
+Wikipedia is one of the largest collaborations to use consensus-based
+decision-making,
+making it an excellent place to study the role of network structure in
+large-scale collaboration.
 
@@
 problem-solvers.
-A similar result was observed on Wikipedia by
-Robert and Romero, who found that
+In sociology, much research has been done examining the relationship between
+network structure and social capital.
+Powerful individuals are often ``brokers''
+who act as exclusive intermediaries between disconnected portions of the
+social network \mbox{\cite{silverman_patronage_1965}}.
+Similarly, successful innovation in organizations often occurs in ``structural
+holes'' between groups \mbox{\cite{granovetter_strength_1973}}.
+There is some evidence that groups with high structural inequality,
+as evidenced by highly-skewed degree distributions,
+perform worse on colaborative tasks \mbox{\cite{kearns_experiments_2012}}.
+In the present project, we examine the effect of structural inequality
+on collaboration in Wikipedia.
+
+Several studies have examined the role of community in the specific context
+of Wikipedia.
+Robert and Romero found that
 larger group sizes yield higher article ratings
@@
 
-In sociology and anthropology, it has often been observed that an individual's
-position within a social network can result in privilege or power relative to
-others.
-For example, powerful individuals are often ``brokers''
-who act as exclusive intermediaries between disconnected portions of the
-social network \mbox{\cite{silverman_patronage_1965}}.
-Similarly, successful innovation in organizations often occurs in ``structural
-holes'' between groups \mbox{\cite{granovetter_strength_1973}}.
-Thus, the structure of a social network might encode meaningful information
-about the distribution of power and social capital within a group.
-This \mbox{\em strucural (in)equality} might have important consequences for the
-ability of a group to collaborate.
-There is some evidence that groups with high structural inequality,
-as evidenced by highly-skewed degree distributions,
-perform worse on colaborative tasks \mbox{\cite{kearns_experiments_2012}}.
-
 Across the broad range of work on collaboration and related topics,
@@
 The efficiency and performance of collaborations are important considerations
-and vary between different networks and problem types.
+and vary depending on both network structure and type of task.
 While social learning predicts no relationship between the two,
 contagion-style innovation models predict a tradeoff.
-Such a tradeoff has been observed in networked problem-solving and in
-different forms of group decision-making.
-
+Such a tradeoff has been observed in simulations and lab experiments on
+collaboration.
 In this project, I will investigate several gaps in the existing literature.
-In most cases, degree distribution seems to correlate to performance.
+In much of the existing literature,
+degree distribution correlate to performance.
 But aside from the naive Bayes case in social learning, it is unkown whether
@@
 network properties that correlate with outcome variables.
-This project will also test whether the detrimental effects of skewed
-distributions of network properties that have been observed in lab experiments
-\mbox{\cite{kearns_experiments_2012}}
-can be observed in large-scale, naturally-occuring data.
+This project will also examine Wikipedia for evidence that structural
+inequality (in the form of skewed
+degree distributions) has a deterimental effect on performance,
+as has been observed in lab experiments
+\mbox{\cite{kearns_experiments_2012}}.
+
+Wikipedia
 
@@
 
+\begin{figure*}
+\includegraphics[width=6.67in,height=1.33in]{fig-deg-eff.pdf}
+\includegraphics[width=6.67in,height=1.33in]{fig-deg-perf.pdf}
+\caption{
+TODO
+\label{fig:deg-eff-perf}
+}
+\end{figure*}
+
+\begin{table}
+\small
+\caption{
+Efficiency regression coefficients.
+\label{tab:sim-eff}
+}
+\centering
+\bigskip
+\begin{tabular}{llc}
+\hline
+Strategy & Std. Coeff. \\
+\hline
+Best-neighbor       & -0.064 \\
+Conformity          & -0.080 \\
+Local best-neighbor & -0.086 \\
+Local conformity    & \+0.049 \\
+Consensus           & -0.0325$^{***}$ \\
+\hline
+\end{tabular}
+\begin{tablenotes}
+\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
+\end{tablenotes}
+\end{table}
+
+\begin{table}
+\small
+\caption{
+Performance regression coefficients.
+\label{tab:sim-perf}
+}
+\centering
+\bigskip
+\begin{tabular}{llc}
+\hline
+Strategy & Std. Coeff. \\
+\hline
+Best-neighbor       & \+0.084 \\
+Conformity          & \+0.130 \\
+Local best-neighbor & -0.080 \\
+Local conformity    & -0.020 \\
+Consensus           & \+2.38$\times{10^{-4\;**}}$ \\
+\hline
+\end{tabular}
+\begin{tablenotes}
+\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
+\end{tablenotes}
+\end{table}
+
 \section{Discussion}

### 2017-08-09 paper.tex
Add sim results.

@@
 
-TODO
+We simulated 100 trials for rewiring values of 0.0, 0.167, 0.333, 0.5, 0.667, 0.833, and 1.0.
+For each trial we generated an NK model with N=250 and K=7 and ran each social learning strategy
+for 300 iterations,
+as well as a network based on that NK model and rewired.
+We confirmed that all trials converged to their maximum value before reaching the last iteration.
+Some statistics on the network properties of the networks are summarized in Table \ref{tab:stats}.
+We see that the coefficient of variation of degree is approimately 10\%,
+while only 1\% for mean path length, confirming that the rewiring process has a stronger influence
+on degree than on path length.
+
+\begin{table}
+\small
+\centering
+\caption{
+Simulated network statistics.
+\label{tab:stats}
+}
+\bigskip
+\begin{tabular}{lcc}
+\hline
+Property          & Mean  & Std. Dev. \\
+\hline
+Mean Degree       & 132.3 & 9.2 \\
+Mean Path length  & 1.735 & 0.019 \\
+\hline
+\end{tabular}
+\end{table}
+
+Figure \ref{fig:val-iter} shows how agents' solutions improve after repeated applications of
+different learning strategies and rewiring values.
+Each curve represents an average over 100 trials, each with 250 agent solutions.
+For all rewiring values, local strategies are less efficient and more performant than their
+nonlocal counterparts.
+The consensus strategy is both more efficient and more performant than others,
+with its performance increasing with higher rewiring.
+
+The effect of degree on performance and efficiency is shown in Figure \ref{fig:deg-eff-perf} and
+Tables \ref{tab:sim-eff} and \ref{tab:sim-perf}.
+For both local and nonlocal versions of the best-neighbor and conformity strategies,
+there is no significant effect of degree on performance or efficiency.
+As noted above however, the local versions consistently have higher performance and lower efficiency
+than their nonlocal counterparts.
+We observe more interesting behavior with the consensus strategy.
+Node degree shows a significant negative correlation with degree,
+and a small but significant positive correlation with efficiency.
+The consensus simulations replicate the efficiency behavior observed in WikiProjects,
+but the opposite behavior for performance.
+But unlike other strategies, consensus demonstrates that degree distribution can have an
+impact on both performance and efficiency.
 

### 2017-08-09 paper.tex
Add discussion.

@@
 % Document-specific definitions
-\newcommand{\beq}{\begin{eqnarray}}
-\newcommand{\eeq}{\end{eqnarray}}
-\newcommand{\+}{\phantom{-}}
-
-% Copyright
-%\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-%\acmDOI{10.475/123_4}
-
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
-%  Paso, Texas USA} 
-%\acmYear{1997}
-%\copyrightyear{2016}
-
-%\acmPrice{15.00}
-
-\begin{document}
-\title{Network Structure, Efficiency, and Performance in WikiProjects}
-
-% ACM
-%\author{Edward L. Platt}
-%\affiliation{%
-%  \institution{University of Michigan}
-%  \city{Ann Arbor} 
-%  \state{Michigan} 
-%}
-%\email{elplatt@umich.edu}
-
-% Manuscript
-\author{Edward L. Platt \\ University of Michigan \\ Ann Arbor, Michigan \\ elplatt@umich.edu}
-
-% The default list of authors is too long for headers}
-%\renewcommand{\shortauthors}{B. Trovato et al.}
-
-% ACM
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-%\begin{CCSXML}
-%\end{CCSXML}
+\newcommand{\beq}{\begin{eqnarray
 
@@
 
-Contributions
+Our main findings are:
+\begin{itemize}
+\item WikiProjects having low-degree coeditor networks tend to have both higher performance and higher efficiency, independent of path lengths;
+\item Short path lengths tend to be associated with higher performance, consistent with a conformity-based learning strategy;
+\item Structural inequality, as measured by degree skewness, is associated with lower performance,
+and lower efficiency at reaching the highest quality levels;
+\item Using numerical simulations, we show that the performance and efficiency of some networked learning strategies depends on degree.
+\end{itemize}
+
+The rest of the paper is structured as follows.
+Section \ref{sec:background} reviews related work and the motivation for the present project,
+Section \ref{sec:wp} describes the methodology and results of our empirical analysis of WikiProjects,
+Section \ref{sec:sim} describes the methodology and results of our numerical simulations,
+Section \ref{sec:discuss} discusses the interpretation and broader impact of our results,
+and Section \ref{sec:conclusion} concludes.
 
 \section{Background and Related Work}
+\label{sec:background}
 
@@
 
-Wikipedia
-
 \section{WikiProjects}
+\label{sec:wp}
 
@@
 For information about edit history, we used a publicly-available dataset containing
-metadata about all edits between TODO.
+metadata about all edits from July 12, 2006 to December 2, 2015.
 To get the rating history of each article,
 we wrote a script to scrape the daily logs produced by WP 1.0 Bot for each WikiProject
-between TODO.
+between May 4, 2006 and December 2, 2015.
 Finally, we used a publicly-available log of page events (including rename events)
@@
 Our models are summarized in Table \ref{tab:model}.
-Mean min-cut was found to be highly correlated with degree (see Figure \ref{fig:degree-mincut}),
+Mean min-cut was found to be highly correlated with degree ($r=0.980$, $p<0.001$),
 so we exclude min-cut to prevent collinearity.
@@
 more efficiently, and reach higher quality ratings in general.
-
-\begin{figure}
-\caption{
-TODO
-\label{fig:degree-mincut}
-}
-\end{figure}
 
@@
 \section{Numerical Simulations}
+\label{sec:sim}
 
@@
 \section{Discussion}
-TODO
+\label{sec:discuss}
+
+While existing research into the role of network structure in collaboration
+has focused on numerical simulations and lab experiements,
+analysis of large real-world systems is an important next step.
+Our empirical analysis of WikiProjects contributes several findings towards a better
+understanding of large, decentralized, real-world collaboration.
+We observe several results consistent with previous work:
+a tradeoff between performance and efficiency,
+higher performance for shorter path lengths in a conformity setting,
+and a reduction in performance with increased structural inequality.
+By using real-world networks, we were also able to analyze network properties independently,
+allowing us to show that while most existing work has focused on the importance of path length,
+degree distribution may be just as, or more, important.
+The association of low-degree with both high performance and high efficiency is compelling,
+as it sidesteps the usual tradeoff between performance and efficiency.
+In low-degree networks, agents have more repeated interactions with smaller groups of collaborators,
+possibly suggesting that small team sizes could be beneficial for large collaborations.
+Similarly, the observation that performance is higher in projects with less structural inequality suggests that,
+if the challenges of egalitarian organizing can be overcome,
+decentralized collaborations may produce better outcomes than those with centralized, top-down structures.
+
+Our numerical simulations offer a few additional insights.
+Our proposed local variants of best-neighbor and conformity strategies out-performed
+the standard variants while searching fewer alternatives.
+The higher performance for less work is analogous to the performance increases that
+have been seen for sampling fewer neighbors \cite{barkoczi_social_2016}.
+However, our network is a special case in that its structure is related to the structure of
+the NK model being optimized, which could increase the usefulness of local information.
+Our proposed consensus strategy, intended to model Wikipedia more closely,
+exhibits a degree-dependent performance and efficiency, unlike other strategies.
+This dependence is also seen in our Wikipedia analysis, although performance's dependence has the opposite sign.
+The consensus strategy is also interesting in that it is more efficient and higher performance than the other strategies.
+The unique properties of the consensus strategy may be due to a major difference it has from the others:
+rather than exploring through local hill-climbing,
+the consensus strategy combines parts of existing solutions to create entirely new ones.
+
+Our work has several limitations.
+Our empirical analysis is purely correlative and cannot be used to draw
+conclusions about the causal influence of network structure on collaboration.
+However, the consistency of our results with other lab-based and numerical studies
+suggests that the causal link is worth further study.
+Similarly, our study focuses entirely on a single setting and while it is suggestive,
+does not necessarily generalize,
+and studies of other systems are necessary to corroborate our findings.
+
+Our work raises several questions that could be the subject of future work.
+Is the correlation between network structure, performance, and efficiency causal?
+A time-dependent analysis of our data could offer insight.
+Are similar relationships observed in other large-scale collaborations?
+Does varing degree independently of path length influence performance and efficiency in a controlled
+lab setting?
 
 \section{Conclusion}
+\label{sec:conclusion}
+
 TODO
@@
 \section{Acknowledgements}
-I would like to thank Daniel Romero for valuable guidance and feedback;
+I would like to thank Daniel M. Romero for valuable guidance and feedback;
+Ceren Budak and Scott E. Page for their time and feedback;
 Danielle Livneh and Karthik Ramanathan for help collecting the data sets;

### 2017-08-09 paper.tex
Fix deleted content.
Done.

@@
 % Document-specific definitions
-\newcommand{\beq}{\begin{eqnarray
+\newcommand{\beq}{\begin{eqnarray}}
+\newcommand{\eeq}{\end{eqnarray}}
+\newcommand{\+}{\phantom{-}}
+
+% Copyright
+%\setcopyright{none}
+%\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+%\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
+
+% DOI
+%\acmDOI{10.475/123_4}
+
+% ISBN
+%\acmISBN{123-4567-24-567/08/06}
+
+%Conference
+%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
+%  Paso, Texas USA} 
+%\acmYear{1997}
+%\copyrightyear{2016}
+
+%\acmPrice{15.00}
+
+\begin{document}
+\title{Network Structure, Efficiency, and Performance in WikiProjects}
+
+% ACM
+%\author{Edward L. Platt}
+%\affiliation{%
+%  \institution{University of Michigan}
+%  \city{Ann Arbor} 
+%  \state{Michigan} 
+%}
+%\email{elplatt@umich.edu}
+
+% Manuscript
+\author{Edward L. Platt \\ University of Michigan \\ Ann Arbor, Michigan \\ elplatt@umich.edu}
+
+% The default list of authors is too long for headers}
+%\renewcommand{\shortauthors}{B. Trovato et al.}
+
+% ACM
+% The code below should be generated by the tool at
+% http://dl.acm.org/ccs.cfm
+% Please copy and paste the code instead of the example below. 
+%
+%\begin{CCSXML}
+%\end{CCSXML}
 
@@
 \begin{abstract}
-TODO
+The internet has enabled collaborations at a scale never before possible,
+but the best practices for organizting such large collaboartions are still not clear.
+Wikipedia is a visible and successful example of such a collaboration which might offer
+insight into what makes large-scale, decentralized collaborations successful.
+We analyze the relationship between the structural properties of WikiProject coeditor networks
+and the performance and efficiency of those networks.
+We also perform numerical simulations to determine whether social learning on an NK model can
+reproduce the behavior observed on Wikipedia.
+We find several results seen in numerical and small-scale lab studies:
+a tradeoff between performance and efficiency and
+higher performance with less skewed node distributions and shorter path lengths.
+We also see behaviors not previously identified: an association between low degree coeditor networks
+and both higher performance and higher efficiency,
+suggesting possible benefits to decentralized collaborations made of smaller, more tightly-knit teams.
+We also propose a novel consensus-based social learning strategy that is both more efficient and higher
+performance than existing strategies, and reproduces some behaviors seen in WikiProjects.
 \end{abstract}
@@
 
-Wikipedia successful decentralized.
+The internet has enabled collaborations at a scale never before possible, a global scale.
+Wikipedia is one of the most successful and visible of these collaborations,
+and is particularly interesting for its highly decentralized structure with very little top-down control.
+It is notoriously difficult to organize even small groups without top-down control,
+and yet Wikipedia, with millions of editors, somehow functions.
+A better theoretical understanding of projects like Wikipedia is highly desireable as it could
+help inform the design of new collaborative projects.
+We focus on one aspect of organizing a large-scale decentralized collaboration: the network structure.
+If Wikipedia is not structured as a top-down hierarchy, how is it structured?
+And how does that structure influence its success?
 
-Efficiency Performance
-
-Coeditor network
-
-NK Simulations
+We approach these questions by analyzing WikiProjects on the English-language Wikipedia.
+WikiProjects are collections of thematically related articles,
+each with their own standards, norms, and processes for evaluating and improving articles.
+We analyze the coeditor networks of these projects: which editors have worked together on at least
+one article?
+In particular, we examine the relationship between the structure of a project's coeditor network
+and the performance and efficiency of its articles.
+Performance represents the ability of a project to get articles to a high quality level,
+while efficiency represents the ability to improve articles of any level quickly.
+We also perform numerical simulations to compare the behavior observed on Wikipedia to the results
+of several variants of a simple networked social learning model.
 
@@
 
-We model performance and efficiency in WikiProjects using ordinary least-squares linear regression.
-Each WikiProject is taken as a single observation.
-The models include each project's coeditor network properties as independent variables.
-We also include several project-level variables to control for confounding factors.
-The C-efficiency is included in the model for performance to control for the presence of articles
-that are actively being improved.
-Projects with lower efficiency will have more works-in-progress and could have an artifically low
-performance without controlling for efficiency.
-Some variables are log-transformed to reduce heteroscedasticity.
-
-Our models are summarized in Table \ref{tab:model}.
-Mean min-cut was found to be highly correlated with degree ($r=0.980$, $p<0.001$),
-so we exclude min-cut to prevent collinearity.
-The high correlation between mean degree and min-cut implies that in most cases
-the minimum $st$-cut is simply the either set of edges from $s$ or the set of edges to $t$.
-The rarity of non-trivial min-cuts suggests that WikiProject coeditor networks have very few central
-bottlenecks and are thus highly decentralized.
-In-degree and out-degree skewness were also highly correlated, so each dependent variable was modelled twice:
-once with in-degree skewness and once with out-degree skewness.
-
-The regression results are consistent whether in-degree or out-degree skewness is used,
-although the out-degree models are slightly more significant when modelling efficiency.
-We also see that B-efficiency and C-efficiency have very similar models, but that A-efficiency behaves
-differently in its dependence on degree skewness and connectivity.
-The different behavior of A-efficiency is likely explained by the observation that the A-Class quality is
-infrequently used in practice, meaning that the quality level is usually achieved when an article is rated
-as a good or featured article, which involves a different consensus process than lower ratings.
-
-The negative dependence of performance on C-efficiency suggests there is generally a tradeoff between
-performance and efficiency.
-However, low degree is correlated with both higher efficiency and higher performance,
-suggesting that it is sometimes possible to improve both simultaneously.
-Much of the existing numerical work on networked social learning focuses on path length rather than degree,
-so we explore this result further using simulations in the next section.
-
-For path length, we find that longer lengths correspond to lower performance, contrary to the conjecture
-that longer path lengths allow more exploration \cite{mason_propagation_2008}
-but consistent with a conformity-based social learning strategy \cite{barkoczi_social_2016}.
-
-We also observe that high degree skewness is correlated with lower performance and lower A-efficiency,
-suggesting that articles in projects with decentralized coeditor networks reach featured or good status
-more efficiently, and reach higher quality ratings in general.
-
-\begin{table*}
+\begin{table*}[!ht]
 \small
@@
 \end{table*}
+
+We model performance and efficiency in WikiProjects using ordinary least-squares linear regression.
+Each WikiProject is taken as a single observation.
+The models include each project's coeditor network properties as independent variables.
+We also include several project-level variables to control for confounding factors.
+The C-efficiency is included in the model for performance to control for the presence of articles
+that are actively being improved.
+Projects with lower efficiency will have more works-in-progress and could have an artifically low
+performance without controlling for efficiency.
+Some variables are log-transformed to reduce heteroscedasticity.
+
+Our models are summarized in Table \ref{tab:model}.
+Mean min-cut was found to be highly correlated with degree ($r=0.980$, $p<0.001$),
+so we exclude min-cut to prevent collinearity.
+The high correlation between mean degree and min-cut implies that in most cases
+the minimum $st$-cut is simply the either set of edges from $s$ or the set of edges to $t$.
+The rarity of non-trivial min-cuts suggests that WikiProject coeditor networks have very few central
+bottlenecks and are thus highly decentralized.
+In-degree and out-degree skewness were also highly correlated, so each dependent variable was modelled twice:
+once with in-degree skewness and once with out-degree skewness.
+
+The regression results are consistent whether in-degree or out-degree skewness is used,
+although the out-degree models are slightly more significant when modelling efficiency.
+We also see that B-efficiency and C-efficiency have very similar models, but that A-efficiency behaves
+differently in its dependence on degree skewness and connectivity.
+The different behavior of A-efficiency is likely explained by the observation that the A-Class quality is
+infrequently used in practice, meaning that the quality level is usually achieved when an article is rated
+as a good or featured article, which involves a different consensus process than lower ratings.
+
+The negative dependence of performance on C-efficiency suggests there is generally a tradeoff between
+performance and efficiency.
+However, low degree is correlated with both higher efficiency and higher performance,
+suggesting that it is sometimes possible to improve both simultaneously.
+Much of the existing numerical work on networked social learning focuses on path length rather than degree,
+so we explore this result further using simulations in the next section.
+
+For path length, we find that longer lengths correspond to lower performance, contrary to the conjecture
+that longer path lengths allow more exploration \cite{mason_propagation_2008}
+but consistent with a conformity-based social learning strategy \cite{barkoczi_social_2016}.
+
+We also observe that high degree skewness is correlated with lower performance and lower A-efficiency,
+suggesting that articles in projects with decentralized coeditor networks reach featured or good status
+more efficiently, and reach higher quality ratings in general.
 
@@
 
-Figure \ref{fig:val-iter} shows how agents' solutions improve after repeated applications of
-different learning strategies and rewiring values.
-Each curve represents an average over 100 trials, each with 250 agent solutions.
-For all rewiring values, local strategies are less efficient and more performant than their
-nonlocal counterparts.
-The consensus strategy is both more efficient and more performant than others,
-with its performance increasing with higher rewiring.
-
-The effect of degree on performance and efficiency is shown in Figure \ref{fig:deg-eff-perf} and
-Tables \ref{tab:sim-eff} and \ref{tab:sim-perf}.
-For both local and nonlocal versions of the best-neighbor and conformity strategies,
-there is no significant effect of degree on performance or efficiency.
-As noted above however, the local versions consistently have higher performance and lower efficiency
-than their nonlocal counterparts.
-We observe more interesting behavior with the consensus strategy.
-Node degree shows a significant negative correlation with degree,
-and a small but significant positive correlation with efficiency.
-The consensus simulations replicate the efficiency behavior observed in WikiProjects,
-but the opposite behavior for performance.
-But unlike other strategies, consensus demonstrates that degree distribution can have an
-impact on both performance and efficiency.
-
 \begin{figure}
@@
 \end{figure}
-
-\begin{figure*}
-\includegraphics[width=6.67in,height=1.33in]{fig-deg-eff.pdf}
-\includegraphics[width=6.67in,height=1.33in]{fig-deg-perf.pdf}
-\caption{
-TODO
-\label{fig:deg-eff-perf}
-}
-\end{figure*}
 
@@
 \end{table}
+
+\begin{figure*}
+\includegraphics[width=6.67in,height=1.33in]{fig-deg-eff.pdf}
+\includegraphics[width=6.67in,height=1.33in]{fig-deg-perf.pdf}
+\caption{
+Efficiency and Performance of social learning strategies vs network degree.
+Each point represents a single trial of 300 iterations.
+The consensus strategy shows increased performance and decreased efficiency as
+degree increases, while other strategies show no degree dependence.
+\label{fig:deg-eff-perf}
+}
+\end{figure*}
+
+Figure \ref{fig:val-iter} shows how agents' solutions improve after repeated applications of
+different learning strategies and rewiring values.
+Each curve represents an average over 100 trials, each with 250 agent solutions.
+For all rewiring values, local strategies are less efficient and more performant than their
+nonlocal counterparts.
+The consensus strategy is both more efficient and more performant than others,
+with its performance increasing with higher rewiring.
+
+The effect of degree on performance and efficiency is shown in Figure \ref{fig:deg-eff-perf} and
+Tables \ref{tab:sim-eff} and \ref{tab:sim-perf}.
+For both local and nonlocal versions of the best-neighbor and conformity strategies,
+there is no significant effect of degree on performance or efficiency.
+As noted above however, the local versions consistently have higher performance and lower efficiency
+than their nonlocal counterparts.
+We observe more interesting behavior with the consensus strategy.
+Node degree shows a significant negative correlation with degree,
+and a small but significant positive correlation with efficiency.
+The consensus simulations replicate the efficiency behavior observed in WikiProjects,
+but the opposite behavior for performance.
+But unlike other strategies, consensus demonstrates that degree distribution can have an
+impact on both performance and efficiency.
 
@@
 
-TODO
+In this paper, we have described the relationship between the structural properties of WikiProject
+coeditor networks and the performance and efficiency of those networks.
+As in other studies, we see a tradeoff between performance and efficiency,
+but not an absolute tradeoff.
+Some properties, such as low degree, are associated with both higher performance and higher efficiency.
+We also find that the correlations between path length and performance are consistent with a conformity-based
+social learning strategy, but not a greedy best-neighbor strategy.
+We also observe improved performance in more decentralized project, as has been seen in small-scale lab experiments.
+While the performance and efficiency of most previously-studied social learning strategies depend more on path lenght than
+degree,
+we have proposed a novel consensus learning strategy that is more realistic, more efficient, and higher performance than
+existing strategies.
+While the efficiency and performance of existing strategies do not exhibit any degree-dependence, our consensus strategy
+demonstrates that degree-dependence is possible.
+While additional work is needed to determine causal relationships and how generalizable our results are,
+we have shown evidence that several phenomena predicted by numerical and small-scale lab experiments are present in a large,
+real-world network.
+And, we have identified new behaviors not explained by existing models, suggesting the need for alternate models.
+Our results suggest that the success of large-scale collaborations may be aided by greater decentralization,
+consensus or conformity-baased decision-making, and more tightly-knit collaborations between smaller teams.
 

### 2017-08-13 paper.tex
Fix typos and change quote.

@@
 The internet has enabled collaborations at a scale never before possible,
-but the best practices for organizting such large collaboartions are still not clear.
+but the best practices for organizing such large collaborations are still not clear.
 Wikipedia is a visible and successful example of such a collaboration which might offer
@@
 We find several results seen in numerical and small-scale lab studies:
-a tradeoff between performance and efficiency and
+a trade-off between performance and efficiency and
 higher performance with less skewed node distributions and shorter path lengths.
@@
 \epigraph
-{The problem with Wikipedia is that it only works in practice. In theory, it can never work.}
-{Miikka Ryokas \cite{cohen_latest_2007} }
+{The problem with Wikipedia is that it only works in practice. In theory, it's a total disaster.}
+{Gareth Owen \cite{elsharbaty_editing_2016} }
 
@@
 and yet Wikipedia, with millions of editors, somehow functions.
-A better theoretical understanding of projects like Wikipedia is highly desireable as it could
+A better theoretical understanding of projects like Wikipedia is highly desirable as it could
 help inform the design of new collaborative projects.
@@
 \cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, grim_scientific_2013, barkoczi_social_2016}.
-Numerical simulations have shown ttht efficient networks (those with short paths between nodes)
+Numerical simulations have shown that efficient networks (those with short paths between nodes)
 can allow less exploration of possible solutions,
@@
 existence of conditional altruism,
-but conlcuded that altruistic
+but concluded that altruistic
 behavior only influences first-degree neighbors.
@@
 ``talking'' and ``voting'' stages.
-While heirarchical representative democracy sometimes improves the outcome
+While hierarchical representative democracy sometimes improves the outcome
 of ``talk,'' it weakens the result of the Condoret jury theorem for voting
@@
 of a group.
-Key findings include the tradeoff between speed and quality of decisions,
+Key findings include the trade-off between speed and quality of decisions,
 the importance of expressing conflict early in the process,
@@
 Research on digital communities has also examined some non-network factors
-influcencing the quality of decisions and collaborative work.
+influencing the quality of decisions and collaborative work.
 Using a simulation model, Hong and Page \cite{hong_groups_2004} found that
@@
 as evidenced by highly-skewed degree distributions,
-perform worse on colaborative tasks \mbox{\cite{kearns_experiments_2012}}.
+perform worse on collaborative tasks \mbox{\cite{kearns_experiments_2012}}.
 In the present project, we examine the effect of structural inequality
@@
 While social learning predicts no relationship between the two,
-contagion-style innovation models predict a tradeoff.
-Such a tradeoff has been observed in simulations and lab experiments on
+contagion-style innovation models predict a trade-off.
+Such a trade-off has been observed in simulations and lab experiments on
 collaboration.
@@
 degree distribution correlate to performance.
-But aside from the naive Bayes case in social learning, it is unkown whether
+But aside from the naive Bayes case in social learning, it is unknown whether
 the correlation is explained best by degree or by another structural property
@@
 While existing work has focused on families of artificial networks,
-this project examines a large number of naturally-occuring networks.
-Unlike artificial networks, the structural properties of these naturally-occuring
+this project examines a large number of naturally-occurring networks.
+Unlike artificial networks, the structural properties of these naturally-occurring
 networks can vary independently, making it easier to isolate individual
@@
 inequality (in the form of skewed
-degree distributions) has a deterimental effect on performance,
+degree distributions) has a detrimental effect on performance,
 as has been observed in lab experiments
@@
 
-Our analysis combines multiple datasets from the English-language Wikipedia.
-For information about edit history, we used a publicly-available dataset containing
+Our analysis combines multiple data sets from the English-language Wikipedia.
+For information about edit history, we used a publicly-available data set containing
 metadata about all edits from July 12, 2006 to December 2, 2015.
@@
 projects.
-Our definitions are inpsired by work modeling collective problem-solving as an optimization
+Our definitions are inspired by work modeling collective problem-solving as an optimization
 problem \cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012,
 grim_scientific_2013, barkoczi_social_2016}.
-The efficiency quantifies how quikly a solution is reached,
+The efficiency quantifies how quickly a solution is reached,
 while the performance quantifies how good the eventual solution is.
@@
 So the efficiency is not a measure of how quickly some objective measure of quality improves,
-but rather of how quickly the project participants can reach consensus on the improvments that
+but rather of how quickly the project participants can reach consensus on the improvements that
 need to be made and make those improvements.
@@
 \beq
-E(W,G) &=& \sum_{t \in W(P,G)} \left[ \frac{r(t)}{g(t)} \right]^{-1},
+E(W,G) &=& \frac{1}{|W(P,G)|} \sum_{t \in W(P,G)} \left[ \frac{r(t)}{g(t)} \right]^{-1},
 \eeq
@@
 Measuring performance is difficult for several reasons:
-there is no objective meaasure of article quality avaialbe,
+there is no objective measure of article quality available,
 and articles are always changing, making it difficult to know which articles should be considered
@@
 
-Our final network measure quantifies the connectivy of a project's coeditor network using
+Our final network measure quantifies the connectivity of a project's coeditor network using
 min-cut size.
@@
 and allow innovations to propagate through complex contagion,
-in which innovations are only adopted after multiple exposures thorugh different sources
+in which innovations are only adopted after multiple exposures through different sources
 \cite{centola_complex_2007}.
@@
 that are actively being improved.
-Projects with lower efficiency will have more works-in-progress and could have an artifically low
+Projects with lower efficiency will have more works-in-progress and could have an artificially low
 performance without controlling for efficiency.
@@
 bottlenecks and are thus highly decentralized.
-In-degree and out-degree skewness were also highly correlated, so each dependent variable was modelled twice:
+In-degree and out-degree skewness were also highly correlated, so each dependent variable was modeled twice:
 once with in-degree skewness and once with out-degree skewness.
@@
 The regression results are consistent whether in-degree or out-degree skewness is used,
-although the out-degree models are slightly more significant when modelling efficiency.
+although the out-degree models are slightly more significant when modeling efficiency.
 We also see that B-efficiency and C-efficiency have very similar models, but that A-efficiency behaves
@@
 
-The negative dependence of performance on C-efficiency suggests there is generally a tradeoff between
+The negative dependence of performance on C-efficiency suggests there is generally a trade-off between
 performance and efficiency.
@@
 one locus in their concerns.
-This process is exactly analagous to our definition of a WikiProject coeditor network,
+This process is exactly analogous to our definition of a WikiProject coeditor network,
 with agents playing the role of editors and NK loci playing the role of Wikipedia articles.
@@
 To create a tunable degree, we duplicate each node and its node-locus edges and then
-randomly rewire those edges before creating the agent-agent netowork.
+randomly rewire those edges before creating the agent-agent network.
 The duplication process creates a high overlap between agent concerns,
@@
 Some statistics on the network properties of the networks are summarized in Table \ref{tab:stats}.
-We see that the coefficient of variation of degree is approimately 10\%,
+We see that the coefficient of variation of degree is approximately 10\%,
 while only 1\% for mean path length, confirming that the rewiring process has a stronger influence
@@
 rewiring set to 0 and 1, respectively.
-In both, local strategies are less efficient and more performant than nonlocal.
+In both, local strategies are less efficient and more performant than non-local.
 The consensus strategy is both more efficient and more performant than others,
@@
 For all rewiring values, local strategies are less efficient and more performant than their
-nonlocal counterparts.
+non-local counterparts.
 The consensus strategy is both more efficient and more performant than others,
@@
 Tables \ref{tab:sim-eff} and \ref{tab:sim-perf}.
-For both local and nonlocal versions of the best-neighbor and conformity strategies,
+For both local and non-local versions of the best-neighbor and conformity strategies,
 there is no significant effect of degree on performance or efficiency.
 As noted above however, the local versions consistently have higher performance and lower efficiency
-than their nonlocal counterparts.
+than their non-local counterparts.
 We observe more interesting behavior with the consensus strategy.
@@
 While existing research into the role of network structure in collaboration
-has focused on numerical simulations and lab experiements,
+has focused on numerical simulations and lab experiments,
 analysis of large real-world systems is an important next step.
@@
 We observe several results consistent with previous work:
-a tradeoff between performance and efficiency,
+a trade-off between performance and efficiency,
 higher performance for shorter path lengths in a conformity setting,
@@
 The association of low-degree with both high performance and high efficiency is compelling,
-as it sidesteps the usual tradeoff between performance and efficiency.
+as it sidesteps the usual trade-off between performance and efficiency.
 In low-degree networks, agents have more repeated interactions with smaller groups of collaborators,
@@
 Are similar relationships observed in other large-scale collaborations?
-Does varing degree independently of path length influence performance and efficiency in a controlled
+Does varying degree independently of path length influence performance and efficiency in a controlled
 lab setting?
@@
 coeditor networks and the performance and efficiency of those networks.
-As in other studies, we see a tradeoff between performance and efficiency,
-but not an absolute tradeoff.
+As in other studies, we see a trade-off between performance and efficiency,
+but not an absolute trade-off.
 Some properties, such as low degree, are associated with both higher performance and higher efficiency.
@@
 We also observe improved performance in more decentralized project, as has been seen in small-scale lab experiments.
-While the performance and efficiency of most previously-studied social learning strategies depend more on path lenght than
+While the performance and efficiency of most previously-studied social learning strategies depend more on path length than
 degree,
@@
 Our results suggest that the success of large-scale collaborations may be aided by greater decentralization,
-consensus or conformity-baased decision-making, and more tightly-knit collaborations between smaller teams.
+consensus or conformity-based decision-making, and more tightly-knit collaborations between smaller teams.
 
-\section{Acknowledgements}
+\section{Acknowledgments}
 I would like to thank Daniel M. Romero for valuable guidance and feedback;
@@
 Yan Chen and Tanya Rosenblat for feedback on the methodology;
-and the atendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
+and the attendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
 the Berkman-Klein Center's Cooperation Working Group for helpful feedback on

### 2017-08-13 paper.tex
Add degree mincut figure.

@@
 \beq
-E(W,G) &=& \frac{1}{|W(P,G)|} \sum_{t \in W(P,G)} \left[ \frac{r(t)}{g(t)} \right]^{-1},
+E(W,G) &=& \frac{1}{|T(W,G)|} \sum_{t \in T(W,G)} \left[ \frac{r(t)}{g(t)} \right]^{-1},
 \eeq
@@
 Mean min-cut was found to be highly correlated with degree ($r=0.980$, $p<0.001$),
-so we exclude min-cut to prevent collinearity.
+so we exclude min-cut to prevent collinearity (see Figure \ref{fig:degree-mincut}.
 The high correlation between mean degree and min-cut implies that in most cases
@@
 once with in-degree skewness and once with out-degree skewness.
+
+\begin{figure}
+\centering
+\includegraphics[width=2.33in,height=2.33in]{fig-degree-mincut.pdf}
+\caption{
+Min-cut of WikiProject coeditor networks vs. their mean degree.
+\label{fig:degree-mincut}
+}
+\end{figure}
 

### 2017-08-17 paper-content.tex
Update content and add multiple styles.

--- 2017-08-13 paper.tex
@@
-% ACM
-%\documentclass[sigconf]{acmart}
-
-% Manuscript
-\documentclass[10pt,twocolumn]{article}
-\usepackage[numbers]{natbib}
-
-\usepackage{booktabs} % For formal tables
-
-% Document-specific packages
-\usepackage{epigraph}
-\usepackage[normal]{threeparttable}
-\usepackage{graphicx}
-
-% Document-specific definitions
-\newcommand{\beq}{\begin{eqnarray}}
-\newcommand{\eeq}{\end{eqnarray}}
-\newcommand{\+}{\phantom{-}}
-
-% Copyright
-%\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-%\acmDOI{10.475/123_4}
-
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
-%  Paso, Texas USA} 
-%\acmYear{1997}
-%\copyrightyear{2016}
-
-%\acmPrice{15.00}
-
-\begin{document}
-\title{Network Structure, Efficiency, and Performance in WikiProjects}
-
-% ACM
-%\author{Edward L. Platt}
-%\affiliation{%
-%  \institution{University of Michigan}
-%  \city{Ann Arbor} 
-%  \state{Michigan} 
-%}
-%\email{elplatt@umich.edu}
-
-% Manuscript
-\author{Edward L. Platt \\ University of Michigan \\ Ann Arbor, Michigan \\ elplatt@umich.edu}
-
-% The default list of authors is too long for headers}
-%\renewcommand{\shortauthors}{B. Trovato et al.}
-
-% ACM
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-%\begin{CCSXML}
-%\end{CCSXML}
-
-% ACM
-%\ccsdesc[500]{Computer systems organization~Embedded systems}
-%\ccsdesc[300]{Computer systems organization~Redundancy}
-%\ccsdesc{Computer systems organization~Robotics}
-%\ccsdesc[100]{Networks~Network reliability}
-
-% ACM
-% \keywords{collaboration, peer production, wikipedia}
-
-\maketitle
-
 \begin{abstract}
@@
 We find several results seen in numerical and small-scale lab studies:
-a trade-off between performance and efficiency and
-higher performance with less skewed node distributions and shorter path lengths.
+a performance/efficiency trade-off,
+higher performance with less skewed node distributions,
+and higher performance with shorter path lengths.
 We also see behaviors not previously identified: an association between low degree coeditor networks
@@
 \end{abstract}
+
+\maketitle
 
@@
 If Wikipedia is not structured as a top-down hierarchy, how is it structured?
-And how does that structure influence its success?
+And is that structure related to its success?
 
@@
 For generated signals,
-a naive Bayesian approach converges to the truth when conditions
-on the network's degree distribution,
+a naive Bayesian approach converges to the truth when certain conditions
+on the network's degree distribution are met,
 while the speed of convergence depends on the {\em spectral gap}
 between the two largest eigenvalues of the network's adjacency matrix
-\cite{golub_naive_2010}.
+\cite{degroot_reaching_1974, golub_naive_2010}.
 Complex social learning tasks can also be modeled as the problem
@@
 If $T(W,G)$ is the set of transitions in project $W$ from below grade $G$ to grade $G$ (or higher),
-then we quantify the efficiency $E(W,G)$ as:
+then we first quantify the efficiency $E(W,G)$ as the inverse of the mean number of revisions
+per transition:
 \beq
-E(W,G) &=& \frac{1}{|T(W,G)|} \sum_{t \in T(W,G)} \left[ \frac{r(t)}{g(t)} \right]^{-1},
+E(W,G)
+&=&
+\left[
+\frac{1}{
+|T(W,G)|
+}
+\sum_{t \in T(W,G)} \frac{r(t)}{g(t)}
+\right]^{-1},
 \eeq
@@
 and $n(W)$ is the total number of articles.
+
+Empirically, we find that both efficiency and performance are highly right-skewed,
+with a small number of projects having values much higher than the average.
+After log-transforming the values, both the efficiency and the performance have
+a unimodal distribution with low skew (see Figure \ref{fig:eff-perf-hist}).
 
@@
 \hline
-                               & Perf$^\dagger$ & Perf$^\dagger$ & A-Eff$^\dagger$ & A-Eff$^\dagger$ & B-Eff$^\dagger$ & B-Eff$^\dagger$ & C-Eff$^\dagger$ & C-Eff$^\dagger$ \\
+                               & Perf$_1^\dagger$ & Perf$_2^\dagger$ & A-Eff$_1^\dagger$ & A-Eff$_2^\dagger$ & B-Eff$_1^\dagger$ & B-Eff$_2^\dagger$ & C-Eff$_1^\dagger$ & C-Eff$_2^\dagger$ \\
 \hline
@@
 once with in-degree skewness and once with out-degree skewness.
+
+\begin{figure}
+\centering
+\includegraphics[width=3in,height=3in]{fig-eff-perf-hist.pdf}
+\caption{
+Histograms of WikiProject efficiency and performance.
+Both measures are highly right-skewed, but form unimodal distributions
+with low skewness after log transformation.
+\label{fig:eff-perf-hist}
+}
+\end{figure}
 
@@
 \begin{figure}
-\includegraphics[width=3.33in,height=1.67in]{fig-val-iter.pdf}
+\includegraphics[width=3in,height=1.5in]{fig-val-iter.pdf}
 \caption{
@@
 This research was funded by the University of Michigan School of Information.
-
-% ACM
-%\bibliographystyle{ACM-Reference-Format}
-
-% Manuscript
-\bibliographystyle{acm}
-
-\bibliography{paper}
-
-\end{document}

### 2017-08-17 paper.tex
Update content and add multiple styles.

--- 2017-08-09 paper.tex
@@
 % ACM
-%\documentclass[sigconf]{acmart}
-
-% Manuscript
-\documentclass[10pt,twocolumn]{article}
-\usepackage[numbers]{natbib}
+\documentclass[sigconf]{acmart}
 
@@
 
-% Document-specific packages
-\usepackage{epigraph}
-\usepackage[normal]{threeparttable}
-\usepackage{graphicx}
-
-% Document-specific definitions
-\newcommand{\beq}{\begin{eqnarray}}
-\newcommand{\eeq}{\end{eqnarray}}
-\newcommand{\+}{\phantom{-}}
+\input{paper-preamble.tex}
 
@@
 %Conference
-%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
-%  Paso, Texas USA} 
-%\acmYear{1997}
-%\copyrightyear{2016}
+\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El Paso, Texas USA} 
+\acmYear{1997}
+\copyrightyear{2016}
 
@@
 % ACM
-%\author{Edward L. Platt}
-%\affiliation{%
-%  \institution{University of Michigan}
-%  \city{Ann Arbor} 
-%  \state{Michigan} 
-%}
-%\email{elplatt@umich.edu}
-
-% Manuscript
-\author{Edward L. Platt \\ University of Michigan \\ Ann Arbor, Michigan \\ elplatt@umich.edu}
+\author{Edward L. Platt}
+\affiliation{%
+  \institution{University of Michigan}
+  \city{Ann Arbor} 
+  \state{Michigan} 
+}
+\email{elplatt@umich.edu}
+\author{Daniel M. Romero}
+\affiliation{%
+  \institution{University of Michigan}
+  \city{Ann Arbor} 
+  \state{Michigan} 
+}
+\email{drom@umich.edu}
 
 % The default list of authors is too long for headers}
-%\renewcommand{\shortauthors}{B. Trovato et al.}
+\renewcommand{\shortauthors}{E.L. Platt \& D.M. Romero}
 
@@
 %
-%\begin{CCSXML}
-%\end{CCSXML}
+\begin{CCSXML}
+\end{CCSXML}
 
 % ACM
-%\ccsdesc[500]{Computer systems organization~Embedded systems}
-%\ccsdesc[300]{Computer systems organization~Redundancy}
-%\ccsdesc{Computer systems organization~Robotics}
-%\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Computer systems organization~Embedded systems}
+\ccsdesc[300]{Computer systems organization~Redundancy}
+\ccsdesc{Computer systems organization~Robotics}
+\ccsdesc[100]{Networks~Network reliability}
 
 % ACM
-% \keywords{collaboration, peer production, wikipedia}
+\keywords{collaboration, cooperation, peer production, wikipedia, wikiprojects, }
 
-\maketitle
-
-\begin{abstract}
-The internet has enabled collaborations at a scale never before possible,
-but the best practices for organizting such large collaboartions are still not clear.
-Wikipedia is a visible and successful example of such a collaboration which might offer
-insight into what makes large-scale, decentralized collaborations successful.
-We analyze the relationship between the structural properties of WikiProject coeditor networks
-and the performance and efficiency of those networks.
-We also perform numerical simulations to determine whether social learning on an NK model can
-reproduce the behavior observed on Wikipedia.
-We find several results seen in numerical and small-scale lab studies:
-a tradeoff between performance and efficiency and
-higher performance with less skewed node distributions and shorter path lengths.
-We also see behaviors not previously identified: an association between low degree coeditor networks
-and both higher performance and higher efficiency,
-suggesting possible benefits to decentralized collaborations made of smaller, more tightly-knit teams.
-We also propose a novel consensus-based social learning strategy that is both more efficient and higher
-performance than existing strategies, and reproduces some behaviors seen in WikiProjects.
-\end{abstract}
-
-\section{Introduction}
-\epigraph
-{The problem with Wikipedia is that it only works in practice. In theory, it can never work.}
-{Miikka Ryokas \cite{cohen_latest_2007} }
-
-The internet has enabled collaborations at a scale never before possible, a global scale.
-Wikipedia is one of the most successful and visible of these collaborations,
-and is particularly interesting for its highly decentralized structure with very little top-down control.
-It is notoriously difficult to organize even small groups without top-down control,
-and yet Wikipedia, with millions of editors, somehow functions.
-A better theoretical understanding of projects like Wikipedia is highly desireable as it could
-help inform the design of new collaborative projects.
-We focus on one aspect of organizing a large-scale decentralized collaboration: the network structure.
-If Wikipedia is not structured as a top-down hierarchy, how is it structured?
-And how does that structure influence its success?
-
-We approach these questions by analyzing WikiProjects on the English-language Wikipedia.
-WikiProjects are collections of thematically related articles,
-each with their own standards, norms, and processes for evaluating and improving articles.
-We analyze the coeditor networks of these projects: which editors have worked together on at least
-one article?
-In particular, we examine the relationship between the structure of a project's coeditor network
-and the performance and efficiency of its articles.
-Performance represents the ability of a project to get articles to a high quality level,
-while efficiency represents the ability to improve articles of any level quickly.
-We also perform numerical simulations to compare the behavior observed on Wikipedia to the results
-of several variants of a simple networked social learning model.
-
-Our main findings are:
-\begin{itemize}
-\item WikiProjects having low-degree coeditor networks tend to have both higher performance and higher efficiency, independent of path lengths;
-\item Short path lengths tend to be associated with higher performance, consistent with a conformity-based learning strategy;
-\item Structural inequality, as measured by degree skewness, is associated with lower performance,
-and lower efficiency at reaching the highest quality levels;
-\item Using numerical simulations, we show that the performance and efficiency of some networked learning strategies depends on degree.
-\end{itemize}
-
-The rest of the paper is structured as follows.
-Section \ref{sec:background} reviews related work and the motivation for the present project,
-Section \ref{sec:wp} describes the methodology and results of our empirical analysis of WikiProjects,
-Section \ref{sec:sim} describes the methodology and results of our numerical simulations,
-Section \ref{sec:discuss} discusses the interpretation and broader impact of our results,
-and Section \ref{sec:conclusion} concludes.
-
-\section{Background and Related Work}
-\label{sec:background}
-
-In the field of social learning,
-much research has been done to understand how groups of agents
-can solve problems collaboratively.
-In {\em networked social learning}, agents are represented by nodes on a network
-and can only interact with their neighbors.
-Social learning tasks can be divided into cases where agents have {\em generated signals}
-(independently noisy estimates of a true value)
-and those where agents have {\em interpreted signals}
-(solutions based on different internal models of available data)
-\cite{hong_interpreted_2009}.
-For generated signals,
-a naive Bayesian approach converges to the truth when conditions
-on the network's degree distribution,
-while the speed of convergence depends on the {\em spectral gap}
-between the two largest eigenvalues of the network's adjacency matrix
-\cite{golub_naive_2010}.
-Complex social learning tasks can also be modeled as the problem
-of maximizing an objective function with many local maxima,
-referred to as a {\em rugged landscape}
-\cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, grim_scientific_2013, barkoczi_social_2016}.
-Numerical simulations have shown ttht efficient networks (those with short paths between nodes)
-can allow less exploration of possible solutions,
-resulting in a fast convergence to a non-optimal solution \cite{mason_propagation_2008, grim_scientific_2013}.
-However, when conformity-based social learning strategies are used, efficient networks can outperform
-inefficient ones \cite{barkoczi_social_2016}.
-
-Lab-based experiments on networked collaboration
-suggest a complex interaction between network topology,
-and other factors.
-While groups of networked human subjects reliably perform very well on
-difficult graph-coloring tasks, the best performing network architectures
-(e.g., fully-connected vs. small-world) vary
-from task to task \cite{kearns_experiments_2012}.
-The same studies found that while human subjects tend to perform very well on
-a number of networks, they perform worst on collaboratively self-organized
-networks, highlighting the importance of intentionality
-in constructing communication channels for collective decision-making.
-Similarly, some network topologies are able to reach faster decisions in the
-presence of more information, while others show the opposite effect
-\cite{kearns_experimental_2006}.
-Based on lab experiments, Fowler and Christakis \cite{fowler_cooperative_2010}
-suggest that individual decisions towards altruism are conditional on their
-neighbor's behavior and ``contagious'' up to three degrees away.
-Later experiments by Suri and Watts \cite{suri_cooperation_2011} confirmed the
-existence of conditional altruism,
-but conlcuded that altruistic
-behavior only influences first-degree neighbors.
-While theories of networked social learning have been tested in small-scale lab experiments,
-there is a need to study real-world, large-scale collaborations,
-as we do in the present paper.
-
-In addition to learning, decision-making is a crucial component of collaboration.
-The Condorcet jury theorem and its extensions \cite{list_epistemic_2001}
-describe how individuals can use majority voting to improve their
-decision-making ability.
-The process of decision-making is sometimes divided into
-``talking'' and ``voting'' stages.
-While heirarchical representative democracy sometimes improves the outcome
-of ``talk,'' it weakens the result of the Condoret jury theorem for voting
-\cite{list_epistemic_2001}.
-Robert Michels proposed the ``iron law of oligarchy,''
-\cite{michels_political_1999} which states that
-the earlier members of a group will, over time, gain disproportionate
-decision-making power and act increasingly out of self-interest rather than
-the good of the group.
-Shaw and Hill found that behavior in online wiki communities is consistent
-with the iron law \cite{shaw_laboratories_2014}.
-A number of studies, summarized in \cite{gentry_consensus_1982},
-have examined consensus-based decision-making procedures, used extensively by
-the Quakers and later by activist communities.
-The hallmark of consensus is the equal and active participation by all members
-of a group.
-Key findings include the tradeoff between speed and quality of decisions,
-the importance of expressing conflict early in the process,
-and the willingness to recognize when one's own views are counter to the
-existing consensus.
-De Tar created InterTwinkles \cite{detar_intertwinkles:_2013},
-an online suite of tools to facilitate consensus decision-making
-in small cooperatives.
-Consensus decision making is notoriously difficult to apply in large groups.
-Wikipedia is one of the largest collaborations to use consensus-based
-decision-making,
-making it an excellent place to study the role of network structure in
-large-scale collaboration.
-
-Research on digital communities has also examined some non-network factors
-influcencing the quality of decisions and collaborative work.
-Using a simulation model, Hong and Page \cite{hong_groups_2004} found that
-diverse groups can outperform groups composed of the best individual
-problem-solvers.
-In sociology, much research has been done examining the relationship between
-network structure and social capital.
-Powerful individuals are often ``brokers''
-who act as exclusive intermediaries between disconnected portions of the
-social network \mbox{\cite{silverman_patronage_1965}}.
-Similarly, successful innovation in organizations often occurs in ``structural
-holes'' between groups \mbox{\cite{granovetter_strength_1973}}.
-There is some evidence that groups with high structural inequality,
-as evidenced by highly-skewed degree distributions,
-perform worse on colaborative tasks \mbox{\cite{kearns_experiments_2012}}.
-In the present project, we examine the effect of structural inequality
-on collaboration in Wikipedia.
-
-Several studies have examined the role of community in the specific context
-of Wikipedia.
-Robert and Romero found that
-larger group sizes yield higher article ratings
-(as determined by editor peer-review)
-when the groups are diverse and experienced
-\cite{robert_when_2015}.
-Also on Wikipedia,
-Kittur and Kraut found that different types of coordination have a complex
-effect on the quality of Wikipedia articles \cite{kittur_harnessing_2008}.
-Both explicit and implicit coordination result in higher quality articles,
-with explicit coordination being especially central in the early life of an
-article.
-
-Across the broad range of work on collaboration and related topics,
-a few key themes emerge.
-The efficiency and performance of collaborations are important considerations
-and vary depending on both network structure and type of task.
-While social learning predicts no relationship between the two,
-contagion-style innovation models predict a tradeoff.
-Such a tradeoff has been observed in simulations and lab experiments on
-collaboration.
-In this project, I will investigate several gaps in the existing literature.
-In much of the existing literature,
-degree distribution correlate to performance.
-But aside from the naive Bayes case in social learning, it is unkown whether
-the correlation is explained best by degree or by another structural property
-correlated with degree.
-The characteristic path length and min-cut studied here are candidates for such
-degree-correlated factors.
-While existing work has focused on families of artificial networks,
-this project examines a large number of naturally-occuring networks.
-Unlike artificial networks, the structural properties of these naturally-occuring
-networks can vary independently, making it easier to isolate individual
-network properties that correlate with outcome variables.
-This project will also examine Wikipedia for evidence that structural
-inequality (in the form of skewed
-degree distributions) has a deterimental effect on performance,
-as has been observed in lab experiments
-\mbox{\cite{kearns_experiments_2012}}.
-
-\section{WikiProjects}
-\label{sec:wp}
-
-\subsection{Data}
-
-Our analysis combines multiple datasets from the English-language Wikipedia.
-For information about edit history, we used a publicly-available dataset containing
-metadata about all edits from July 12, 2006 to December 2, 2015.
-To get the rating history of each article,
-we wrote a script to scrape the daily logs produced by WP 1.0 Bot for each WikiProject
-between May 4, 2006 and December 2, 2015.
-Finally, we used a publicly-available log of page events (including rename events)
-to reconstruct the unique identifier for each article title mentioned in the rating history logs.
-
-\subsection{Efficiency and Performance}
-
-To model the relationship between performance, efficiency, and network structure,
-we must have a way to quantify performance and efficiency.
-We define these quantities on a per-WikiProject basis to enable comparisons across different
-projects.
-Our definitions are inpsired by work modeling collective problem-solving as an optimization
-problem \cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012,
-grim_scientific_2013, barkoczi_social_2016}.
-The efficiency quantifies how quikly a solution is reached,
-while the performance quantifies how good the eventual solution is.
-
-For a WikiProject, efficiency quantifies how quickly project participants can improve the
-assessed quality of an article.
-Quality assessments are made through consensus of the project participants themselves,
-so different projects can have different standards and practices for assessing article quality.
-So the efficiency is not a measure of how quickly some objective measure of quality improves,
-but rather of how quickly the project participants can reach consensus on the improvments that
-need to be made and make those improvements.
-Because our definition relies on assessment transitions, we define efficiency variables for
-each of the project-level quality assessments: A, B, and C.
-If $T(W,G)$ is the set of transitions in project $W$ from below grade $G$ to grade $G$ (or higher),
-then we quantify the efficiency $E(W,G)$ as:
-\beq
-E(W,G) &=& \sum_{t \in W(P,G)} \left[ \frac{r(t)}{g(t)} \right]^{-1},
-\eeq
-where $r(t)$ is the number of revisions since the previous grade transition,
-and $g(t)$ is the number of grade levels crossed by transition $t$.
-The $g(t)$ term is added because an assessments often raise article quality by several
-grades, in which case the revisions are divided evenly between all grade levels achieved.
-It is also worth noting that we measure efficiency in terms of revisions made,
-rather than time passed.
-We focus on revisions because the amount of work done on an article varies widely from day to day.
-
-For performance, we wish to quantify how good articles tend to be when they reach a stable state.
-Measuring performance is difficult for several reasons:
-there is no objective meaasure of article quality avaialbe,
-and articles are always changing, making it difficult to know which articles should be considered
-complete or stable.
-We use an extremely simple performance measure that gives surprisingly consistent results.
-In addition to per-project quality assessment, articles can be given ``featured article'' or
-``good article'' status.
-The criteria for these statuses are consistent across all of Wikipedia,
-and any editor can participate in the discussion and decision to award good or featured
-status.
-In other words, the good and featured statuses are more objective than per-project assessments.
-Our performance measure $P(W)$ is just the percentage of articles in project $W$ which have reached
-good or featured status:
-\beq
-P(W) &=& \frac{f(W) + g(W)}{n(W)},
-\eeq
-where $f(W)$ and $g(W)$ are the numbered of featured and good articles respectively,
-and $n(W)$ is the total number of articles.
-
-\subsection{Coeditor Networks}
-
-For each WikiProject, we compare the efficiency and performance measures to the structural
-properties of its coeditor network.
-The {\em coeditor network} of a WikiProject consists of nodes representing editors.
-Two editors are connected when they have both edited the same article or talk page.
-The edges are directed, with the direction representing the direction of
-{\em plausible information flow};
-an edge from editor A to editor B exists if A edited an article and then B edited the same article at
-a later time.
-Edges can exist in both directions e.g., if an article was edited first by A, then by B, and again by A.
-For simplicity, we assign all edges unit weight.
-We focus on three structural properties: degree, characteristic path length, and min-cut.
-
-The node degree distribution is the simplest structural property we analyze for WikiProject
-coeditor networks.
-The in-degree (out-degree) of a node is the number of edges to (from) that node.
-Taking the average of either in-degree or out-degree gives the same value:
-the {\em mean degree} of the network.
-In our context, the mean degree represents how many others a given editor has collaborated with.
-We also consider the {\em skewness} of the in-degree and out-degree distributions.
-A large positive degree skewness value for a WikiProject coeditor network
-implies that a small number of editors have a very large number of collaborators,
-while a small positive value implies that the editors having the most collaborators
-don't have many more than a typical editor.
-
-We also calculate the characteristic path length for each WikiProject coeditor network.
-The {\em distance} from editor A to editor B is the length of the shortest path from A to B.
-The {\em characteristic path length} is the mean distance between all editor pairs.
-If no path exists between two editors, we exclude that pair from the mean.
-For brevity, we will simply refer to this quantity as the {\em path length}.
-The path length represents how quickly information can move through the network.
-Networks with longer paths require more interactions for information to propagate through
-the network,
-which has been shown to reduce efficiency in some settings
-\cite{mason_propagation_2008,barkoczi_social_2016}.
-
-Our final network measure quantifies the connectivy of a project's coeditor network using
-min-cut size.
-The minimum $st$-cut between nodes $s$ and $t$ is the set of edges that must be removed in order that
-no path exists from $s$ to $t$.
-The minimum cut (min-cut) of a graph is the smallest minimum $st$-cut over all node pairs $st$. 
-The size of the graph min-cut quantifies the connectivity of a graph,
-but only incorporates information about edges lying on paths crossing the min-cut.
-Instead, we use the mean size of all minimum $st$-cuts, which we refer to as the
-{\em mean min-cut}.
-This measure quantifies the number of redundant paths information can take through the network.
-Networks with higher redundancy are more resilient to errors on one path \cite{albert_error_2000}
-and allow innovations to propagate through complex contagion,
-in which innovations are only adopted after multiple exposures thorugh different sources
-\cite{centola_complex_2007}.
-
-The mean path and min-cut network measures are computationally intensive,
-requiring distance and minimum $st$-cut calculations for each all node pairs.
-For larger projects, these calculations are impractical.
-When coeditor networks were large, we employed sampling to determine mean path length and mean
-min-cut.
-For mean path length, source nodes were sampled, and path length was calculated to all destination nodes
-from each of these.
-For min-cut, node pairs were sampled.
-In both cases, stratification was used to ensure the same number of nodes were were sampled from each of
-12 node degree quantiles.
-We estimated the error due to sampling by determining true values for a medium-sized project,
-and calculating error as a function of sample-size.
-Sample sizes were chosen such that relative error was below 10\%.
-Even with sampling, however, it was impractical to calculate these properties for the largest projects,
-so we exclude them from the analysis.
-To control for bias in project size, we include several size-related variables in our models.
-
-\subsection{Regression Models}
-
-\begin{table*}[!ht]
-\small
-\caption{Standardized coefficients for OLS models.
-\label{tab:model}
-}
-\bigskip
-\begin{tabular}{lllllllll}
-\hline
-                               & Perf$^\dagger$ & Perf$^\dagger$ & A-Eff$^\dagger$ & A-Eff$^\dagger$ & B-Eff$^\dagger$ & B-Eff$^\dagger$ & C-Eff$^\dagger$ & C-Eff$^\dagger$ \\
-\hline
-Mean degree$^\dagger$          &  -0.84$^{***}$  &  -0.78$^{***}$
-                               &  -0.61$^{**}$   &  -0.84$^{***}$
-                               &  -0.50$^{***}$  &  -0.61$^{***}$
-                               &  -0.34$^{**}$   &  -0.31$^{*}$ \\
-In-degree skewness$^\dagger$   &  -0.58$^{***}$  & \+ ---      
-                               &  -0.43$^{**}$   & \+ ---      
-                               &  -0.19          & \+ ---      
-                               &  -0.1           & \+ ---      \\
-Out-degree skewness$^\dagger$  &  \+ ---         &  -0.48$^{***}$  
-                               &  \+ ---         &  -0.57$^{***}$
-                               &  \+ ---         &  -0.26$^{*}$
-                               &  \+ ---         &  -0.066 \\
-Mean path$^\dagger$            &  -0.357$^{***}$ &  -0.356$^{***}$ 
-                               &  -0.026         &  -0.096
-                               &  -0.020         &  -0.045
-                               &  -0.092$^{**}$  &  -0.086 \\
-C-eff$^\dagger$                &  -0.083$^{**}$  & -0.085$^{**}$  
-                               &  \+ ---         & \+ ---      
-                               &  \+ ---         & \+ ---      
-                               &  \+ ---         & \+ --- \\
-Connectivity                   & \+0.018         & \+0.016        
-                               & \+0.081         & \+0.088
-                               & \+0.126$^{***}$ & \+0.142$^{***}$
-                               & \+0.080$^{**}$  & \+0.081$^{**}$ \\
-Mean editors/article$^\dagger$ & \+0.37$^{***}$  & \+0.40$^{***}$ 
-                               & \+0.22          & \+0.27
-                               & \+0.20          & \+0.22$^{*}$
-                               & \+0.076         & \+0.075 \\
-Article count$^\dagger$        &  -0.32          & -0.27          
-                               & \+0.63${^*}$    & \+0.70${^*}$ 
-                               & \+0.76$^{**}$   & \+0.78$^{**}$
-                               & \+0.67$^{***}$  & \+0.67$^{***}$ \\
-Editor count$^\dagger$         & \+0.68$^{*}$    & \+0.48         
-                               & \+0.74$^{*}$    & \+0.97$^{**}$
-                               & \+0.60$^{*}$    & \+0.72$^{**}$
-                               & \+0.52$^{*}$    & \+0.46$^{*}$ \\
-Revision count$^\dagger$       & \+0.37          & \+0.39         
-                               &  -0.84$^{**}$   & -0.88$^{**}$
-                               &  -1.05$^{***}$  & -1.05$^{***}$
-                               &  -1.00$^{***}$  & -1.00$^{***}$ \\
-First assessment               & \+0.028         & \+0.058        
-                               & \+0.086$^{*}$   & \+0.101$^{**}$
-                               & \+0.309$^{***}$ & \+0.321$^{***}$
-                               & \+0.456$^{***}$ & \+0.460$^{***}$ \\
-Mean article age               &  -0.040         & -0.029         
-                               &  -0.049         & -0.037
-                               &  -0.019         & -0.014
-                               &  -0.046$^{*}$   & -0.045$^{*}$ \\
-\hline
-DoF                            & 1278            & 1278          
-                               & 1048            & 1048
-                               & 1371            & 1371
-                               & 1540            & 1540 \\
-R$^2_{adj}$                    & 0.37            & 0.37          
-                               & 0.15            & 0.16
-                               & 0.30            & 0.30
-                               & 0.43            & 0.43 \\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item $\dagger$ Log-transformed. * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
-\end{tablenotes}
-\end{table*}
-
-We model performance and efficiency in WikiProjects using ordinary least-squares linear regression.
-Each WikiProject is taken as a single observation.
-The models include each project's coeditor network properties as independent variables.
-We also include several project-level variables to control for confounding factors.
-The C-efficiency is included in the model for performance to control for the presence of articles
-that are actively being improved.
-Projects with lower efficiency will have more works-in-progress and could have an artifically low
-performance without controlling for efficiency.
-Some variables are log-transformed to reduce heteroscedasticity.
-
-Our models are summarized in Table \ref{tab:model}.
-Mean min-cut was found to be highly correlated with degree ($r=0.980$, $p<0.001$),
-so we exclude min-cut to prevent collinearity.
-The high correlation between mean degree and min-cut implies that in most cases
-the minimum $st$-cut is simply the either set of edges from $s$ or the set of edges to $t$.
-The rarity of non-trivial min-cuts suggests that WikiProject coeditor networks have very few central
-bottlenecks and are thus highly decentralized.
-In-degree and out-degree skewness were also highly correlated, so each dependent variable was modelled twice:
-once with in-degree skewness and once with out-degree skewness.
-
-The regression results are consistent whether in-degree or out-degree skewness is used,
-although the out-degree models are slightly more significant when modelling efficiency.
-We also see that B-efficiency and C-efficiency have very similar models, but that A-efficiency behaves
-differently in its dependence on degree skewness and connectivity.
-The different behavior of A-efficiency is likely explained by the observation that the A-Class quality is
-infrequently used in practice, meaning that the quality level is usually achieved when an article is rated
-as a good or featured article, which involves a different consensus process than lower ratings.
-
-The negative dependence of performance on C-efficiency suggests there is generally a tradeoff between
-performance and efficiency.
-However, low degree is correlated with both higher efficiency and higher performance,
-suggesting that it is sometimes possible to improve both simultaneously.
-Much of the existing numerical work on networked social learning focuses on path length rather than degree,
-so we explore this result further using simulations in the next section.
-
-For path length, we find that longer lengths correspond to lower performance, contrary to the conjecture
-that longer path lengths allow more exploration \cite{mason_propagation_2008}
-but consistent with a conformity-based social learning strategy \cite{barkoczi_social_2016}.
-
-We also observe that high degree skewness is correlated with lower performance and lower A-efficiency,
-suggesting that articles in projects with decentralized coeditor networks reach featured or good status
-more efficiently, and reach higher quality ratings in general.
-
-\section{Numerical Simulations}
-\label{sec:sim}
-
-We use numerical simulations to determine whether simple models can reproduce the behavior we
-observe in WikiProject coeditor networks.
-Following existing numerical work on networked social learning
-\cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, barkoczi_social_2016},
-we use the NK model \cite{kauffman_towards_1987} to create NP-hard, nonlinear optimization problems
-and evaluate the effects of network structure and learning strategy on a group's ability to
-find solution to those problems.
-We are particularly interested in the effect of degree on the efficiency and performance of a group
-of networked problem-solving agents.
-
-In the NK model, N loci each have a binary state and value determined by a random lookup table mapping its state
-and the state of another K loci to a real number in $[0,1]$.
-We report results for the case $N=250$, $K=7$.
-Solutions thus take the form of an N-bit string, and the value of the solution is the mean over all loci values.
-
-For a particular problem-solving trial, agents each store their current favored solution and
-apply learning strategies to iteratively improve those solutions. We define their
-efficiency and performance in terms of the mean solution values for each time step.
-We define the performance to be the mean solution value after the process has converged,
-while the efficiency is the reciprocal of the number of steps required to converge.
-We measure the time to convergence as the number of steps required to reach 99\% of the maximum
-mean solution value.
-
-\subsection{Learning Strategies}
-
-Agents can engage in individual learning by applying a hill-climbing algorithm to their current solution.
-In each iteration, one bit of the NK solution string is flipped to maximize the solution value.
-If no change improves the value, the original solution is kept.
-Agents can also incorporate information from any other agents they are connected to by a network edge.
-While individual learning always converges to the local maximum relative to the starting point,
-social learning strategies allow agents to ``jump'' to drastically different solutions with higher local maxima.
-
-We use both the conformity and best-neighbor strategy from \cite{barkoczi_social_2016}.
-In the {\em best-neighbor} strategy, each agent compares its solution to the those of all its
-neighbors, and chooses the solution with the highest value.
-In the {\em conformity} strategy, agents simply choose the most common solution among their neighbors
-(ties are broken uniformly at random).
-In both cases, a single iteration of individual learning is performed after each social learning
-iteration.
-
-We introduce a new strategy, which we call the consensus strategy.
-In {\em consensus}, agents first apply individual learning.
-Next, a consensus solution is constructed from each agent's individual solution by setting
-each NK locus's state to its most common value among the agent's individual solutions.
-The result of this process is that agents accept a single consensus solution at each iteration,
-which forms the basis for future individual learning.
-We include this strategy because of its similarity to the editing process of Wikipedia:
-at any given time, a Wikipedia article has a single state, determined by consensus,
-but editors may have differing opinions on how to improve that article.
-
-We also introduce local variants of the above strategies.
-The local variants are meant to reflect a more realistic collaboration setting where
-individual agents focus on sub-problems.
-In these variants, individual learning takes place on a subset of NK loci.
-Each agent is associated with an NK locus and the loci its value depends on.
-These loci are the agent's {\em concern},
-and are the only ones used for individual learning.
-Similarly, in the consensus strategy, an NK locus's value is determined only by the agents
-concerned with that locus, rather than all agents.
-
-\subsection{Network family}
-
-The agent networks used in our simulations vary from those in previous work in two important ways:
-they reflect the structure of the NK model being optimized,
-and they allow the degree to be tuned with minimal change to the mean path length.
-
-Our networks are generated by first creating an agent node for each NK locus.
-Each node is assigned a concern consisting of its associated locus and all loci its value depends on,
-as in the local learning strategies.
-This procedure forms an agent-locus affiliation network.
-Next, an agent-agent co-affiliation network is created by connecting two agents if they share at least
-one locus in their concerns.
-This process is exactly analagous to our definition of a WikiProject coeditor network,
-with agents playing the role of editors and NK loci playing the role of Wikipedia articles.
-
-To create a tunable degree, we duplicate each node and its node-locus edges and then
-randomly rewire those edges before creating the agent-agent netowork.
-The duplication process creates a high overlap between agent concerns,
-meaning that most agent-locus edges are redundant and do not create additional agent-agent edges,
-resulting in a low average degree.
-By randomly rewiring the agent-locus edges, the redundancy is reduced and the average degree of
-the agent-agent network is increased.
-
-\subsection{Simulation results}
-
-We simulated 100 trials for rewiring values of 0.0, 0.167, 0.333, 0.5, 0.667, 0.833, and 1.0.
-For each trial we generated an NK model with N=250 and K=7 and ran each social learning strategy
-for 300 iterations,
-as well as a network based on that NK model and rewired.
-We confirmed that all trials converged to their maximum value before reaching the last iteration.
-Some statistics on the network properties of the networks are summarized in Table \ref{tab:stats}.
-We see that the coefficient of variation of degree is approimately 10\%,
-while only 1\% for mean path length, confirming that the rewiring process has a stronger influence
-on degree than on path length.
-
-\begin{table}
-\small
-\centering
-\caption{
-Simulated network statistics.
-\label{tab:stats}
-}
-\bigskip
-\begin{tabular}{lcc}
-\hline
-Property          & Mean  & Std. Dev. \\
-\hline
-Mean Degree       & 132.3 & 9.2 \\
-Mean Path length  & 1.735 & 0.019 \\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{figure}
-\includegraphics[width=3.33in,height=1.67in]{fig-val-iter.pdf}
-\caption{
-Mean agent solution value over time, averaged over 100 trials.
-The left and right figures show results for agent networks with the probability of
-rewiring set to 0 and 1, respectively.
-In both, local strategies are less efficient and more performant than nonlocal.
-The consensus strategy is both more efficient and more performant than others,
-with its performance increasing with higher rewiring.
-\label{fig:val-iter}
-}
-\end{figure}
-
-\begin{table}
-\small
-\caption{
-Efficiency regression coefficients.
-\label{tab:sim-eff}
-}
-\centering
-\bigskip
-\begin{tabular}{llc}
-\hline
-Strategy & Std. Coeff. \\
-\hline
-Best-neighbor       & -0.064 \\
-Conformity          & -0.080 \\
-Local best-neighbor & -0.086 \\
-Local conformity    & \+0.049 \\
-Consensus           & -0.0325$^{***}$ \\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
-\end{tablenotes}
-\end{table}
-
-\begin{table}
-\small
-\caption{
-Performance regression coefficients.
-\label{tab:sim-perf}
-}
-\centering
-\bigskip
-\begin{tabular}{llc}
-\hline
-Strategy & Std. Coeff. \\
-\hline
-Best-neighbor       & \+0.084 \\
-Conformity          & \+0.130 \\
-Local best-neighbor & -0.080 \\
-Local conformity    & -0.020 \\
-Consensus           & \+2.38$\times{10^{-4\;**}}$ \\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
-\end{tablenotes}
-\end{table}
-
-\begin{figure*}
-\includegraphics[width=6.67in,height=1.33in]{fig-deg-eff.pdf}
-\includegraphics[width=6.67in,height=1.33in]{fig-deg-perf.pdf}
-\caption{
-Efficiency and Performance of social learning strategies vs network degree.
-Each point represents a single trial of 300 iterations.
-The consensus strategy shows increased performance and decreased efficiency as
-degree increases, while other strategies show no degree dependence.
-\label{fig:deg-eff-perf}
-}
-\end{figure*}
-
-Figure \ref{fig:val-iter} shows how agents' solutions improve after repeated applications of
-different learning strategies and rewiring values.
-Each curve represents an average over 100 trials, each with 250 agent solutions.
-For all rewiring values, local strategies are less efficient and more performant than their
-nonlocal counterparts.
-The consensus strategy is both more efficient and more performant than others,
-with its performance increasing with higher rewiring.
-
-The effect of degree on performance and efficiency is shown in Figure \ref{fig:deg-eff-perf} and
-Tables \ref{tab:sim-eff} and \ref{tab:sim-perf}.
-For both local and nonlocal versions of the best-neighbor and conformity strategies,
-there is no significant effect of degree on performance or efficiency.
-As noted above however, the local versions consistently have higher performance and lower efficiency
-than their nonlocal counterparts.
-We observe more interesting behavior with the consensus strategy.
-Node degree shows a significant negative correlation with degree,
-and a small but significant positive correlation with efficiency.
-The consensus simulations replicate the efficiency behavior observed in WikiProjects,
-but the opposite behavior for performance.
-But unlike other strategies, consensus demonstrates that degree distribution can have an
-impact on both performance and efficiency.
-
-\section{Discussion}
-\label{sec:discuss}
-
-While existing research into the role of network structure in collaboration
-has focused on numerical simulations and lab experiements,
-analysis of large real-world systems is an important next step.
-Our empirical analysis of WikiProjects contributes several findings towards a better
-understanding of large, decentralized, real-world collaboration.
-We observe several results consistent with previous work:
-a tradeoff between performance and efficiency,
-higher performance for shorter path lengths in a conformity setting,
-and a reduction in performance with increased structural inequality.
-By using real-world networks, we were also able to analyze network properties independently,
-allowing us to show that while most existing work has focused on the importance of path length,
-degree distribution may be just as, or more, important.
-The association of low-degree with both high performance and high efficiency is compelling,
-as it sidesteps the usual tradeoff between performance and efficiency.
-In low-degree networks, agents have more repeated interactions with smaller groups of collaborators,
-possibly suggesting that small team sizes could be beneficial for large collaborations.
-Similarly, the observation that performance is higher in projects with less structural inequality suggests that,
-if the challenges of egalitarian organizing can be overcome,
-decentralized collaborations may produce better outcomes than those with centralized, top-down structures.
-
-Our numerical simulations offer a few additional insights.
-Our proposed local variants of best-neighbor and conformity strategies out-performed
-the standard variants while searching fewer alternatives.
-The higher performance for less work is analogous to the performance increases that
-have been seen for sampling fewer neighbors \cite{barkoczi_social_2016}.
-However, our network is a special case in that its structure is related to the structure of
-the NK model being optimized, which could increase the usefulness of local information.
-Our proposed consensus strategy, intended to model Wikipedia more closely,
-exhibits a degree-dependent performance and efficiency, unlike other strategies.
-This dependence is also seen in our Wikipedia analysis, although performance's dependence has the opposite sign.
-The consensus strategy is also interesting in that it is more efficient and higher performance than the other strategies.
-The unique properties of the consensus strategy may be due to a major difference it has from the others:
-rather than exploring through local hill-climbing,
-the consensus strategy combines parts of existing solutions to create entirely new ones.
-
-Our work has several limitations.
-Our empirical analysis is purely correlative and cannot be used to draw
-conclusions about the causal influence of network structure on collaboration.
-However, the consistency of our results with other lab-based and numerical studies
-suggests that the causal link is worth further study.
-Similarly, our study focuses entirely on a single setting and while it is suggestive,
-does not necessarily generalize,
-and studies of other systems are necessary to corroborate our findings.
-
-Our work raises several questions that could be the subject of future work.
-Is the correlation between network structure, performance, and efficiency causal?
-A time-dependent analysis of our data could offer insight.
-Are similar relationships observed in other large-scale collaborations?
-Does varing degree independently of path length influence performance and efficiency in a controlled
-lab setting?
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-In this paper, we have described the relationship between the structural properties of WikiProject
-coeditor networks and the performance and efficiency of those networks.
-As in other studies, we see a tradeoff between performance and efficiency,
-but not an absolute tradeoff.
-Some properties, such as low degree, are associated with both higher performance and higher efficiency.
-We also find that the correlations between path length and performance are consistent with a conformity-based
-social learning strategy, but not a greedy best-neighbor strategy.
-We also observe improved performance in more decentralized project, as has been seen in small-scale lab experiments.
-While the performance and efficiency of most previously-studied social learning strategies depend more on path lenght than
-degree,
-we have proposed a novel consensus learning strategy that is more realistic, more efficient, and higher performance than
-existing strategies.
-While the efficiency and performance of existing strategies do not exhibit any degree-dependence, our consensus strategy
-demonstrates that degree-dependence is possible.
-While additional work is needed to determine causal relationships and how generalizable our results are,
-we have shown evidence that several phenomena predicted by numerical and small-scale lab experiments are present in a large,
-real-world network.
-And, we have identified new behaviors not explained by existing models, suggesting the need for alternate models.
-Our results suggest that the success of large-scale collaborations may be aided by greater decentralization,
-consensus or conformity-baased decision-making, and more tightly-knit collaborations between smaller teams.
-
-\section{Acknowledgements}
-I would like to thank Daniel M. Romero for valuable guidance and feedback;
-Ceren Budak and Scott E. Page for their time and feedback;
-Danielle Livneh and Karthik Ramanathan for help collecting the data sets;
-Yan Chen and Tanya Rosenblat for feedback on the methodology;
-and the atendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
-the Berkman-Klein Center's Cooperation Working Group for helpful feedback on
-preliminary results.
-This research was funded by the University of Michigan School of Information.
+\input{paper-content.tex}
 
 % ACM
-%\bibliographystyle{ACM-Reference-Format}
-
-% Manuscript
-\bibliographystyle{acm}
+\bibliographystyle{ACM-Reference-Format}
 

### 2017-08-18 paper-content.tex
Add citations.

@@
 and is particularly interesting for its highly decentralized structure with very little top-down control.
-It is notoriously difficult to organize even small groups without top-down control,
-and yet Wikipedia, with millions of editors, somehow functions.
+It is notoriously difficult to organize even small groups without top-down control
+\cite{freeman_tyranny_1972},
+and yet Wikipedia, with millions of self-organized editors,
+has produced a high-quality encyclopedia \cite{giles_internet_2005}.
 A better theoretical understanding of projects like Wikipedia is highly desirable as it could

### 2018-01-05 paper-content.tex
Update for icwsm2018.

@@
 between the two largest eigenvalues of the network's adjacency matrix
-\cite{degroot_reaching_1974, golub_naive_2010}.
+\cite{degroot_reaching_1974,golub_naive_2010}.
 Complex social learning tasks can also be modeled as the problem
@@
 referred to as a {\em rugged landscape}
-\cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, grim_scientific_2013, barkoczi_social_2016}.
+\cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,grim_scientific_2013,barkoczi_social_2016}.
 Numerical simulations have shown that efficient networks (those with short paths between nodes)
 can allow less exploration of possible solutions,
-resulting in a fast convergence to a non-optimal solution \cite{mason_propagation_2008, grim_scientific_2013}.
+resulting in a fast convergence to a non-optimal solution \cite{mason_propagation_2008,grim_scientific_2013}.
 However, when conformity-based social learning strategies are used, efficient networks can outperform
@@
 when the groups are diverse and experienced
-\cite{robert_when_2015}.
+\cite{robert_crowd_2015}.
 Also on Wikipedia,
@@
 Our definitions are inspired by work modeling collective problem-solving as an optimization
-problem \cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012,
-grim_scientific_2013, barkoczi_social_2016}.
+problem \cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,grim_scientific_2013,barkoczi_social_2016}.
 The efficiency quantifies how quickly a solution is reached,
@@
 Following existing numerical work on networked social learning
-\cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, barkoczi_social_2016},
+\cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,barkoczi_social_2016},
 we use the NK model \cite{kauffman_towards_1987} to create NP-hard, nonlinear optimization problems
@@
 \section{Acknowledgments}
-I would like to thank Daniel M. Romero for valuable guidance and feedback;
-Ceren Budak and Scott E. Page for their time and feedback;
-Danielle Livneh and Karthik Ramanathan for help collecting the data sets;
-Yan Chen and Tanya Rosenblat for feedback on the methodology;
-and the attendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
-the Berkman-Klein Center's Cooperation Working Group for helpful feedback on
-preliminary results.
-This research was funded by the University of Michigan School of Information.
+Anonymized for blind review.
+%I would like to thank Daniel M. Romero for valuable guidance and feedback;
+%Ceren Budak and Scott E. Page for their time and feedback;
+%Danielle Livneh and Karthik Ramanathan for help collecting the data sets;
+%Yan Chen and Tanya Rosenblat for feedback on the methodology;
+%and the attendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
+%the Berkman-Klein Center's Cooperation Working Group for helpful feedback on
+%preliminary results.
+%This research was funded by the University of Michigan School of Information.

### 2018-01-06 paper-content.tex
Revisions to background.

@@
 and yet Wikipedia, with millions of self-organized editors,
-has produced a high-quality encyclopedia \cite{giles_internet_2005}.
+has produced a high-quality encyclopedia \cite{giles_internet_2005,keegan_evolution_2017}.
 A better theoretical understanding of projects like Wikipedia is highly desirable as it could
 help inform the design of new collaborative projects.
-We focus on one aspect of organizing a large-scale decentralized collaboration: the network structure.
+We focus on one aspect of organizing a large-scale decentralized collaboration:
+the network structure \cite{newman_structure_2003}.
 If Wikipedia is not structured as a top-down hierarchy, how is it structured?
@@
 each with their own standards, norms, and processes for evaluating and improving articles.
-We analyze the coeditor networks of these projects: which editors have worked together on at least
-one article?
-In particular, we examine the relationship between the structure of a project's coeditor network
-and the performance and efficiency of its articles.
-Performance represents the ability of a project to get articles to a high quality level,
-while efficiency represents the ability to improve articles of any level quickly.
-We also perform numerical simulations to compare the behavior observed on Wikipedia to the results
-of several variants of a simple networked social learning model.
+We focus on the coeditor networks of these projects:
+which editors have edited at least one article in common?
+When measuring the quality of collaborative projects,
+there are at least two distinct measures to consider.
+The first measure is short-term:
+how effective a unit of work is at improving
+the collaboration's output,
+which we call {\em efficiency}.
+The other measure is long-term:
+the highest quality typically reached by an output,
+which we call {\em performance}.
+These two terms are often used interchangably,
+but we find it fruitful to distinguish between the two concepts.
 
@@
 and lower efficiency at reaching the highest quality levels;
-\item Using numerical simulations, we show that the performance and efficiency of some networked learning strategies depends on degree.
+\item Using numerical simulations, we show that the performance and efficiency of some networked learning strategies depends on degree distribution.
 \end{itemize}
@@
 
-In the field of social learning,
-much research has been done to understand how groups of agents
-can solve problems collaboratively.
-In {\em networked social learning}, agents are represented by nodes on a network
+The field of social learning studies how
+groups of interacting agents
+can collaborate to solve complex problems.
+In {\em networked social learning},
+agents are represented by nodes on a network
 and can only interact with their neighbors.
@@
 and those where agents have {\em interpreted signals}
-(solutions based on different internal models of available data)
+(solutions based on different selections of available data)
 \cite{hong_interpreted_2009}.
+The behavior of individual agents is described by their
+{\em social learning strategy}.
 For generated signals,
-a naive Bayesian approach converges to the truth when certain conditions
-on the network's degree distribution are met,
+a naive Bayesian approach converges to the truth
+when all agents have the same degree,
 while the speed of convergence depends on the {\em spectral gap}
@@
 \cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,grim_scientific_2013,barkoczi_social_2016}.
-Numerical simulations have shown that efficient networks (those with short paths between nodes)
-can allow less exploration of possible solutions,
-resulting in a fast convergence to a non-optimal solution \cite{mason_propagation_2008,grim_scientific_2013}.
-However, when conformity-based social learning strategies are used, efficient networks can outperform
+Numerical simulations have shown that efficient networks
+(those with short paths between nodes)
+can result in faster convergence at the cost of a less optimal solution,
+due to less time for exploration
+\cite{mason_propagation_2008,grim_scientific_2013}.
+However, when conformity-based social learning strategies are used,
+efficient networks can sometimes find more optimal solutions than
 inefficient ones \cite{barkoczi_social_2016}.
+The above tradeoff between convergence time, optimality, and learning strategy
+motivates the distinction between performance and efficiency in the current study.
 
@@
 of ``talk,'' it weakens the result of the Condoret jury theorem for voting
-\cite{list_epistemic_2001}.
+\cite{}.
 Robert Michels proposed the ``iron law of oligarchy,''
@@
 
-Research on digital communities has also examined some non-network factors
-influencing the quality of decisions and collaborative work.
+Research on digital communities has also examined the role of factors
+such as diversity and inequality
+in collaborative work and decision-making.
 Using a simulation model, Hong and Page \cite{hong_groups_2004} found that
@@
 perform worse on collaborative tasks \mbox{\cite{kearns_experiments_2012}}.
-In the present project, we examine the effect of structural inequality
-on collaboration in Wikipedia.
+In the present project, we use co-editor network degree skewness to
+examine the relationships between structural inequality,
+project performance, and project efficiency.
 
@@
 article.
+Looking specifically at Wikipedia policies determined by editor consenus,
+Keegan and Fiesler found a trend
+from flexibile rule-making towards less flexible maintenance and deliberation
+\cite{keegan_evolution_2017}.
 

### 2018-01-09 paper-content.tex
Revisions in coeditor network section.

@@
 ``talking'' and ``voting'' stages.
-While hierarchical representative democracy sometimes improves the outcome
-of ``talk,'' it weakens the result of the Condoret jury theorem for voting
-\cite{}.
+% Not yet published
+%While hierarchical representative democracy sometimes improves the outcome
+%of ``talk,'' it weakens the result of the Condoret jury theorem for voting
+%\cite{}.
 Robert Michels proposed the ``iron law of oligarchy,''
@@
 
-Across the broad range of work on collaboration and related topics,
+Across the broad range of work discussed above,
 a few key themes emerge.
 The efficiency and performance of collaborations are important considerations
-and vary depending on both network structure and type of task.
-While social learning predicts no relationship between the two,
-contagion-style innovation models predict a trade-off.
+and vary depending on both network structure and type of task
+\cite{kearns_experiments_2012}.
+While generated signal models of social learning predict no relationship between the two
+\cite{golub_naive_2010},
+contagion-style innovation models predict a trade-off
+\cite{mason_collaborative_2012,barkoczi_social_2016}.
 Such a trade-off has been observed in simulations and lab experiments on
-collaboration.
+collaboration
+\cite{kearns_experiments_2012,grim_scientific_2013}.
+
 In this project, I will investigate several gaps in the existing literature.
 In much of the existing literature,
-degree distribution correlate to performance.
+degree distribution correlates to performance.
 But aside from the naive Bayes case in social learning, it is unknown whether
@@
 This project will also examine Wikipedia for evidence that structural
-inequality (in the form of skewed
-degree distributions) has a detrimental effect on performance,
+inequality (in the form of skewed degree distributions)
+has relationship with performance,
 as has been observed in lab experiments
-\mbox{\cite{kearns_experiments_2012}}.
+\cite{kearns_experiments_2012}.
 
@@
 \label{sec:wp}
+
+Many articles on Wikipedia belong to one or more WikiProject.
+WikiProjects are groups of thematically-related articles
+(e.g., articles related to Philosophy).
+Information about the an article's associated WikiProjects
+can be viewed on that
+article's talk page (Figure \ref{fig:knitting}).
+Each WikiProject has its own page and talk page.
+These pages contain information about community norms within the project
+as well as discussions about individual articles.
+WikiProjects are thus distinct communities, with distinct norms and processes.
+These communities are the fundamental units of analysis in the present paper.
+
+One of the main roles of a WikiProject is to evaluate the quality of its articles.
+Quality assessments are made through consensus-based deliberation on the WikiProject
+talk page.
+Within a WikiProject,
+assessments are typically made using the following {\em assessment classes}
+(in order of increasing quality):
+Stub, Start, C, B, A.
+Different WikiProjects can assign different quality assessments to the same
+article.
+Differences between quality assessments could reflect different quality standards,
+different grading systems, different responsiveness to changes in an article, etc.
+
+In addition to the above assessment classes, articles on Wikipedia can be tagged as
+"good article" (GA) or "featured article" (FA) quality.
+FA and GA determinations are made using a Wikipedia-wide consensus,
+in parallel to any WikiProject-based evaluations.
+FA articles are ``the best articles Wikipedia has to offer''
+\cite{}.
+GA articles meet ``a core set of editorial standards`` but are ``not featured article quality''
+\cite{}.
+When an article is assigned GA or FA status,
+WikiProject quality assessments are often updated to reflect that status.
+For example, the article {\em Mewtwo} was assessed as GA status on October 5,
+2009 and shortly afterwards
+its quality assessment was changed from B to GA within both
+{\em WikiProject Pok\'emon} and
+{\em WikiProject Video Games}.
+This example also illustrates a quirk of Wikipedia norms:
+very often, articles pass to GA or FA directly from B, skipping A.
+The majority of WikiProjects rarely use the A class quality assessment.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=3in]{fig-knitting.png}
+\caption{
+Templates appearing at the top of the English-language Wikipedia talk page
+for {\em Knitting}.
+The article belongs to both {\em WikiProject Technology} and
+{\em WikiProject Textile Arts}.
+Both WikiProjects have assessed the article as B-class quality.
+The article has also been nominated for both good article (GA) and
+featured article (FA) status,
+but after a consensus-based deliberation open to all Wikipedia editors,
+was not assigned GA or FA status.
+\label{fig:knitting}
+}
+\end{center}
+\end{figure}
 
@@
 To get the rating history of each article,
-we wrote a script to scrape the daily logs produced by WP 1.0 Bot for each WikiProject
+we wrote a script to scrape the daily logs produced by WP 1.0 Bot for
+all unique WikiProjects (2279)
 between May 4, 2006 and December 2, 2015.
@@
 
-To model the relationship between performance, efficiency, and network structure,
-we must have a way to quantify performance and efficiency.
-We define these quantities on a per-WikiProject basis to enable comparisons across different
-projects.
-Our definitions are inspired by work modeling collective problem-solving as an optimization
-problem \cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,grim_scientific_2013,barkoczi_social_2016}.
-The efficiency quantifies how quickly a solution is reached,
-while the performance quantifies how good the eventual solution is.
+When individuals collaborate to solve a problem,
+there are many ways to gauge their success.
+Two possibilities are
+1. how quickly they find a solution, and
+2. how good their solution is.
+Evidence from numerical simulations
+\cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,grim_scientific_2013,barkoczi_social_2016},
+lab studies \cite{kearns_experiments_2012},
+and field observations \cite{gentry_consensus_1982}
+all suggest a trade-off between performance and efficiency.
+While common, this trade-off is not absolute,
+suggesting it is sometimes possible to simultaneously increase
+performance and efficiency.
+The identification of factors associated with both higher efficiency
+and higher performance has obvious practical importance.
+In this paper, we focus specifically on how network structure
+relates to efficiency and performance within WikiProjects.
 
-For a WikiProject, efficiency quantifies how quickly project participants can improve the
-assessed quality of an article.
+For a WikiProject, efficiency quantifies how much participants can raise the
+assessed quality of an article for a fixed amount of work.
+We measure work by the number of revisions made.
 Quality assessments are made through consensus of the project participants themselves,
@@
 need to be made and make those improvements.
-Because our definition relies on assessment transitions, we define efficiency variables for
+Because our definition relies on assessment transitions,
+we must define efficiency variables for
 each of the project-level quality assessments: A, B, and C.
-If $T(W,G)$ is the set of transitions in project $W$ from below grade $G$ to grade $G$ (or higher),
-then we first quantify the efficiency $E(W,G)$ as the inverse of the mean number of revisions
+For a particular grade $G$,
+we desire our definition of efficiency to meet the following conditions:
+\begin{itemize}
+\item{Strictly increasing in the number of articles reaching grade $G$ (with revision count fixed);}
+\item{Strictly decreasing in the number of revisions (with transition count fixed);}
+\item{Independent of WikiProject size: not affected by adding an article if that article's transition/revision ratio is equal to the efficiency.}
+\end{itemize}
+
+We now define an efficiency measure which meets the above criteria.
+Let $T(W,G)$ be the set of article assessment transitions from below grade $G$
+to grade $G$ or higher in project $W$.
+Let $N(W,G)$ be the number of articles in project $W$ which ever transition
+from below grade $G$ to grade $G$ (or higher).
+Let $r(t)$ be the number of article revisions since its previous grade transition,
+and let $g(t)$ be the number of grade levels crossed by transition $t$.
+We quantify the efficiency $E(W,G)$ as the inverse of the mean number of revisions
 per transition:
@@
 \frac{1}{
-|T(W,G)|
+N(W,G)
 }
@@
 \eeq
-where $r(t)$ is the number of revisions since the previous grade transition,
-and $g(t)$ is the number of grade levels crossed by transition $t$.
-The $g(t)$ term is added because an assessments often raise article quality by several
-grades, in which case the revisions are divided evenly between all grade levels achieved.
-It is also worth noting that we measure efficiency in terms of revisions made,
-rather than time passed.
-We focus on revisions because the amount of work done on an article varies widely from day to day.
+Where the $g(t)$ term is present because a assessments sometimes raise article quality by several
+grades, in which case we divide the revisions evenly between all grade levels achieved.
 
@@
 In other words, the good and featured statuses are more objective than per-project assessments.
-Our performance measure $P(W)$ is just the percentage of articles in project $W$ which have reached
+
+Our performance measure $P(W)$ is defined simply as
+the percentage of articles in project $W$ which have reached
 good or featured status:
@@
 
-For each WikiProject, we compare the efficiency and performance measures to the structural
-properties of its coeditor network.
-The {\em coeditor network} of a WikiProject consists of nodes representing editors.
-Two editors are connected when they have both edited the same article or talk page.
+We would like to determine how the social network structure of
+Wikipedia--the pattern of who interacts with whom--relates to
+efficiency and performance.
+There are several types of interactions we could focus on,
+including:
+coediting, user talk messages, and talk page replies.
+We choose to focus on coediting: when two editors have made changes to the
+same article or talk page.
+While editors can communicate directly through user talk messages,
+the number of such messages is small compared to the number of edits to article
+and talk pages.
+We also could have considered direct replies between editors on article talk
+pages, but these replies are typically seen (and intended to be seen)
+by everyone reading the talk page,
+and are part of larger conversations.
+When an editor views a page,
+they are potentially viewing content from and interactions
+between all editors who came before them,
+motivating our choice to focus on the social network structure of
+coeditors.
+
+The {\em coeditor network} of a WikiProject consists of nodes representing editors,
+and edges connecting any editors who have edited the same article.
 The edges are directed, with the direction representing the direction of
 {\em plausible information flow};
-an edge from editor A to editor B exists if A edited an article and then B edited the same article at
+an edge from Alice to Bob exists if Alice edited an article and then Bob edited the same article at
 a later time.
-Edges can exist in both directions e.g., if an article was edited first by A, then by B, and again by A.
-For simplicity, we assign all edges unit weight.
-We focus on three structural properties: degree, characteristic path length, and min-cut.
+Edges can exist in both directions e.g.,
+if an article was edited first by Alice, then by Bob, and again by Alice.
+We make the simplifying assumption of unit weight for all edges.
+We focus on three structural properties:
+degree, characteristic path length, and min-cut.
+Degree and characteristic path length have been shown to correlate with
+performance and efficiency in some social learning settings
+\cite{golub_naive_2010,mason_propagation_2008,grim_scientific_2013},
+while min-cut can be interpreted as a measure of decentralization,
+a key property of Wikipedia.
 
-The node degree distribution is the simplest structural property we analyze for WikiProject
-coeditor networks.
+The degree distribution is the simplest network property we analyze.
 The in-degree (out-degree) of a node is the number of edges to (from) that node.

### 2018-01-09 paper-content.tex
Revise coeditor networks, and empirical results.

@@
 
-Empirically, we find that both efficiency and performance are highly right-skewed,
-with a small number of projects having values much higher than the average.
-After log-transforming the values, both the efficiency and the performance have
-a unimodal distribution with low skew (see Figure \ref{fig:eff-perf-hist}).
-
 \subsection{Coeditor Networks}
@@
 while min-cut can be interpreted as a measure of decentralization,
-a key property of Wikipedia.
+common feature of peer-produced communities such as Wikipedia
+\cite{benkler_wealth_2006}.
 
@@
 We also calculate the characteristic path length for each WikiProject coeditor network.
-The {\em distance} from editor A to editor B is the length of the shortest path from A to B.
-The {\em characteristic path length} is the mean distance between all editor pairs.
-If no path exists between two editors, we exclude that pair from the mean.
-For brevity, we will simply refer to this quantity as the {\em path length}.
+The {\em distance} from node $s$ to node $t$ is the distance of the shortest path
+from $s$ to $t$.
+The {\em characteristic path length} (or just {\em path length} for brevity)
+is the mean distance between all editor pairs,
+excluding unconnected pairs.
+To account for unconnected pairs, we also measure the {\em connected fraction}
+of all possible edge pairs.
 The path length represents how quickly information can move through the network.
@@
 Even with sampling, however, it was impractical to calculate these properties for the largest projects,
-so we exclude them from the analysis.
+so we exclude the 183 largest projects from the analysis.
 To control for bias in project size, we include several size-related variables in our models.
 
-\subsection{Regression Models}
+\subsection{Empirical Results}
+
+We find that both efficiency and performance are highly right-skewed,
+with a small number of projects having values much higher than the average.
+After log-transforming the values, both the efficiency and the performance have
+a unimodal distribution with low skew (see Figure \ref{fig:eff-perf-hist}).
+
+We also find that mean min-cut is highly correlated with degree ($r=0.980$, $p<0.001$),
+so we exclude min-cut from regression models to prevent collinearity (see Figure \ref{fig:degree-mincut}).
+The high correlation between mean degree and min-cut implies that in most cases
+the minimum $st$-cut is simply the either set of edges from $s$ or the set of edges to $t$.
+The rarity of non-trivial min-cuts suggests that WikiProject coeditor networks have very few central
+bottlenecks and are thus highly decentralized.
+
+\begin{figure}
+\centering
+\includegraphics[width=3in,height=3in]{fig-eff-perf-hist.pdf}
+\caption{
+Histograms of WikiProject efficiency and performance.
+Both measures are highly right-skewed, but form unimodal distributions
+with low skewness after log transformation.
+\label{fig:eff-perf-hist}
+}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=2.33in,height=2.33in]{fig-degree-mincut.pdf}
+\caption{
+Min-cut of WikiProject coeditor networks vs. their mean degree.
+\label{fig:degree-mincut}
+}
+\end{figure}
 
@@
 
-We model performance and efficiency in WikiProjects using ordinary least-squares linear regression.
+To study the relationship between network structure, efficiency, and performance,
+we model the performance and efficiency of WikiProjects using ordinary least-squares linear regression.
 Each WikiProject is taken as a single observation.
 The models include each project's coeditor network properties as independent variables.
-We also include several project-level variables to control for confounding factors.
-The C-efficiency is included in the model for performance to control for the presence of articles
-that are actively being improved.
-Projects with lower efficiency will have more works-in-progress and could have an artificially low
-performance without controlling for efficiency.
-Some variables are log-transformed to reduce heteroscedasticity.
+We also include several project-level variables to control for confounding factors,
+described below.
+\begin{description}
+\item[C-efficiency] Quantifies how quickly a WikiProject improves low-quality articles.
+\item[Connected fraction] Fraction of coeditor pairs connected by a path.
+\item[Mean editors/article] Mean number of editors collaborating on each article in a WikiProject.
+\item[Article count] Total number of articles in the WikiProject.
+\item[Editor count] Total number of editors working on articles within a WikiProject.
+\item[Revision count] Total number of revisions to articles in a WikiProject.
+\item[First assessment] Timesamp of first assessment; a measure of how long a WikiProject has been active.
+\item[Mean article age] Mean age of articles within a WikiProject.
+\item[Mean similarity] Mean Jaccard similarity (by article) with other WikiProjects; a measure of topical complexity.
+\end{description}
 
 Our models are summarized in Table \ref{tab:model}.
-Mean min-cut was found to be highly correlated with degree ($r=0.980$, $p<0.001$),
-so we exclude min-cut to prevent collinearity (see Figure \ref{fig:degree-mincut}.
-The high correlation between mean degree and min-cut implies that in most cases
-the minimum $st$-cut is simply the either set of edges from $s$ or the set of edges to $t$.
-The rarity of non-trivial min-cuts suggests that WikiProject coeditor networks have very few central
-bottlenecks and are thus highly decentralized.
-In-degree and out-degree skewness were also highly correlated, so each dependent variable was modeled twice:
-once with in-degree skewness and once with out-degree skewness.
+Min-cut is excluded from all models to avoid collinearity,
+as it is highly correlated with degree.
+In-degree and out-degree skewness were also highly correlated,
+so we only include out-degree skewness in the models.
+Some variables are log-transformed.
+To test the robustness of our results,
+we also computed models using cube root instead of logarithmic transformations,
+as well as using only top-importance and high-importance articles.
+These robustness check yielded qualitatively similar results for all variables,
+except for degree-skewness, which had an inconsistent sign across models.
 
-\begin{figure}
-\centering
-\includegraphics[width=3in,height=3in]{fig-eff-perf-hist.pdf}
-\caption{
-Histograms of WikiProject efficiency and performance.
-Both measures are highly right-skewed, but form unimodal distributions
-with low skewness after log transformation.
-\label{fig:eff-perf-hist}
-}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=2.33in,height=2.33in]{fig-degree-mincut.pdf}
-\caption{
-Min-cut of WikiProject coeditor networks vs. their mean degree.
-\label{fig:degree-mincut}
-}
-\end{figure}
-
-The regression results are consistent whether in-degree or out-degree skewness is used,
-although the out-degree models are slightly more significant when modeling efficiency.
-We also see that B-efficiency and C-efficiency have very similar models, but that A-efficiency behaves
+We see that B-efficiency and C-efficiency have very similar models, but that A-efficiency behaves
 differently in its dependence on degree skewness and connectivity.

### 2018-01-11 paper-content.tex
Revisions to agent-based model sec.

@@
 
-\section{Numerical Simulations}
+\section{Agent-Based Model}
 \label{sec:sim}
 
-We use numerical simulations to determine whether simple models can reproduce the behavior we
-observe in WikiProject coeditor networks.
-Following existing numerical work on networked social learning
-\cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,barkoczi_social_2016},
-we use the NK model \cite{kauffman_towards_1987} to create NP-hard, nonlinear optimization problems
-and evaluate the effects of network structure and learning strategy on a group's ability to
-find solution to those problems.
-We are particularly interested in the effect of degree on the efficiency and performance of a group
-of networked problem-solving agents.
+In addition to our empirical study,
+we use a simple agent-based model of collaboration to better understand
+the relationship between node degree, efficiency, and performance.
+Numerical models allow us to determine the effect of changing a single
+variable (e.g., network strucutre, learning strategy),
+which is impractical in the empirical setting.
+It is important to note that the goal of our model is not to create an
+accurate simulation of Wikipedia or any other specific platform.
+Rather, our goal is to simulate collaboration in the abstract so that we can
+examine the results of altering various assumptions and parameters.
 
-In the NK model, N loci each have a binary state and value determined by a random lookup table mapping its state
-and the state of another K loci to a real number in $[0,1]$.
-We report results for the case $N=250$, $K=7$.
-Solutions thus take the form of an N-bit string, and the value of the solution is the mean over all loci values.
+Past work in the field of social learning typically models collaboration
+as an optimization problem:
+finding a state of the world which maximizes some objective function
+\cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,barkoczi_social_2016}.
+Wikipedia itself can be regarded as an optimization problem.
+On Wikipedia, editors are generally seeking to improve the quality of articles
+and have some personal preference over possible states of an article.
+When editors do not agree on the optimal state of an article,
+the conflict is resolved through a consensus-based deliberation.
+This consensus process can be regarded as a {\em social choice function}
+\cite{arrow_social_2012,brandt_computational_2012}
+which maps individual preferences to community preferences.
+Wikipedia can thus be thought of as a group of editors with individual preferences
+for article states,
+collaborating to optimize articles according to community preferences.
+
+To simulate collaboration, we need a model problem for collaborators to solve.
+Following existing literature on social learning,
+we use the NK model \cite{kauffman_towards_1987}
+to create NP-hard, nonlinear optimization problems.
+The NK model produces an objective function with a
+{\em rugged landscape}, i.e., many local optima.
+The ruggedness of the model can be tuned through the parameters $N$ and $K$.
+Formally, the NK model produces a function $F$ mapping a binary string $S$ of length
+$N$ to a real value in $[0,1]$.
+The model consists of $N$ {\em loci}, with locus $i$ having a binary state $S_i$
+and a value $f_i(S)$ dependent on its own state
+and on the state of $K$ random other loci.
+The functions $f_i(S)$ are created by selecting a random value in $[0,1]$ for
+each possible state of locus $i$ and its $K$ neighbors.
+The value of the model $F(S)$ is the mean of all locus values $f_i(S)$.
+In our models,
+agents thus seek to find a bit string $S$ that achieves the largest $F(S)$.
+
+In a typical social learning model,
+a set of agents each maintain an estimate of the optimal state
+and update that estimate based on information available from other agents,
+according to some {\em learning strategy}.
+In networked social learning,
+agents are associated with the nodes of a network and share information
+only with their neighbors.
 
 For a particular problem-solving trial, agents each store their current favored solution and
-apply learning strategies to iteratively improve those solutions. We define their
-efficiency and performance in terms of the mean solution values for each time step.
+apply learning strategies to iteratively improve those solutions.
+We define their efficiency and performance in terms of the mean solution values for each time step.
 We define the performance to be the mean solution value after the process has converged,
@@
 
-\subsection{Learning Strategies}
+While the above model is often used to study collaboration,
+several key properties of real-world collaborations are missing
+without additional constraints.
+In designing our agent-based model, we paid attention to the
+following properties, motivated by real-world collaborations.
+\begin{description}
+\item[Limited concern] Agents are concerned only with a subset of the entire
+state when making decisions and determining preferences.
+\item[Concern-based network] Agents interact with other agents who share a
+common concern over some subset of the state.
+\item[Unknown objective] Agents can rank states in order of preference,
+but do not have access to the objective function.
+\item[Single source of truth] At any given time, the system is in a single state
+and agent preferences are based on local modifications to that state.
+\end{description}
+
+\subsection{Concern-Based Networks}
+
+On Wikipedia, editors interact by editing articles and talk pages.
+Thus, the editors who interact with each other are exactly those who care about the same pages.
+Rather than using arbitrary networks,
+we devise a network structure inspired by the above observation.
+We do so by associating agents with particular loci in the NK model.
+We also wish to study the effect of varying network degree,
+which we achieve through a rewiring process described below.
+
+Our concern-based networks are generated directly from the structure of the NK model.
+The value of each NK locus depends on its own state and the state of $K$ other loci.
+For each locus, we define an agent and assign these $K+1$ loci as its concern.
+Next, an agent-agent co-affiliation network is created by connecting two agents if they share at least
+one locus in their concerns.
+This process is analogous to our construction of WikiProject coeditor networks.
+
+To create a tunable degree, we duplicate each agent and its concern,
+then randomly rewire a fraction of agent concerns before creating the agent-agent network.
+With no rewiring, the duplication process creates a high overlap between agent concerns.
+This overlap results in redundant links to a small number of agents,
+rather than unique links to a large number of agents,
+and therefore to an agent-agent network with small average degree.
+By randomly rewiring the agent concerns, the redundancy is reduced and the average degree of
+the agent-agent network is increased.
+
+\subsection{Networked Learning Strategies}
 
@@
 
-We introduce a new strategy, which we call the consensus strategy.
-In {\em consensus}, agents first apply individual learning.
-Next, a consensus solution is constructed from each agent's individual solution by setting
-each NK locus's state to its most common value among the agent's individual solutions.
-The result of this process is that agents accept a single consensus solution at each iteration,
-which forms the basis for future individual learning.
-We include this strategy because of its similarity to the editing process of Wikipedia:
-at any given time, a Wikipedia article has a single state, determined by consensus,
-but editors may have differing opinions on how to improve that article.
-
 We also introduce local variants of the above strategies.
@@
 
-\subsection{Network family}
+\subsection{Consensus Strategy}
 
-The agent networks used in our simulations vary from those in previous work in two important ways:
-they reflect the structure of the NK model being optimized,
-and they allow the degree to be tuned with minimal change to the mean path length.
-
-Our networks are generated by first creating an agent node for each NK locus.
-Each node is assigned a concern consisting of its associated locus and all loci its value depends on,
-as in the local learning strategies.
-This procedure forms an agent-locus affiliation network.
-Next, an agent-agent co-affiliation network is created by connecting two agents if they share at least
-one locus in their concerns.
-This process is exactly analogous to our definition of a WikiProject coeditor network,
-with agents playing the role of editors and NK loci playing the role of Wikipedia articles.
-
-To create a tunable degree, we duplicate each node and its node-locus edges and then
-randomly rewire those edges before creating the agent-agent network.
-The duplication process creates a high overlap between agent concerns,
-meaning that most agent-locus edges are redundant and do not create additional agent-agent edges,
-resulting in a low average degree.
-By randomly rewiring the agent-locus edges, the redundancy is reduced and the average degree of
-the agent-agent network is increased.
+We introduce a new strategy, which we call the consensus strategy.
+In {\em consensus}, agents first apply individual learning.
+Next, a consensus solution is constructed from each agent's individual solution by setting
+each NK locus's state to its most common value among the agent's individual solutions.
+The result of this process is that agents accept a single consensus solution at each iteration,
+which forms the basis for future individual learning.
+We include this strategy because of its similarity to the editing process of Wikipedia:
+at any given time, a Wikipedia article has a single state, determined by consensus,
+but editors may have differing opinions on how to improve that article.
 

### 2018-01-11 paper-content.tex
Update learning strategies.

@@
 a set of agents each maintain an estimate of the optimal state
-and update that estimate based on information available from other agents,
+and iteratively update that estimate based on information available from other agents,
 according to some {\em learning strategy}.
@@
 only with their neighbors.
-
-For a particular problem-solving trial, agents each store their current favored solution and
-apply learning strategies to iteratively improve those solutions.
-We define their efficiency and performance in terms of the mean solution values for each time step.
+We define efficiency and performance in terms of the solution values for each time step
+(averaged over many trials).
 We define the performance to be the mean solution value after the process has converged,
@@
 
-While the above model is often used to study collaboration,
-several key properties of real-world collaborations are missing
-without additional constraints.
+Without additional constraints,
+the above model is missing
+several key properties of real-world collaborations.
 In designing our agent-based model, we paid attention to the
@@
 On Wikipedia, editors interact by editing articles and talk pages.
-Thus, the editors who interact with each other are exactly those who care about the same pages.
+Thus, the editors who interact with each other are exactly those who care about the same content.
 Rather than using arbitrary networks,
@@
 and therefore to an agent-agent network with small average degree.
-By randomly rewiring the agent concerns, the redundancy is reduced and the average degree of
-the agent-agent network is increased.
+By randomly rewiring the agent concerns, the redundancy is reduced
+and the average degree of the agent-agent network is increased.
 
@@
 
-Agents can engage in individual learning by applying a hill-climbing algorithm to their current solution.
+Learning strategies determine how agents update their preferences based on
+available information.
+Agents can engage in individual learning \cite{barkoczi_social_2016}
+by applying a hill-climbing algorithm to their current solution.
 In each iteration, one bit of the NK solution string is flipped to maximize the solution value.
-If no change improves the value, the original solution is kept.
-Agents can also incorporate information from any other agents they are connected to by a network edge.
+If no change improves the value, the original solution is kept
+The above strategy relies only on rankings of states,
+satisfying the unknown objective assumption.
+However, it does rely on information about the entire state,
+violating the limited concern assumption.
+In order to satisfy this assumption,
+we also define a local variant
+in which only a subset of bits in the NK solution string are considered.
+This variant reflects a more realistic style of collaboration,
+in which individual agents focus on sub-problems.
+
+In social learning,
+agents can also incorporate information from
+other agents they are connected to by a network edge.
 While individual learning always converges to the local maximum relative to the starting point,
 social learning strategies allow agents to ``jump'' to drastically different solutions with higher local maxima.
-
-We use both the conformity and best-neighbor strategy from \cite{barkoczi_social_2016}.
-In the {\em best-neighbor} strategy, each agent compares its solution to the those of all its
+In our model, we use both the conformity and best-neighbor strategies from \cite{barkoczi_social_2016}.
+In the {\em best-neighbor} strategy, each agent compares its solution to a sample of its
 neighbors, and chooses the solution with the highest value.
+In order to compare solutions between neighbors,
+the exact value of the objective function must be known for each solution,
+so this strategy does not satisfy the unknown objective assumption
+or the limited concern assumption.
 In the {\em conformity} strategy, agents simply choose the most common solution among their neighbors
 (ties are broken uniformly at random).
+This strategy does not rely on solution value at all, so clearly satisfies the
+unknown objective assumption,
+but it fails to satisfy the limited concern assumption because it updates all
+bits of the NK solution.
 In both cases, a single iteration of individual learning is performed after each social learning
 iteration.
-
-We also introduce local variants of the above strategies.
-The local variants are meant to reflect a more realistic collaboration setting where
-individual agents focus on sub-problems.
-In these variants, individual learning takes place on a subset of NK loci.
-Each agent is associated with an NK locus and the loci its value depends on.
-These loci are the agent's {\em concern},
-and are the only ones used for individual learning.
-Similarly, in the consensus strategy, an NK locus's value is determined only by the agents
-concerned with that locus, rather than all agents.
-
-\subsection{Consensus Strategy}
-
-We introduce a new strategy, which we call the consensus strategy.
-In {\em consensus}, agents first apply individual learning.
-Next, a consensus solution is constructed from each agent's individual solution by setting
-each NK locus's state to its most common value among the agent's individual solutions.
-The result of this process is that agents accept a single consensus solution at each iteration,
-which forms the basis for future individual learning.
-We include this strategy because of its similarity to the editing process of Wikipedia:
+Because each agent maintains a separate estimate of the solution,
+neither of these strategies satisfies the single source of truth assumption.
+
+\subsection{Local Majority Strategy}
+
+In order to satisfy the single source of truth assumption,
+we introduce a new strategy, which we call the local majority strategy.
+In {\em local majority}, agents begin with exactly the same starting state,
+and apply individual learning to their concern to generate
+possible improvements to the solution.
+Next, a new solution is constructed by considering each locus of the NK solution
+individually.
+Every agent concerned with a bit votes for its state based on their preferred
+new solution and the majority state is chosen.
+The result of this process is that all agents agree on a single improved state,
+which forms the basis for the next iteration.
+This strategy more realistically reflects collaborations like Wikipedia:
 at any given time, a Wikipedia article has a single state, determined by consensus,

### 2018-01-12 paper-content.tex
Update empirical tables and figures.

@@
 
-\begin{table*}[!ht]
+\begin{table}
 \small
@@
 \begin{tabular}{lllllllll}
+&Perf$^\dagger$&A-Eff$^\dagger$&B-Eff$^\dagger$&C-Eff$^\dagger$\\
 \hline
-                               & Perf$_1^\dagger$ & Perf$_2^\dagger$ & A-Eff$_1^\dagger$ & A-Eff$_2^\dagger$ & B-Eff$_1^\dagger$ & B-Eff$_2^\dagger$ & C-Eff$_1^\dagger$ & C-Eff$_2^\dagger$ \\
+Mean degree$^\dagger$&-0.7$^{***}$&-0.8$^{***}$&-0.6$^{***}$&-0.3$^{*}$\\
+Out degree skew$^\dagger$&-0.4$^{***}$&-0.5$^{**}$&-0.3$^{*}$&-0.06\\
+Mean path length$^\dagger$&-0.33$^{***}$&-0.09&-0.05&-0.09\\
+C-Efficiency$^\dagger$&-0.08$^{*}$&\+---&\+---&\+---\\
+Connected frac.&0.01&0.09$^{*}$&0.15$^{***}$&0.06\\
+Talk fraction$^\dagger$&0&-0.02&-0.03&0.01\\
+Mean similarity$^\dagger$&0.06$^{**}$&-0.03&0.01&0.02\\
+Mean editors/art.$^\dagger$&0.3$^{**}$&0.3&0.2$^{*}$&0.09\\
+Article count$^\dagger$&-0.4&0.7$^{*}$&0.8$^{**}$&0.7$^{**}$\\
+Editor count$^\dagger$&0.4&0.9$^{**}$&0.8$^{**}$&0.5$^{*}$\\
+Revision count$^\dagger$&0.6$^{*}$&-1$^{**}$&-1.1$^{***}$&-1$^{***}$\\
+First assessment&0.05&0.11$^{**}$&0.31$^{***}$&0.43$^{***}$\\
+Mean article age&-0.03&-0.04&-0.01&-0.05$^{*}$\\
 \hline
-Mean degree$^\dagger$          &  -0.84$^{***}$  &  -0.78$^{***}$
-                               &  -0.61$^{**}$   &  -0.84$^{***}$
-                               &  -0.50$^{***}$  &  -0.61$^{***}$
-                               &  -0.34$^{**}$   &  -0.31$^{*}$ \\
-In-degree skewness$^\dagger$   &  -0.58$^{***}$  & \+ ---      
-                               &  -0.43$^{**}$   & \+ ---      
-                               &  -0.19          & \+ ---      
-                               &  -0.1           & \+ ---      \\
-Out-degree skewness$^\dagger$  &  \+ ---         &  -0.48$^{***}$  
-                               &  \+ ---         &  -0.57$^{***}$
-                               &  \+ ---         &  -0.26$^{*}$
-                               &  \+ ---         &  -0.066 \\
-Mean path$^\dagger$            &  -0.357$^{***}$ &  -0.356$^{***}$ 
-                               &  -0.026         &  -0.096
-                               &  -0.020         &  -0.045
-                               &  -0.092$^{**}$  &  -0.086 \\
-C-eff$^\dagger$                &  -0.083$^{**}$  & -0.085$^{**}$  
-                               &  \+ ---         & \+ ---      
-                               &  \+ ---         & \+ ---      
-                               &  \+ ---         & \+ --- \\
-Connectivity                   & \+0.018         & \+0.016        
-                               & \+0.081         & \+0.088
-                               & \+0.126$^{***}$ & \+0.142$^{***}$
-                               & \+0.080$^{**}$  & \+0.081$^{**}$ \\
-Mean editors/article$^\dagger$ & \+0.37$^{***}$  & \+0.40$^{***}$ 
-                               & \+0.22          & \+0.27
-                               & \+0.20          & \+0.22$^{*}$
-                               & \+0.076         & \+0.075 \\
-Article count$^\dagger$        &  -0.32          & -0.27          
-                               & \+0.63${^*}$    & \+0.70${^*}$ 
-                               & \+0.76$^{**}$   & \+0.78$^{**}$
-                               & \+0.67$^{***}$  & \+0.67$^{***}$ \\
-Editor count$^\dagger$         & \+0.68$^{*}$    & \+0.48         
-                               & \+0.74$^{*}$    & \+0.97$^{**}$
-                               & \+0.60$^{*}$    & \+0.72$^{**}$
-                               & \+0.52$^{*}$    & \+0.46$^{*}$ \\
-Revision count$^\dagger$       & \+0.37          & \+0.39         
-                               &  -0.84$^{**}$   & -0.88$^{**}$
-                               &  -1.05$^{***}$  & -1.05$^{***}$
-                               &  -1.00$^{***}$  & -1.00$^{***}$ \\
-First assessment               & \+0.028         & \+0.058        
-                               & \+0.086$^{*}$   & \+0.101$^{**}$
-                               & \+0.309$^{***}$ & \+0.321$^{***}$
-                               & \+0.456$^{***}$ & \+0.460$^{***}$ \\
-Mean article age               &  -0.040         & -0.029         
-                               &  -0.049         & -0.037
-                               &  -0.019         & -0.014
-                               &  -0.046$^{*}$   & -0.045$^{*}$ \\
-\hline
-DoF                            & 1278            & 1278          
-                               & 1048            & 1048
-                               & 1371            & 1371
-                               & 1540            & 1540 \\
-R$^2_{adj}$                    & 0.37            & 0.37          
-                               & 0.15            & 0.16
-                               & 0.30            & 0.30
-                               & 0.43            & 0.43 \\
+N&1179&966&1260&1415\\
+R$^2_{adj}$&0.37&0.17&0.30&0.43\\
 \hline
@@
 \end{tablenotes}
-\end{table*}
+\end{table}
 
@@
 \item[Connected fraction] Fraction of coeditor pairs connected by a path.
+\item[Talk fraction] Fraction of total revisions made to talk pages.
 \item[Mean editors/article] Mean number of editors collaborating on each article in a WikiProject.
@@
 collaborating to optimize articles according to community preferences.
+Note that these community preferences don't assume the existence of any
+ground truth, other than the preferences themselves.
 
@@
 This strategy does not rely on solution value at all, so clearly satisfies the
-unknown objective assumption,
-but it fails to satisfy the limited concern assumption because it updates all
-bits of the NK solution.
+unknown objective and limited concern assumptions.
 In both cases, a single iteration of individual learning is performed after each social learning
@@
 we introduce a new strategy, which we call the local majority strategy.
-In {\em local majority}, agents begin with exactly the same starting state,
+In {\em local majority}, agents all begin with the same starting state,
 and apply individual learning to their concern to generate
@@
 
+\begin{table*}
+\small
+\centering
+\caption{
+Social learning strategies
+\label{tab:strat}
+}
+\bigskip
+\begin{tabular}{lccccc}
+Name          & Social & Individual & Limited concern & Unknown objective & Single truth \\
+\hline
+Best+I & Best neighbor   & Global & & & \\
+Conf+I & Conformity      & Global & & \Checkmark & \\
+Best+LI & Best neighbor  & Local  & \Checkmark & & \\
+Conf+LI & Conformity     & Local  & \Checkmark & \Checkmark & \\
+LMaj+LI & Local majority & Local  & \Checkmark & \Checkmark & \Checkmark \\
+\hline
+\end{tabular}
+\end{table*}
+
 \subsection{Simulation results}
@@
 For each trial we generated an NK model with N=250 and K=7 and ran each social learning strategy
-for 300 iterations,
+(Table \ref{tab:strat}) for 300 iterations,
 as well as a network based on that NK model and rewired.
+For conformity and best-neighbor strategy, we used a sample size of 3, following
+\cite{barkoczi_social_2016}.
 We confirmed that all trials converged to their maximum value before reaching the last iteration.
@@
 \begin{tabular}{lcc}
-\hline
 Property          & Mean  & Std. Dev. \\
@@
 \begin{tabular}{llc}
-\hline
 Strategy & Std. Coeff. \\

### 2018-01-12 paper-content.tex
Update nk figure.
Update tables for nk.

@@
 \begin{tabular}{lccccc}
-Name          & Social & Individual & Limited concern & Unknown objective & Single truth \\
+Name          & Social stage & Individual stage & Limited concern & Unknown objective & Single truth \\
 \hline
@@
 \hline
-Mean Degree       & 132.3 & 9.2 \\
-Mean Path length  & 1.735 & 0.019 \\
+Mean Degree       & 116.6 & 1.3 \\
+Mean Path length  & 1.766 & 0.0027 \\
 \hline
@@
 \begin{figure}
-\includegraphics[width=3in,height=1.5in]{fig-val-iter.pdf}
+\centering
+\includegraphics[width=2.5in,height=5in]{fig-val-iter.pdf}
 \caption{
 Mean agent solution value over time, averaged over 100 trials.
-The left and right figures show results for agent networks with the probability of
+The top and bottom figures show results for agent networks with the probability of
 rewiring set to 0 and 1, respectively.
-In both, local strategies are less efficient and more performant than non-local.
-The consensus strategy is both more efficient and more performant than others,
-with its performance increasing with higher rewiring.
+In both, local strategies are less efficient than their non-local counterparts.
+Local best-neighbor out-performs global,
+while local conformity is the worst performer in all cases.
+The local majority strategy is both more efficient and more performant than others.
 \label{fig:val-iter}
@@
 \caption{
-Efficiency regression coefficients.
-\label{tab:sim-eff}
+Degree regression coefficients for agent-based models.
+\label{tab:sim-perf}
 }
@@
 \bigskip
-\begin{tabular}{llc}
-Strategy & Std. Coeff. \\
+\begin{tabular}{lll}
+Strategy & Perf. Std. Coeff. & Eff. Std. Coeff.\\
 \hline
-Best-neighbor       & -0.064 \\
-Conformity          & -0.080 \\
-Local best-neighbor & -0.086 \\
-Local conformity    & \+0.049 \\
-Consensus           & -0.0325$^{***}$ \\
+Best+I  & -4.2$\times{10^{-5}}$ & \+4.1$\times{10^{-5}}$ \\
+Conf+I  & \+2.7$\times{10^{-5}}$ & \+9.4$\times{10^{-5}}$ \\
+Best+LI & -9.6$\times{10^{-4\;**}}$ & \+7.7$\times{10^{-5}}$ \\
+Conf+LI & -1.5$\times{10^{-3\;***}}$ & \+8.7$\times{10^{-5\;*}}$ \\
+LMaj+LI & \+1.2$\times{10^{-4\;**}}$ & -0.038$^{***}$ \\
 \hline
@@
 
-\begin{table}
-\small
-\caption{
-Performance regression coefficients.
-\label{tab:sim-perf}
-}
-\centering
-\bigskip
-\begin{tabular}{llc}
-Strategy & Std. Coeff. \\
-\hline
-Best-neighbor       & \+0.084 \\
-Conformity          & \+0.130 \\
-Local best-neighbor & -0.080 \\
-Local conformity    & -0.020 \\
-Consensus           & \+2.38$\times{10^{-4\;**}}$ \\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item \centering * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
-\end{tablenotes}
-\end{table}
-
 \begin{figure*}
@@
 \caption{
-Efficiency and Performance of social learning strategies vs network degree.
+Efficiency and Performance of social learning strategies vs. network degree.
 Each point represents a single trial of 300 iterations.
-The consensus strategy shows increased performance and decreased efficiency as
-degree increases, while other strategies show no degree dependence.
+The local best-neighbor strategy shows
+decreased performance at high degree,
+with no significant change in efficiency.
+Local conformity shows decreased performance and increased efficiency at high
+degree.
+Local majority shows the opposite behavior:
+increased performance and decreased efficiency at high degree,
+with the efficiency showing the largest effect size of all strategies.
 \label{fig:deg-eff-perf}
@@
 The effect of degree on performance and efficiency is shown in Figure \ref{fig:deg-eff-perf} and
-Tables \ref{tab:sim-eff} and \ref{tab:sim-perf}.
+Table \ref{tab:sim-perf}.
 For both local and non-local versions of the best-neighbor and conformity strategies,

### 2018-01-12 paper-content.tex
Layout.

@@
 and the performance and efficiency of those networks.
-We also perform numerical simulations to determine whether social learning on an NK model can
+We also perform agent-based simulations to determine whether social learning on an NK model can
 reproduce the behavior observed on Wikipedia.
@@
 suggesting possible benefits to decentralized collaborations made of smaller, more tightly-knit teams.
-We also propose a novel consensus-based social learning strategy that is both more efficient and higher
+We also propose a novel local majority-based social learning strategy that is both more efficient and higher
 performance than existing strategies, and reproduces some behaviors seen in WikiProjects.
@@
 and lower efficiency at reaching the highest quality levels;
-\item Using numerical simulations, we show that the performance and efficiency of some networked learning strategies depends on degree distribution.
+\item Using agent-based modeling, we show that the performance and efficiency of some networked learning strategies depends on degree distribution.
 \end{itemize}
@@
 Section \ref{sec:wp} describes the methodology and results of our empirical analysis of WikiProjects,
-Section \ref{sec:sim} describes the methodology and results of our numerical simulations,
+Section \ref{sec:sim} describes the methodology and results of our agent-based models,
 Section \ref{sec:discuss} discusses the interpretation and broader impact of our results,
@@
 inefficient ones \cite{barkoczi_social_2016}.
-The above tradeoff between convergence time, optimality, and learning strategy
+The above trade-off between convergence time, optimality, and learning strategy
 motivates the distinction between performance and efficiency in the current study.
@@
 as evidenced by highly-skewed degree distributions,
-perform worse on collaborative tasks \mbox{\cite{kearns_experiments_2012}}.
+perform worse on collaborative tasks \cite{kearns_experiments_2012}.
 In the present project, we use co-editor network degree skewness to
@@
 We also find that mean min-cut is highly correlated with degree ($r=0.980$, $p<0.001$),
-so we exclude min-cut from regression models to prevent collinearity (see Figure \ref{fig:degree-mincut}).
+so we exclude min-cut from regression models to prevent collinearity.
 The high correlation between mean degree and min-cut implies that in most cases
@@
 \centering
-\includegraphics[width=3in,height=3in]{fig-eff-perf-hist.pdf}
+\includegraphics[width=2.5in,height=2.5in]{fig-eff-perf-hist.pdf}
 \caption{
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=2.33in,height=2.33in]{fig-degree-mincut.pdf}
-\caption{
-Min-cut of WikiProject coeditor networks vs. their mean degree.
-\label{fig:degree-mincut}
-}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=2.33in,height=2.33in]{fig-degree-mincut.pdf}
+%\caption{
+%Min-cut of WikiProject coeditor networks vs. their mean degree.
+%\label{fig:degree-mincut}
+%}
+%\end{figure}
 
@@
 
+\begin{table*}[!ht]
+\small
+\centering
+\caption{
+Social learning strategies
+\label{tab:strat}
+}
+\bigskip
+\begin{tabular}{lccccc}
+Name          & Social stage & Individual stage & Limited concern & Unknown objective & Single truth \\
+\hline
+Best+I & Best neighbor   & Global & & & \\
+Conf+I & Conformity      & Global & & \Checkmark & \\
+Best+LI & Best neighbor  & Local  & \Checkmark & & \\
+Conf+LI & Conformity     & Local  & \Checkmark & \Checkmark & \\
+LMaj+LI & Local majority & Local  & \Checkmark & \Checkmark & \Checkmark \\
+\hline
+\end{tabular}
+\end{table*}
+
 In addition to our empirical study,
@@
 
-\begin{table*}
-\small
-\centering
-\caption{
-Social learning strategies
-\label{tab:strat}
-}
-\bigskip
-\begin{tabular}{lccccc}
-Name          & Social stage & Individual stage & Limited concern & Unknown objective & Single truth \\
-\hline
-Best+I & Best neighbor   & Global & & & \\
-Conf+I & Conformity      & Global & & \Checkmark & \\
-Best+LI & Best neighbor  & Local  & \Checkmark & & \\
-Conf+LI & Conformity     & Local  & \Checkmark & \Checkmark & \\
-LMaj+LI & Local majority & Local  & \Checkmark & \Checkmark & \Checkmark \\
-\hline
-\end{tabular}
-\end{table*}
-
 \subsection{Simulation results}
@@
 \caption{
-Degree regression coefficients for agent-based models.
+Degree regression coefficients for simulations.
 \label{tab:sim-perf}
@@
 non-local counterparts.
-The consensus strategy is both more efficient and more performant than others,
+For the best-neighbor strtegy, local outperforms global.
+For local conformity strategy performs notably worse than all other strategies.
+The local majority strategy is both more efficient and more performant than others,
 with its performance increasing with higher rewiring.
+These results imply that,
+at least in a simple model of collaboration,
+the performance and efficiency can be simultaneously increased.
+Furthermore, performance and efficiency are potentially affected by both the choice of
+learning strategy and the average degree of the agents' social network.
 
@@
 Table \ref{tab:sim-perf}.
-For both local and non-local versions of the best-neighbor and conformity strategies,
+For non-local versions of both conformity and best-neighbor strategy,
 there is no significant effect of degree on performance or efficiency.
-As noted above however, the local versions consistently have higher performance and lower efficiency
-than their non-local counterparts.
-We observe more interesting behavior with the consensus strategy.
-Node degree shows a significant negative correlation with degree,
-and a small but significant positive correlation with efficiency.
-The consensus simulations replicate the efficiency behavior observed in WikiProjects,
-but the opposite behavior for performance.
-But unlike other strategies, consensus demonstrates that degree distribution can have an
-impact on both performance and efficiency.
+The local best-neighbor strategy shows reduced performance with increasing degree,
+but no change in efficiency.
+Local conformity and local majority show opposite behavior as degree increases:
+with local conformity gaining efficiency at the expense of performance,
+while local majority increases in performance and decreases in efficiency.
+The largest effect size is achieved for efficiency in the local majority simulation,
+which is consistent with the efficiency behavior observed in WikiProjects.
+However, the performance behavior for local majority is opposite that observed on
+Wikipedia.
+These agent-based models confirm that network degree has the potential to influence
+the performance and efficiency of collaborations.
+Furthermore, this influence can be drastically different depending on the strategies
+used by collaborators.
 
@@
 We observe several results consistent with previous work:
-a trade-off between performance and efficiency,
-higher performance for shorter path lengths in a conformity setting,
-and a reduction in performance with increased structural inequality.
+a trade-off between performance and efficiency
+\cite{mason_propagation_2008,grim_scientific_2013},
+higher performance for shorter path lengths in a conformity setting
+\cite{barkoczi_social_2016},
+and a reduction in performance with increased structural inequality
+\cite{kearns_experiments_2012}.
 By using real-world networks, we were also able to analyze network properties independently,
@@
 
-Our numerical simulations offer a few additional insights.
-Our proposed local variants of best-neighbor and conformity strategies out-performed
-the standard variants while searching fewer alternatives.
-The higher performance for less work is analogous to the performance increases that
-have been seen for sampling fewer neighbors \cite{barkoczi_social_2016}.
-However, our network is a special case in that its structure is related to the structure of
-the NK model being optimized, which could increase the usefulness of local information.
-Our proposed consensus strategy, intended to model Wikipedia more closely,
-exhibits a degree-dependent performance and efficiency, unlike other strategies.
-This dependence is also seen in our Wikipedia analysis, although performance's dependence has the opposite sign.
-The consensus strategy is also interesting in that it is more efficient and higher performance than the other strategies.
-The unique properties of the consensus strategy may be due to a major difference it has from the others:
-rather than exploring through local hill-climbing,
-the consensus strategy combines parts of existing solutions to create entirely new ones.
+Our agent-based models offer a few additional insights.
+We observe degree-dependent performance and efficiency dependence for both local conformity
+and local majority strategies.
+However, these two strategies have opposite degree dependence,
+suggesting that different strategies may be preferable for high-degree and low-degree
+networks.
+Our local majority strategy,
+designed to satisfy several properties present in real-world collaborations,
+shows the strongest effects on performance and efficiency as network degree changes.
+For the local majority strategy,
+the relationship between degree and efficiency is consistent with our
+empirical observations on Wikipedia,
+suggesting one possible mechanism underlying that efficiency dependence.
+However, the performance dependence of this strategy
+is opposite that observed on Wikipedia,
+suggesting that either the local majority strategy
+is incompatible with actual behavior on Wikipedia or
+that other factors (possibly including degree skewness)
+outweigh the contribution of mean degree.
 
@@
 However, the consistency of our results with other lab-based and numerical studies
-suggests that the causal link is worth further study.
-Similarly, our study focuses entirely on a single setting and while it is suggestive,
+suggests that the causal link is worthy of further study.
+Similarly, our study focuses entirely on a single online community and while it is suggestive,
 does not necessarily generalize,
@@
 degree,
-we have proposed a novel consensus learning strategy that is more realistic, more efficient, and higher performance than
+we have proposed a novel local majority learning strategy that is more realistic, more efficient, and higher performance than
 existing strategies.
-While the efficiency and performance of existing strategies do not exhibit any degree-dependence, our consensus strategy
-demonstrates that degree-dependence is possible.
+We observe that in both the local majority strategy and a localized version of
+the conformity strategy,
+the performance and efficiency of a collaboration can exhibit degree dependence,
+and that the direction of that dependence depends on the specific strategy being used.
 While additional work is needed to determine causal relationships and how generalizable our results are,

### 2018-01-24 paper-content.tex
Revisions based on Daniel's feedback.

@@
 and the performance and efficiency of those networks.
-We also perform agent-based simulations to determine whether social learning on an NK model can
-reproduce the behavior observed on Wikipedia.
-We find several results seen in numerical and small-scale lab studies:
+WikiProject performance is consistent with results seen in numerical and small-scale lab studies:
 a performance/efficiency trade-off,
@@
 We also see behaviors not previously identified: an association between low degree coeditor networks
-and both higher performance and higher efficiency,
-suggesting possible benefits to decentralized collaborations made of smaller, more tightly-knit teams.
-We also propose a novel local majority-based social learning strategy that is both more efficient and higher
-performance than existing strategies, and reproduces some behaviors seen in WikiProjects.
+and both higher performance and higher efficiency.
+We also use agent-based models to explore possible mechanisms for
+degree-dependent performance and efficiency.
+We present a novel local-majority learning strategy designed to satisfy properties
+of real-world collaborations.
+The local-majority strategy as well as a localized conformity-based strategy
+both show degree-dependent performance and efficiency,
+but in opposite directions,
+suggesting that these factors depend on both network structure and learning strategy.
+Our empirical and numerical results suggest 
+possible benefits to decentralized collaborations made of smaller,
+more tightly-knit teams,
+and that these benefits may be modulated by the particular learning strategies
+in use.
 \end{abstract}
@@
 
-The internet has enabled collaborations at a scale never before possible, a global scale.
-Wikipedia is one of the most successful and visible of these collaborations,
-and is particularly interesting for its highly decentralized structure with very little top-down control.
-It is notoriously difficult to organize even small groups without top-down control
+The internet has enabled collaborations at a global scale.
+Wikipedia, a free encyclopedia that invites anyone to edit articles,
+is one of the most successful and visible examples of such a collaboration.
+Organizing groups, even small ones, without top-down control is notoriously
+difficult
 \cite{freeman_tyranny_1972},
@@
 If Wikipedia is not structured as a top-down hierarchy, how is it structured?
-And is that structure related to its success?
+And how does that structure relate to its success?
 
@@
 each with their own standards, norms, and processes for evaluating and improving articles.
-We focus on the coeditor networks of these projects:
-which editors have edited at least one article in common?
 When measuring the quality of collaborative projects,
@@
 
+Our study focuses on the coeditor networks of each WikiProject:
+which editors have edited at least one article in common?
+These relationships represent possible flows of information.
+We focus specifically on mean degree, degree skewness, and path length.
+High-degree editors have more collaborators,
+which can increase diversity and access to information at the possible
+expense of higher coordination costs
+\cite{hong_groups_2004,golub_naive_2010}.
+Highly skewed degree distributions can amplify the biases of high-degree
+editors while reducing the need for explicit coordination
+\cite{kearns_experiments_2012}.
+Networks with shorter path lengths allow information to travel more quickly
+at the possible expense of less localized diversity
+\cite{mason_propagation_2008,barkoczi_social_2016}.
+
+In addition to our emperical study,
+we use agent-based modeling to examine the consequences of specific
+assumptions on networked collaboration.
+We model individual behavior using a {\em social learning strategy} that
+assumes agents 1. can only access a fraction of the model's state,
+2. interact with others who share their concerns,
+and 3. reconcile their preferences into a single state.
+Our model is the first we are aware of to incorporate these assumptions,
+which are present across many real-world collaborations
+including Wikipedia.
+
 Our main findings are:
 \begin{itemize}
-\item WikiProjects having low-degree coeditor networks tend to have both higher performance and higher efficiency, independent of path lengths;
+\item WikiProjects having low-degree coeditor networks tend to have both higher performance and higher efficiency, even when controlling for path length;
 \item Short path lengths tend to be associated with higher performance, consistent with a conformity-based learning strategy;
@@
 and lower efficiency at reaching the highest quality levels;
-\item Using agent-based modeling, we show that the performance and efficiency of some networked learning strategies depends on degree distribution.
+\item Our agent-based model
+shows that the efficiency and performance of collaborations can
+depend on network degree,
+and that the direction of that dependence varies with social learning strategy.
 \end{itemize}
 
+Our findings shed light on the importance of network structure for successful
+collaboration.
+These findings might be informative for future interventions which
+recommend tasks based on how they will
+influence network structure,
+or interventions which seek to encourage the behavioral norms most
+effective for existing network structure.
+
 The rest of the paper is structured as follows.
-Section \ref{sec:background} reviews related work and the motivation for the present project,
-Section \ref{sec:wp} describes the methodology and results of our empirical analysis of WikiProjects,
-Section \ref{sec:sim} describes the methodology and results of our agent-based models,
-Section \ref{sec:discuss} discusses the interpretation and broader impact of our results,
-and Section \ref{sec:conclusion} concludes.
+The following section reviews related work and the motivation for the present project.
+We next describe the methodology and results of our empirical analysis of WikiProjects,
+followed by the methodology and results of our agent-based models.
+We continue to discuss the interpretation and broader impact of our results,
+and then conclude.
 
@@
 \label{sec:background}
-
-The field of social learning studies how
-groups of interacting agents
-can collaborate to solve complex problems.
-In {\em networked social learning},
+The present paper investigates the relationship between social networks
+and collaboration outcomes.
+This connection has been explored by a number of theoretical,
+numerical, and small-scale lab studies in the field of
+{\em social learning}.
+We expand the literature with a large-scale, empirical field study.
+In much of the existing literature,
+degree distribution correlates with outcome measures.
+But aside from the naive Bayes case, it is unknown whether
+the correlation is explained best by degree or by another structural property
+correlated with degree, such as characteristic path length.
+In the empirical networks we study,
+unlike artificial networks,
+the structural properties vary independently,
+making it easier to isolate individual
+network properties that correlate with outcome variables.
+
+{\bf Social Learning.} In {\em networked social learning},
 agents are represented by nodes on a network
@@
 inefficient ones \cite{barkoczi_social_2016}.
-The above trade-off between convergence time, optimality, and learning strategy
-motivates the distinction between performance and efficiency in the current study.
-
-Lab-based experiments on networked collaboration
+
+{\bf Lab experiments.} Lab-based experiments on networked collaboration
 suggest a complex interaction between network topology,
@@
 The same studies found that while human subjects tend to perform very well on
-a number of networks, they perform worst on collaboratively self-organized
-networks, highlighting the importance of intentionality
-in constructing communication channels for collective decision-making.
+a number of networks, they perform worst on self-organized
+networks.
 Similarly, some network topologies are able to reach faster decisions in the
@@
 behavior only influences first-degree neighbors.
-While theories of networked social learning have been tested in small-scale lab experiments,
-there is a need to study real-world, large-scale collaborations,
-as we do in the present paper.
-
-In addition to learning, decision-making is a crucial component of collaboration.
-The Condorcet jury theorem and its extensions \cite{list_epistemic_2001}
-describe how individuals can use majority voting to improve their
-decision-making ability.
-The process of decision-making is sometimes divided into
-``talking'' and ``voting'' stages.
-% Not yet published
-%While hierarchical representative democracy sometimes improves the outcome
-%of ``talk,'' it weakens the result of the Condoret jury theorem for voting
-%\cite{}.
-Robert Michels proposed the ``iron law of oligarchy,''
-\cite{michels_political_1999} which states that
-the earlier members of a group will, over time, gain disproportionate
-decision-making power and act increasingly out of self-interest rather than
-the good of the group.
-Shaw and Hill found that behavior in online wiki communities is consistent
-with the iron law \cite{shaw_laboratories_2014}.
-A number of studies, summarized in \cite{gentry_consensus_1982},
-have examined consensus-based decision-making procedures, used extensively by
-the Quakers and later by activist communities.
-The hallmark of consensus is the equal and active participation by all members
-of a group.
-Key findings include the trade-off between speed and quality of decisions,
-the importance of expressing conflict early in the process,
-and the willingness to recognize when one's own views are counter to the
-existing consensus.
-De Tar created InterTwinkles \cite{detar_intertwinkles:_2013},
-an online suite of tools to facilitate consensus decision-making
-in small cooperatives.
-Consensus decision making is notoriously difficult to apply in large groups.
-Wikipedia is one of the largest collaborations to use consensus-based
-decision-making,
-making it an excellent place to study the role of network structure in
-large-scale collaboration.
-
+
+{\bf Digital Communities.}
 Research on digital communities has also examined the role of factors
@@
 in collaborative work and decision-making.
-Using a simulation model, Hong and Page \cite{hong_groups_2004} found that
+Using an agent-based model, Hong and Page \cite{hong_groups_2004} found that
 diverse groups can outperform groups composed of the best individual
@@
 who act as exclusive intermediaries between disconnected portions of the
-social network \mbox{\cite{silverman_patronage_1965}}.
+social network \cite{silverman_patronage_1965}.
 Similarly, successful innovation in organizations often occurs in ``structural
-holes'' between groups \mbox{\cite{granovetter_strength_1973}}.
+holes'' between groups \cite{granovetter_strength_1973}.
 There is some evidence that groups with high structural inequality,
@@
 perform worse on collaborative tasks \cite{kearns_experiments_2012}.
-In the present project, we use co-editor network degree skewness to
-examine the relationships between structural inequality,
-project performance, and project efficiency.
 
@@
 article.
+Shaw and Hill found that behavior in online wiki communities is consistent
+with the Robert Michels' ``iron law of oligarchy,''
+which states that
+earlier members of a group will, over time, gain disproportionate
+decision-making power and act increasingly out of self-interest rather than
+the good of the group.\cite{michels_political_1999,shaw_laboratories_2014}.
 Looking specifically at Wikipedia policies determined by editor consenus,
@@
 a few key themes emerge.
-The efficiency and performance of collaborations are important considerations
+The efficiency and performance of collaborations are both important considerations
 and vary depending on both network structure and type of task
 \cite{kearns_experiments_2012}.
-While generated signal models of social learning predict no relationship between the two
+While generated signal models of social learning predict no relationship
+between the two
 \cite{golub_naive_2010},
@@
 \cite{kearns_experiments_2012,grim_scientific_2013}.
-
-In this project, I will investigate several gaps in the existing literature.
-In much of the existing literature,
-degree distribution correlates to performance.
-But aside from the naive Bayes case in social learning, it is unknown whether
-the correlation is explained best by degree or by another structural property
-correlated with degree.
-The characteristic path length and min-cut studied here are candidates for such
-degree-correlated factors.
-While existing work has focused on families of artificial networks,
-this project examines a large number of naturally-occurring networks.
-Unlike artificial networks, the structural properties of these naturally-occurring
-networks can vary independently, making it easier to isolate individual
-network properties that correlate with outcome variables.
-This project will also examine Wikipedia for evidence that structural
-inequality (in the form of skewed degree distributions)
-has relationship with performance,
-as has been observed in lab experiments
-\cite{kearns_experiments_2012}.
 
@@
 Two possibilities are
-1. how quickly they find a solution, and
-2. how good their solution is.
+1. how quickly they find a solution,
+which we call {\em efficiency}, and
+2. how good their solution is,
+which we call {\em performance}.
 Evidence from numerical simulations
@@
 and field observations \cite{gentry_consensus_1982}
-all suggest a trade-off between performance and efficiency.
+all suggest a trade-off between efficiency and performance.
 While common, this trade-off is not absolute,
@@
 \begin{description}
-\item[C-efficiency] Quantifies how quickly a WikiProject improves low-quality articles.
-\item[Connected fraction] Fraction of coeditor pairs connected by a path.
+\item[C-efficiency]
+(Only used for performance.)
+Quantifies how quickly a WikiProject improves articles.
+Efficiencies for different grades are highly correlated,
+so we include only one.
+\item[Connected fraction]
+Fraction of coeditor pairs connected by a path.
 \item[Talk fraction] Fraction of total revisions made to talk pages.
+\item[Mean similarity] Mean Jaccard similarity (by article) with other WikiProjects; a measure of topical complexity.
 \item[Mean editors/article] Mean number of editors collaborating on each article in a WikiProject.
@@
 \item[Mean article age] Mean age of articles within a WikiProject.
-\item[Mean similarity] Mean Jaccard similarity (by article) with other WikiProjects; a measure of topical complexity.
 \end{description}
@@
 In-degree and out-degree skewness were also highly correlated,
-so we only include out-degree skewness in the models.
-Some variables are log-transformed.
+so we only include out-degree skewness in the models
+(results are qualitatively similar).
+Heavy-tailed variables are log-transformed.
 To test the robustness of our results,
@@
 which is impractical in the empirical setting.
-It is important to note that the goal of our model is not to create an
-accurate simulation of Wikipedia or any other specific platform.
-Rather, our goal is to simulate collaboration in the abstract so that we can
-examine the results of altering various assumptions and parameters.
+It is important to note that the goal of our model is not to simulate
+all the intricacies of Wikipedia or any other specific platform.
+Rather, our goal is to determine whether the correlations we observe
+between degree and outcome variables
+on Wikipedia can be reproduced in a more general setting.
 
@@
 collaborating to optimize articles according to community preferences.
-Note that these community preferences don't assume the existence of any
+Note that these community preferences do not assume the existence of any
 ground truth, other than the preferences themselves.
@@
 state when making decisions and determining preferences.
+(On Wikipedia, editors typically interact with a small subset of the articles.)
 \item[Concern-based network] Agents interact with other agents who share a
 common concern over some subset of the state.
+(On Wikipedia, editors interact with others who share interests in the same articles.)
 \item[Unknown objective] Agents can rank states in order of preference,
 but do not have access to the objective function.
+(On Wikipedia, there is no ground truth measure of quality.)
 \item[Single source of truth] At any given time, the system is in a single state
 and agent preferences are based on local modifications to that state.
+(At any point in time, there is only one current version of Wikipedia.)
 \end{description}

### 2018-01-24 paper-content.tex
More revisions, some trimming.

@@
 FA articles are ``the best articles Wikipedia has to offer''
-\cite{}.
+\cite{wikipedia_contributors_wikipedia:featured_2018}.
 GA articles meet ``a core set of editorial standards`` but are ``not featured article quality''
-\cite{}.
+\cite{wikipedia_contributors_wikipedia:good_2017}.
 When an article is assigned GA or FA status,
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \begin{center}
@@
 \caption{
-Templates appearing at the top of the English-language Wikipedia talk page
+From Wikipedia talk page
 for {\em Knitting}.
-The article belongs to both {\em WikiProject Technology} and
-{\em WikiProject Textile Arts}.
-Both WikiProjects have assessed the article as B-class quality.
+Both {\em WikiProject Technology} and
+{\em WikiProject Textile Arts}
+have assessed the article as B-class quality.
 The article has also been nominated for both good article (GA) and
 featured article (FA) status,
-but after a consensus-based deliberation open to all Wikipedia editors,
-was not assigned GA or FA status.
+but was not assigned either status after a site-wide consensus-based deliberation.
 \label{fig:knitting}
@@
 \small
-\caption{Standardized coefficients for OLS models.
-\label{tab:model}
-}
-\bigskip
 \begin{tabular}{lllllllll}
@@
 \end{tablenotes}
+\caption{Standardized coefficients for OLS models.
+\label{tab:model}
+}
 \end{table}
@@
 \centering
-\caption{
-Social learning strategies
-\label{tab:strat}
-}
-\bigskip
 \begin{tabular}{lccccc}
@@
 \end{tabular}
+\caption{
+Definitions and properties of social learning strategies.
+Each consists of a social stage and an individual stage.
+Individual stages use hill-climbing based on either the global state,
+or the agent's local concern.
+\label{tab:strat}
+}
 \end{table*}
@@
 \cite{barkoczi_social_2016}.
-We confirmed that all trials converged to their maximum value before reaching the last iteration.
-Some statistics on the network properties of the networks are summarized in Table \ref{tab:stats}.
-We see that the coefficient of variation of degree is approximately 10\%,
+We confirmed that all trials converged to their maximum value before reaching
+the last iteration.
+Networks had mean degree 116.6 with 1.3 standard deviation,
+and mean path length of 1.766 with 0.0027 standard deviation.
+The coefficient of variation of degree is approximately 10\%,
 while only 1\% for mean path length, confirming that the rewiring process has a stronger influence
@@
 
-\begin{table}
-\small
-\centering
-\caption{
-Simulated network statistics.
-\label{tab:stats}
-}
-\bigskip
-\begin{tabular}{lcc}
-Property          & Mean  & Std. Dev. \\
-\hline
-Mean Degree       & 116.6 & 1.3 \\
-Mean Path length  & 1.766 & 0.0027 \\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{figure}
+\begin{figure}[t!]
 \centering
@@
 Mean agent solution value over time, averaged over 100 trials.
+Strategies are defined in Table \ref{tab:strat}.
 The top and bottom figures show results for agent networks with the probability of
@@
 Each point represents a single trial of 300 iterations.
+Strategies are defined in Table \ref{tab:strat}.
 The local best-neighbor strategy shows
@@
 non-local counterparts.
-For the best-neighbor strtegy, local outperforms global.
+For the best-neighbor strategy, local outperforms global.
 For local conformity strategy performs notably worse than all other strategies.
@@
 
-Our work raises several questions that could be the subject of future work.
+A better understanding of the relationship between network structure and collaboration
+outcomes has many practical applications.
+Online communities using recommender systems to improve collaboration
+could make recommendations guided by desirable network properties.
+Similarly, network structure could be used to identify underperforming
+groups in need of an intervention.
+The relationship between network structure and learning strategy suggests that
+behavioral norms interact with network structure.
+This knowledge could be used by interventions to ensure that behavioral norms
+and network structure are aligned for best performance and efficiency.
+
+Our work suggests several directions for future work.
 Is the correlation between network structure, performance, and efficiency causal?
@@
 Are similar relationships observed in other large-scale collaborations?
-Does varying degree independently of path length influence performance and efficiency in a controlled
-lab setting?
+Does varying degree independently of path length influence
+performance and efficiency in a controlled lab setting?
 

### 2018-01-24 paper-content.tex
Trim.
Spelling and formatting fixes.

@@
 which we call {\em performance}.
-These two terms are often used interchangably,
+These two terms are often used interchangeably,
 but we find it fruitful to distinguish between the two concepts.
@@
 
-In addition to our emperical study,
+In addition to our empirical study,
 we use agent-based modeling to examine the consequences of specific
@@
 the good of the group.\cite{michels_political_1999,shaw_laboratories_2014}.
-Looking specifically at Wikipedia policies determined by editor consenus,
+Looking specifically at Wikipedia policies determined by editor consensus,
 Keegan and Fiesler found a trend
-from flexibile rule-making towards less flexible maintenance and deliberation
+from flexible rule-making towards less flexible maintenance and deliberation
 \cite{keegan_evolution_2017}.
@@
 \item[Revision count] Total number of revisions to articles in a WikiProject.
-\item[First assessment] Timesamp of first assessment; a measure of how long a WikiProject has been active.
+\item[First assessment] Timestamp of first assessment; a measure of how long a WikiProject has been active.
 \item[Mean article age] Mean age of articles within a WikiProject.
@@
 Numerical models allow us to determine the effect of changing a single
-variable (e.g., network strucutre, learning strategy),
+variable (e.g., network structure, learning strategy),
 which is impractical in the empirical setting.
@@
 \centering
-\includegraphics[width=2.5in,height=5in]{fig-val-iter.pdf}
+\includegraphics[width=3in,height=1.5in]{fig-val-iter.pdf}
 \caption{
@@
 could make recommendations guided by desirable network properties.
-Similarly, network structure could be used to identify underperforming
+Similarly, network structure could be used to identify under-performing
 groups in need of an intervention.

### 2018-01-25 paper-content.tex
Highlight eff/perf tradeoff and trim.

@@
 and the performance and efficiency of those networks.
-WikiProject performance is consistent with results seen in numerical and small-scale lab studies:
-a performance/efficiency trade-off,
+We confirm the existence of an overall performance-efficiency trade-off,
+while observing that some projects are higher than others in both performance
+and efficiency,
+suggesting the existence factors correlating positively with both.
+Namely, we find an association between low-degree coeditor networks
+and both high performance and high efficiency.
+We also confirm results seen in previous numerical and small-scale lab studies:
 higher performance with less skewed node distributions,
 and higher performance with shorter path lengths.
-We also see behaviors not previously identified: an association between low degree coeditor networks
-and both higher performance and higher efficiency.
-We also use agent-based models to explore possible mechanisms for
+We use agent-based models to explore possible mechanisms for
 degree-dependent performance and efficiency.
@@
 suggesting that these factors depend on both network structure and learning strategy.
-Our empirical and numerical results suggest 
+Our results suggest 
 possible benefits to decentralized collaborations made of smaller,
@@
 the network structure \cite{newman_structure_2003}.
-If Wikipedia is not structured as a top-down hierarchy, how is it structured?
-And how does that structure relate to its success?
-
-We approach these questions by analyzing WikiProjects on the English-language Wikipedia.
+How does Wikipedia's non-hierarchical structure relate to its success?
+
+We look specifically at WikiProjects on the English-language Wikipedia.
 WikiProjects are collections of thematically related articles,
-each with their own standards, norms, and processes for evaluating and improving articles.
+each with their own standards, norms, and processes.
 When measuring the quality of collaborative projects,
@@
 but we find it fruitful to distinguish between the two concepts.
+We find that Wikipedia, like many other collaborations,
+exhibits an overall trade-off between performance and efficiency.
+However, some WikiProjects are higher in both efficiency and performance
+than others,
+suggesting the existence of factors that correlate positively with both.
 
@@
 \begin{itemize}
-\item WikiProjects having low-degree coeditor networks tend to have both higher performance and higher efficiency, even when controlling for path length;
+\item Despite an overall performance/efficiency trade-off,
+WikiProjects having low-degree coeditor networks tend to have both higher performance and higher efficiency;
 \item Short path lengths tend to be associated with higher performance, consistent with a conformity-based learning strategy;
-\item Structural inequality, as measured by degree skewness, is associated with lower performance,
-and lower efficiency at reaching the highest quality levels;
+\item Structural inequality, as measured by degree skewness, is associated with lower performance;
 \item Our agent-based model
@@
 effective for existing network structure.
-
-The rest of the paper is structured as follows.
-The following section reviews related work and the motivation for the present project.
-We next describe the methodology and results of our empirical analysis of WikiProjects,
-followed by the methodology and results of our agent-based models.
-We continue to discuss the interpretation and broader impact of our results,
-and then conclude.
 
@@
 {\bf Digital Communities.}
-Research on digital communities has also examined the role of factors
-such as diversity and inequality
+Research on digital communities has also examined the role of 
+diversity and inequality
 in collaborative work and decision-making.
@@
 problem-solvers.
-In sociology, much research has been done examining the relationship between
+In sociology, research has focused on the relationship between
 network structure and social capital.
@@
 holes'' between groups \cite{granovetter_strength_1973}.
-There is some evidence that groups with high structural inequality,
-as evidenced by highly-skewed degree distributions,
-perform worse on collaborative tasks \cite{kearns_experiments_2012}.
+There is some evidence that groups with higher structural inequality
+(degree skewness)
+perform worse \cite{kearns_experiments_2012}.
 
@@
 article's talk page (Figure \ref{fig:knitting}).
-Each WikiProject has its own page and talk page.
-These pages contain information about community norms within the project
+Each WikiProject has its own page and talk page,
+containing information about community norms within the project
 as well as discussions about individual articles.
 WikiProjects are thus distinct communities, with distinct norms and processes.
-These communities are the fundamental units of analysis in the present paper.
+These communities are the fundamental units of analysis in this paper.
 
@@
 have assessed the article as B-class quality.
-The article has also been nominated for both good article (GA) and
-featured article (FA) status,
-but was not assigned either status after a site-wide consensus-based deliberation.
 \label{fig:knitting}
@@
 \item{Strictly decreasing in the number of revisions (with transition count fixed);}
-\item{Independent of WikiProject size: not affected by adding an article if that article's transition/revision ratio is equal to the efficiency.}
+\item{Independent of WikiProject size: not affected by adding an article with the same efficiency.}
 \end{itemize}
@@
 \eeq
-Where the $g(t)$ term is present because a assessments sometimes raise article quality by several
-grades, in which case we divide the revisions evenly between all grade levels achieved.
+Where the $g(t)$ term accounts for assessments raising article quality by several
+grades,
+dividing the revisions evenly between all grade levels achieved.
 
@@
 
-The mean path and min-cut network measures are computationally intensive,
+The mean path and min-cutare computationally intensive,
 requiring distance and minimum $st$-cut calculations for each all node pairs.
 For larger projects, these calculations are impractical.
-When coeditor networks were large, we employed sampling to determine mean path length and mean
+For large networks, we employed sampling to determine mean path length and mean
 min-cut.
@@
 a unimodal distribution with low skew (see Figure \ref{fig:eff-perf-hist}).
+Our findings confirm the trade-off between performance and efficiency
+observed in many other settings (Figure \ref{fig:eff-perf}).
+However, when looking at specific projects, some are higher in both performance
+and efficiency,
+suggesting the existence of factors which correlate positively with both.
 
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \centering
@@
 \label{fig:eff-perf-hist}
+}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=2.5in,height=1.67in]{fig-perf-eff.pdf}
+\caption{
+WikiProject performance is anticorrelated with B-level efficiency,
+with Pearson r of -0.12.
+Results are similar for other grade levels.
+On average, highly efficient WikiProjects are under-performing,
+but when looking at specific WikiProjects,
+some are higher than others in both performance and efficiency.
+\label{fig:eff-perf}
 }
@@
 \item[C-efficiency]
-(Only used for performance.)
+(Performance only.)
 Quantifies how quickly a WikiProject improves articles.

### 2018-03-30 ic2s2-2018/ic2s2.tex
Updates based on icwsm reviews.

\documentclass[a4paper,12pt]{article}
% IC2S2 Extended Abstract Template
% version 1.1, last updated 2018-01-26
% This template works best with PDFLaTeX
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{mathptmx}
\usepackage[usenames, dvipsnames]{color}
\usepackage[normal]{threeparttable}
\usepackage{float}

\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\newcommand{\+}{\phantom{-}}

%\usepackage{natbib}
%\bibliographystyle{ksfh_nat}
\bibliographystyle{plain}

%Pleasure ensure the ic2s2.sty file is in the same directory as your LaTeX document
%This package will set the margin, header, etc. as required for submission
\usepackage{ic2s2}

%Directory containing your figure files (optional)
%\graphicspath{{images/}}

%Please complete the following meta information
\title{Network Structure, Efficiency, and Performance in WikiProjects}
\shorttitle{Network Structure, Efficiency, and Performance in WikiProjects}
\keywords{peer-production, networks, collaboration, wikipedia, social learning}
\author{Anonymous}
\date{} %Leave blank for submission
\confdates{July 12--15, 2018}
\conflocation{Northwestern University's Kellogg School of Management, Evanston, IL.~USA}

\begin{document}

\maketitle

%Feel free to retitle this section and to use \section or \section* as you see fit
\section*{Extended Abstract}

Large-scale collaboration in the absence of top-down control is notoriously
difficult\cite{freeman_tyranny_1972},
yet the internet has enabled decentralized collaborations at a global scale.
Wikipedia is one of the most visible examples,
with millions of self-organized editors collaboratively producing
a high-quality encyclopedia \cite{giles_internet_2005}.
A better theoretical understanding of such projects is desirable,
in order to identify best-practices and inform the design of new projects.
We focus specifically on how the network structure formed
by editor interactions within a WikiProject relate to
two variables:
{\em efficiency} (how much is accomplished by a unit of work)
and {\em performance} (the best quality typically reached).
We confirm behaviors observed in numerical and small-scale lab studies
\cite{kearns_experiments_2012,golub_naive_2010,mason_propagation_2008},
such as an overall trade-off between performance and efficiency.
However, we find evidence that some variables correlate positively with both variables.

We focus on WikiProjects on the English-language Wikipedia.
WikiProjects are groups of related articles,
and form distinct communities, with distinct norms and processes.
One of the main roles of a WikiProject is to assess the quality of articles
within that project, which we use to quantify article progress.
We also rely ondesignations of featured article (FA) or good article (GA) status,
which are decided independently of WikiProject assessments.
We combine multiple data sets from the English-language Wikipedia.
For information about edit history, we used a publicly-available data set containing
metadata about all edits from July 12, 2006 to December 2, 2015.
To get the rating history of each article,
we used a custom script to scrape the daily logs produced by WP 1.0 Bot for
all unique WikiProjects (2279)
between May 4, 2006 and December 2, 2015.
Finally, we used a publicly-available log of page events (including rename events)
to reconstruct the unique identifier for each article title mentioned in
the rating history logs.

We define efficiency as the mean number of articles that reach a grade level,
divided by the number of edits since the previous grade level.
Let $T(W,G)$ be the set of article assessment transitions from below grade $G$
to grade $G$ or higher in project $W$.
Let $N(W,G)$ be the number of articles in project $W$ which ever transition
from below grade $G$ to grade $G$ (or higher).
Let $r(t)$ be the number of article revisions since its previous grade transition.
The grade $G$ efficiency is:
\begin{eqnarray}
E(W,G)
&=&
\left[
\frac{1}{
N(W,G)
}
\sum_{t \in T(W,G)} \frac{r(t)}{g(t)}
\right]^{-1},
\end{eqnarray}
where $g(t)$ (the number of grade levels crossed by transition $t$)
divides edits evenly when transitions span multipel grade levels.
Our performance measure $P(W)$ is defined simply as
the percentage of articles in project $W$ which have reached
good or featured status:
\begin{eqnarray}
P(W) &=& \frac{f(W) + g(W)}{n(W)},
\end{eqnarray}
where $f(W)$ and $g(W)$ are the numbered of featured and good articles respectively,
and $n(W)$ is the total number of articles.

For each WikiProject, we construct and analyze the coeditor network:
with editors being connected if they have edited at least one article in common.
These relationships represent possible flows of information.
We focus specifically on mean degree, degree skewness, and path length.
High-degree editors have more collaborators,
which can increase diversity and access to information at the possible
expense of higher coordination costs
\cite{hong_groups_2004,golub_naive_2010}.
Highly skewed degree distributions can amplify the biases of high-degree
editors while reducing the need for explicit coordination
\cite{kearns_experiments_2012}.
Networks with shorter path lengths allow information to travel more quickly
at the possible expense of less localized diversity
\cite{mason_propagation_2008,barkoczi_social_2016}.
The mean path length is computationally intensive,
so we employ stratified sampling,
choosing sample sizes such that the relative error is less than 10,
and exclude the 183 largest projects.

Our main findings (Figure \ref{fig:eff-perf}, Table \ref{tab:model}) are as follows.
Despite an overall performance/efficiency trade-off (r = -0.12, p $<$ 0.001),
Low-degree coeditor networks tend to have both higher performance and higher efficiency.
Short path lengths tend to be associated with higher performance, consistent with a conformity-based learning strategy.
Structural inequality (degree skewness) is associated with lower performance.

Our findings shed light on the importance of network structure for successful
collaboration at very large scales.
Our empirical results are strictly correlative, not causal,
and further work is necessary to determine causality.
However, the consistency of our findings with those in numerical simulations
and small-scale lab studies helps solidify a picture of the role of network
structure in collaboration.
The higher efficiency and performance observed for low-degree projects might
suggest benefits of collaborations of small closely-knit teams,
while the correlations between path length and performance might suggest
overlapping team membership in order to connect distant parts of the network.
And the correlation of low degree skewness with performance may suggest
benefits of decentralized team structure.
These findings might be informative for developing collaboration policies,
for designing interventions to recommend tasks based on how they will
influence network structure,
or for creating interventions which seek to encourage the behavioral norms most
effective for existing network structure.

%\section*{Acknowledgment(s)} %Optional

%\section*{References}
\bibliography{paper}

\section*{Figures and Tables}

\begin{figure}[H]
\centering
\includegraphics[width=4.5in,height=3in]{fig-perf-eff.pdf}
\caption{
WikiProject performance is anticorrelated with efficiency.
\label{fig:eff-perf}
}
\end{figure}

\begin{table}[H]
\centering
\small
\begin{tabular}{lllllllll}
&Perf$^\dagger$&A-Eff$^\dagger$&B-Eff$^\dagger$&C-Eff$^\dagger$\\
\hline
Mean degree$^\dagger$&-0.7$^{***}$&-0.8$^{***}$&-0.6$^{***}$&-0.3$^{*}$\\
Out degree skew$^\dagger$&-0.4$^{***}$&-0.5$^{**}$&-0.3$^{*}$&-0.06\\
Mean path length$^\dagger$&-0.33$^{***}$&-0.09&-0.05&-0.09\\
C-Efficiency$^\dagger$&-0.08$^{*}$&\+---&\+---&\+---\\
Connected frac.&0.01&0.09$^{*}$&0.15$^{***}$&0.06\\
Talk fraction$^\dagger$&0&-0.02&-0.03&0.01\\
Mean similarity$^\dagger$&0.06$^{**}$&-0.03&0.01&0.02\\
Mean editors/art.$^\dagger$&0.3$^{**}$&0.3&0.2$^{*}$&0.09\\
Article count$^\dagger$&-0.4&0.7$^{*}$&0.8$^{**}$&0.7$^{**}$\\
Editor count$^\dagger$&0.4&0.9$^{**}$&0.8$^{**}$&0.5$^{*}$\\
Revision count$^\dagger$&0.6$^{*}$&-1$^{**}$&-1.1$^{***}$&-1$^{***}$\\
First assessment&0.05&0.11$^{**}$&0.31$^{***}$&0.43$^{***}$\\
Mean article age&-0.03&-0.04&-0.01&-0.05$^{*}$\\
\hline
N&1179&966&1260&1415\\
R$^2_{adj}$&0.37&0.17&0.30&0.43\\
\hline
\end{tabular}
\begin{tablenotes}
\centering
\item $\dagger$ Log-transformed. * $p < 0.05$. ** $p < 0.01$. *** $p < 0.001$.
\end{tablenotes}
\caption{Standardized coefficients for OLS models.
\label{tab:model}
}
\end{table}

\end{document}

### 2018-03-30 paper-content.tex
Updates based on icwsm reviews.

@@
 \cite{kearns_experimental_2006}.
-Based on lab experiments, Fowler and Christakis \cite{fowler_cooperative_2010}
+Based on lab experiments, Fowler and Christakis \shortcite{fowler_cooperative_2010}
 suggest that individual decisions towards altruism are conditional on their
 neighbor's behavior and ``contagious'' up to three degrees away.
-Later experiments by Suri and Watts \cite{suri_cooperation_2011} confirmed the
+Later experiments by Suri and Watts \shortcite{suri_cooperation_2011} confirmed the
 existence of conditional altruism,
@@
 in collaborative work and decision-making.
-Using an agent-based model, Hong and Page \cite{hong_groups_2004} found that
+Using an agent-based model, Hong and Page \shortcite{hong_groups_2004} found that
 diverse groups can outperform groups composed of the best individual
@@
 
-Several studies have examined the role of community in the specific context
-of Wikipedia.
-Robert and Romero found that
+For Wikipedia specifically,
+Robert and Romero \shortcite{robert_crowd_2015} found that
 larger group sizes yield higher article ratings
-(as determined by editor peer-review)
-when the groups are diverse and experienced
-\cite{robert_crowd_2015}.
+when the groups are diverse and experienced.
 Also on Wikipedia,
 Kittur and Kraut found that different types of coordination have a complex
-effect on the quality of Wikipedia articles \cite{kittur_harnessing_2008}.
+effect on the quality of Wikipedia articles \shortcite{kittur_harnessing_2008}.
 Both explicit and implicit coordination result in higher quality articles,
@@
 article.
-Shaw and Hill found that behavior in online wiki communities is consistent
-with the Robert Michels' ``iron law of oligarchy,''
+Shaw and Hill \shortcite{shaw_laboratories_2014}
+found that behavior in online wiki communities is consistent
+with the ``iron law of oligarchy,''
 which states that
@@
 decision-making power and act increasingly out of self-interest rather than
-the good of the group.\cite{michels_political_1999,shaw_laboratories_2014}.
+the good of the group \cite{michels_political_1999}.
+Similarly, Halfaker et al. \shortcite{halfaker_rise_2013} attributed decreasing
+participation on Wikipedia to poor retention of new users.
 Looking specifically at Wikipedia policies determined by editor consensus,
-Keegan and Fiesler found a trend
-from flexible rule-making towards less flexible maintenance and deliberation
-\cite{keegan_evolution_2017}.
+Keegan and Fiesler \shortcite{keegan_evolution_2017} found a trend
+from flexible rule-making towards less flexible maintenance and deliberation.
+Using content analysis,
+Morgan et al. \shortcite{morgan_project_2013} found WikiProjects to be
+more loosely organized than traditional teams.
 
@@
 For information about edit history, we used a publicly-available data set containing
-metadata about all edits from July 12, 2006 to December 2, 2015.
-To get the rating history of each article,
-we wrote a script to scrape the daily logs produced by WP 1.0 Bot for
-all unique WikiProjects (2279)
+metadata (time, article id, user) about all edits from July 12, 2006 to December 2, 2015.
+We used a custom script to scrape article quality assessments from logs produced
+by WP 1.0 Bot for 2279 unique WikiProjects
 between May 4, 2006 and December 2, 2015.
-Finally, we used a publicly-available log of page events (including rename events)
-to reconstruct the unique identifier for each article title mentioned in the rating history logs.
+Finally, we used a publicly-available database dump of page events (including rename events)
+to reconstruct the article id for each title mentioned in the assessment logs.
 
@@
 excluding unconnected pairs.
-To account for unconnected pairs, we also measure the {\em connected fraction}
-of all possible edge pairs.
+To account for unconnected nodes, we also measure the {\em connected fraction}:
+the fraction of ordered node pairs with a directed path from source to sink.
 The path length represents how quickly information can move through the network.
@@
 {\em rugged landscape}, i.e., many local optima.
-The ruggedness of the model can be tuned through the parameters $N$ and $K$.
-Formally, the NK model produces a function $F$ mapping a binary string $S$ of length
+The ruggedness of the model can be tuned through the parameters $N$
+(the dimensionality of the solution space)
+and $K$ (the level of inderdependence between dimensions).
+Formally, the NK model produces an objective function $F$ mapping a binary string $S$ of length
 $N$ to a real value in $[0,1]$.
-The model consists of $N$ {\em loci}, with locus $i$ having a binary state $S_i$
+Model state is divided into $N$ {\em loci}, with locus $i$ having a binary state $S_i$
 and a value $f_i(S)$ dependent on its own state
@@
 The value of the model $F(S)$ is the mean of all locus values $f_i(S)$.
-In our models,
-agents thus seek to find a bit string $S$ that achieves the largest $F(S)$.
+In our simulations,
+agents iteratively search for a bit string $S$ that maximizes $F(S)$.
 
@@
 Strategies are defined in Table \ref{tab:strat}.
-The top and bottom figures show results for agent networks with the probability of
-rewiring set to 0 and 1, respectively.
-In both, local strategies are less efficient than their non-local counterparts.
-Local best-neighbor out-performs global,
-while local conformity is the worst performer in all cases.
-The local majority strategy is both more efficient and more performant than others.
 \label{fig:val-iter}
@@
 \end{figure}
+
+\begin{table}
+\small
+\caption{
+Simulated Performance and Efficiency.
+Results shown for 100 trials with P[rewire] = 0.
+Strategies are defined in Table \ref{tab:strat}.
+Local strategies are less efficient than their non-local counterparts.
+Local best-neighbor out-performs global,
+while local conformity is the worst performer in all cases.
+The local majority strategy is both most efficient and most performant.
+\label{tab:sim-eff-perf}
+}
+\centering
+\bigskip
+\begin{tabular}{lll}
+Strategy & Performance & Efficiency\\
+\hline
+Best+I  & 0.722 $\pm$ 0.001 & 0.0221 $\pm$ 0.0003 \\
+Conf+I  & 0.721 $\pm$ 0.001 & 0.0174 $\pm$ 0.0002 \\
+Best+LI & 0.726 $\pm$ 0.001 & 0.0131 $\pm$ 0.0002 \\
+Conf+LI & 0.586 $\pm$ 0.001 & 0.030 $\pm$ 0.001 \\
+LMaj+LI & 0.729 $\pm$ 0.001 & 0.046 $\pm$ 0.002 \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 Each curve represents an average over 100 trials, each with 250 agent solutions.
-For all rewiring values, local strategies are less efficient and more performant than their
-non-local counterparts.
+The mean performance and efficiency are reported in Table \ref{tab:sim-eff-perf}.
+For all rewiring values, local strategies are less efficient and more performant
+than their non-local counterparts.
 For the best-neighbor strategy, local outperforms global.
@@
 
-The effect of degree on performance and efficiency is shown in Figure \ref{fig:deg-eff-perf} and
+The effects of degree on performance and efficiency are shown in Figure \ref{fig:deg-eff-perf} and
 Table \ref{tab:sim-perf}.
@@
 suggests that the causal link is worthy of further study.
-Similarly, our study focuses entirely on a single online community and while it is suggestive,
-does not necessarily generalize,
-and studies of other systems are necessary to corroborate our findings.
+Similarly, our study focuses entirely on a single online community,
+and while the results are suggestive, they do not necessarily generalize.
+We have focused on structure, ignoring content-related variables.
+For simplicity, we have assumed unweighted edges and
+measured work by revision counts rather than bytes changed.
+
+Our work suggests several directions for future work.
+Is the correlation between network structure, performance, and efficiency causal?
+A time-dependent analysis of our data could offer insight.
+Are similar relationships observed in other large-scale collaborations?
+Does varying degree independently of path length influence
+performance and efficiency in a controlled lab setting?
 
@@
 and network structure are aligned for best performance and efficiency.
-
-Our work suggests several directions for future work.
-Is the correlation between network structure, performance, and efficiency causal?
-A time-dependent analysis of our data could offer insight.
-Are similar relationships observed in other large-scale collaborations?
-Does varying degree independently of path length influence
-performance and efficiency in a controlled lab setting?
 
@@
 \section{Acknowledgments}
-Anonymized for blind review.
-%I would like to thank Daniel M. Romero for valuable guidance and feedback;
-%Ceren Budak and Scott E. Page for their time and feedback;
-%Danielle Livneh and Karthik Ramanathan for help collecting the data sets;
-%Yan Chen and Tanya Rosenblat for feedback on the methodology;
-%and the attendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
-%the Berkman-Klein Center's Cooperation Working Group for helpful feedback on
-%preliminary results.
-%This research was funded by the University of Michigan School of Information.
+%Anonymized for blind review.
+Thanks to
+Ceren Budak, Scott E. Page, Yan Chen, Tanya Rosenblat, anonymous reviewers,
+and the attendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
+the Berkman-Klein Center Cooperation Working Group for helpful feedback;
+and to Danielle Livneh and Karthik Ramanathan for help collecting the data.
+This research was funded by the University of Michigan School of Information.

### 2018-04-04 paper-content.tex
Daniel's revisions.

@@
 is one of the most successful and visible examples of such a collaboration.
-Organizing groups, even small ones, without top-down control is notoriously
+Organizing groups without top-down control is notoriously
 difficult
@@
 help inform the design of new collaborative projects.
-We focus on one aspect of organizing a large-scale decentralized collaboration:
-the network structure \cite{newman_structure_2003}.
+We focus on one aspect of a large-scale decentralized collaboration:
+its network structure \cite{newman_structure_2003}.
 How does Wikipedia's non-hierarchical structure relate to its success?
 
-We look specifically at WikiProjects on the English-language Wikipedia.
+We look at WikiProjects on the English-language Wikipedia.
 WikiProjects are collections of thematically related articles,
-each with their own standards, norms, and processes.
+each with their own standards and norms.
 When measuring the quality of collaborative projects,
@@
 These two terms are often used interchangeably,
-but we find it fruitful to distinguish between the two concepts.
-We find that Wikipedia, like many other collaborations,
-exhibits an overall trade-off between performance and efficiency.
+but we find it fruitful to distinguish between the two.
+We find that Wikipedia exhibits an overall trade-off between performance and efficiency.
 However, some WikiProjects are higher in both efficiency and performance
@@
 WikiProjects having low-degree coeditor networks tend to have both higher performance and higher efficiency;
-\item Short path lengths tend to be associated with higher performance, consistent with a conformity-based learning strategy;
+\item Short paths are associated with higher performance, consistent with a conformity-based learning strategy;
 \item Structural inequality, as measured by degree skewness, is associated with lower performance;
@@
 But aside from the naive Bayes case, it is unknown whether
-the correlation is explained best by degree or by another structural property
-correlated with degree, such as characteristic path length.
+the correlation is explained best by degree or by another structural property, such as characteristic path length.
 In the empirical networks we study,
@@
 {\bf Lab experiments.} Lab-based experiments on networked collaboration
-suggest a complex interaction between network topology,
-and other factors.
-While groups of networked human subjects reliably perform very well on
+suggest a complex interaction between network topology and other factors.
+While groups of networked human subjects perform very well on
 difficult graph-coloring tasks, the best performing network architectures
@@
 from task to task \cite{kearns_experiments_2012}.
-The same studies found that while human subjects tend to perform very well on
-a number of networks, they perform worst on self-organized
+The same studies found that while human subjects tend to perform well on
+some networks, they perform worst on self-organized
 networks.
@@
 larger group sizes yield higher article ratings
-when the groups are diverse and experienced.
-Also on Wikipedia,
-Kittur and Kraut found that different types of coordination have a complex
+when the groups are diverse and experienced. Kittur and Kraut found that different types of coordination have a complex
 effect on the quality of Wikipedia articles \shortcite{kittur_harnessing_2008}.
@@
 
-Our analysis combines multiple data sets from the English-language Wikipedia.
+Our analysis combines multiple data
+sets\footnote{Data and code at https://elplatt.com/a/WikiProject-Eff-Perf}
+from the English-language Wikipedia.
 For information about edit history, we used a publicly-available data set containing
@@
 and edges connecting any editors who have edited the same article.
-The edges are directed, with the direction representing the direction of
+The edges are directed, with the direction representing
 {\em plausible information flow};
 an edge from Alice to Bob exists if Alice edited an article and then Bob edited the same article at
-a later time.
-Edges can exist in both directions e.g.,
-if an article was edited first by Alice, then by Bob, and again by Alice.
+a later time. Note that edges can exist in both directions. 
 We make the simplifying assumption of unit weight for all edges.
@@
 We also consider the {\em skewness} of the in-degree and out-degree distributions.
-A large positive degree skewness value for a WikiProject coeditor network
+A large positive degree skewness for a WikiProject coeditor network
 implies that a small number of editors have a very large number of collaborators,
@@
 from $s$ to $t$.
-The {\em characteristic path length} (or just {\em path length} for brevity)
+The {\em characteristic path length} (or just {\em path length})
 is the mean distance between all editor pairs,
@@
 The path length represents how quickly information can move through the network.
-Networks with longer paths require more interactions for information to propagate through
-the network,
+Networks with longer paths require more interactions for information to propagate,
 which has been shown to reduce efficiency in some settings
@@
 and allow innovations to propagate through complex contagion,
-in which innovations are only adopted after multiple exposures through different sources
-\cite{centola_complex_2007}.
-
-The mean path and min-cutare computationally intensive,
+in which innovations are only adopted after multiple exposures \cite{centola_complex_2007}.
+
+The mean path and min-cut are computationally intensive,
 requiring distance and minimum $st$-cut calculations for each all node pairs.
-For larger projects, these calculations are impractical.
-For large networks, we employed sampling to determine mean path length and mean
+For larger projects, these calculations are impractical and we thus employed sampling to determine mean path length and mean
 min-cut.
@@
 so we exclude the 183 largest projects from the analysis.
-To control for bias in project size, we include several size-related variables in our models.
 
@@
 we model the performance and efficiency of WikiProjects using ordinary least-squares linear regression.
-Each WikiProject is taken as a single observation.
+Each WikiProject is a single observation.
 The models include each project's coeditor network properties as independent variables.
-We also include several project-level variables to control for confounding factors,
-described below.
+We also include the following project-level variables to control for confounding factors.
 \begin{description}
@@
 In-degree and out-degree skewness were also highly correlated,
-so we only include out-degree skewness in the models
-(results are qualitatively similar).
+so we only include out-degree skewness
+(results are similar with in-degree skewness).
 Heavy-tailed variables are log-transformed.
@@
 we also computed models using cube root instead of logarithmic transformations,
-as well as using only top-importance and high-importance articles.
-These robustness check yielded qualitatively similar results for all variables,
+and using only top- and high-importance articles.
+The results were qualitatively similar results for all variables,
 except for degree-skewness, which had an inconsistent sign across models.
@@
 However, low degree is correlated with both higher efficiency and higher performance,
-suggesting that it is sometimes possible to improve both simultaneously.
+suggesting that it is possible to improve both simultaneously.
 Much of the existing numerical work on networked social learning focuses on path length rather than degree,
@@
 In designing our agent-based model, we paid attention to the
-following properties, motivated by real-world collaborations.
+following properties.
 \begin{description}
@@
 (On Wikipedia, editors interact with others who share interests in the same articles.)
-\item[Unknown objective] Agents can rank states in order of preference,
+\item[Unknown objective] Agents rank states in order of preference,
 but do not have access to the objective function.
@@
 In each iteration, one bit of the NK solution string is flipped to maximize the solution value.
-If no change improves the value, the original solution is kept
+If no change improves the value, the original solution is kept.
 The above strategy relies only on rankings of states,
 satisfying the unknown objective assumption.
-However, it does rely on information about the entire state,
+However, it relies on information about the entire state,
 violating the limited concern assumption.
@@
 agents can also incorporate information from
-other agents they are connected to by a network edge.
+other agents they are connected to by an edge.
 While individual learning always converges to the local maximum relative to the starting point,
@@
 In our model, we use both the conformity and best-neighbor strategies from \cite{barkoczi_social_2016}.
-In the {\em best-neighbor} strategy, each agent compares its solution to a sample of its
-neighbors, and chooses the solution with the highest value.
+In the {\em best-neighbor} strategy, each agent compares its solution to a sample of neighbors, and chooses the solution with the highest value.
 In order to compare solutions between neighbors,
@@
 Because each agent maintains a separate estimate of the solution,
-neither of these strategies satisfies the single source of truth assumption.
+neither strategy satisfies the single source of truth assumption.
 
@@
 
-In order to satisfy the single source of truth assumption,
-we introduce a new strategy, which we call the local majority strategy.
-In {\em local majority}, agents all begin with the same starting state,
-and apply individual learning to their concern to generate
+To satisfy the single source of truth assumption,
+we introduce a new strategy --- {\em local majority}.
+In local majority, agents all begin with the same starting state and apply individual learning to their concern to generate
 possible improvements to the solution.
@@
 We simulated 100 trials for rewiring values of 0.0, 0.167, 0.333, 0.5, 0.667, 0.833, and 1.0.
-For each trial we generated an NK model with N=250 and K=7 and ran each social learning strategy
+For each trial we generated an NK model with $N=250$ and $K=7$ and ran each social learning strategy
 (Table \ref{tab:strat}) for 300 iterations,
@@
 For the best-neighbor strategy, local outperforms global.
-For local conformity strategy performs notably worse than all other strategies.
-The local majority strategy is both more efficient and more performant than others,
+Local conformity performs notably worse than all others.
+Local majority is both more efficient and more performant than others,
 with its performance increasing with higher rewiring.
-These results imply that,
-at least in a simple model of collaboration,
+This implies that,
+at least in a simple collaboration model,
 the performance and efficiency can be simultaneously increased.
@@
 analysis of large real-world systems is an important next step.
-Our empirical analysis of WikiProjects contributes several findings towards a better
+Our empirical analysis contributes several findings towards a better
 understanding of large, decentralized, real-world collaboration.
@@
 degree distribution may be just as, or more, important.
-The association of low-degree with both high performance and high efficiency is compelling,
+The association of low-degree with both high performance and efficiency is compelling,
 as it sidesteps the usual trade-off between performance and efficiency.
-In low-degree networks, agents have more repeated interactions with smaller groups of collaborators,
-possibly suggesting that small team sizes could be beneficial for large collaborations.
+In low-degree networks, agents have more repeated interactions with smaller groups of collaborators, suggesting that small team sizes could be beneficial for large collaborations.
 Similarly, the observation that performance is higher in projects with less structural inequality suggests that,
-if the challenges of egalitarian organizing can be overcome,
+if the challenges of egalitarian organizing are overcome,
 decentralized collaborations may produce better outcomes than those with centralized, top-down structures.
 
-Our agent-based models offer a few additional insights.
+Our agent-based models offer a several insights.
 We observe degree-dependent performance and efficiency dependence for both local conformity
@@
 Our local majority strategy,
-designed to satisfy several properties present in real-world collaborations,
+designed to satisfy several properties in real-world collaborations,
 shows the strongest effects on performance and efficiency as network degree changes.
@@
 is incompatible with actual behavior on Wikipedia or
-that other factors (possibly including degree skewness)
-outweigh the contribution of mean degree.
+that other factors outweigh the contribution of mean degree.
 
@@
 A better understanding of the relationship between network structure and collaboration
-outcomes has many practical applications.
-Online communities using recommender systems to improve collaboration
-could make recommendations guided by desirable network properties.
+outcomes has practical applications.
+Online communities using recommender systems could make recommendations guided by desirable network properties.
 Similarly, network structure could be used to identify under-performing
@@
 The relationship between network structure and learning strategy suggests that
-behavioral norms interact with network structure.
-This knowledge could be used by interventions to ensure that behavioral norms
-and network structure are aligned for best performance and efficiency.
+behavioral norms interact with network structure, which could be used to ensure that behavioral norms
+and network structure are appropriately aligned.
 
@@
 In this paper, we have described the relationship between the structural properties of WikiProject
-coeditor networks and the performance and efficiency of those networks.
-As in other studies, we see a trade-off between performance and efficiency,
-but not an absolute trade-off.
-Some properties, such as low degree, are associated with both higher performance and higher efficiency.
+coeditor networks and their performance and efficiency.
+As in other studies, we see a trade-off between performance and efficiency. However, 
+some properties, such as low degree, are associated with both higher performance and efficiency.
 We also find that the correlations between path length and performance are consistent with a conformity-based
 social learning strategy, but not a greedy best-neighbor strategy.
-We also observe improved performance in more decentralized project, as has been seen in small-scale lab experiments.
+We observe improved performance in more decentralized projects, as has been seen in small-scale lab experiments.
 While the performance and efficiency of most previously-studied social learning strategies depend more on path length than
@@
 and that the direction of that dependence depends on the specific strategy being used.
-While additional work is needed to determine causal relationships and how generalizable our results are,
+While additional work is needed to determine causal relationships and the generalizability of our results,
 we have shown evidence that several phenomena predicted by numerical and small-scale lab experiments are present in a large,
-real-world network.
-And, we have identified new behaviors not explained by existing models, suggesting the need for alternate models.
-Our results suggest that the success of large-scale collaborations may be aided by greater decentralization,
+real-world network. Our results suggest that the success of large-scale collaborations may be aided by greater decentralization,
 consensus or conformity-based decision-making, and more tightly-knit collaborations between smaller teams.
@@
 Thanks to
-Ceren Budak, Scott E. Page, Yan Chen, Tanya Rosenblat, anonymous reviewers,
+Ceren Budak, Scott E. Page, Yan Chen, Tanya Rosenblat,
 and the attendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
@@
 and to Danielle Livneh and Karthik Ramanathan for help collecting the data.
-This research was funded by the University of Michigan School of Information.
+This research was partly supported by the National Science Foundation under Grant No. IIS-1617820.

### 2018-04-04 paper-content.tex
Trimming and moving table captions.

@@
 {The problem with Wikipedia is that it only works in practice. In theory, it's a total disaster.}
-{Gareth Owen \cite{elsharbaty_editing_2016} }
+{---Gareth Owen \cite{elsharbaty_editing_2016} }
 
@@
 \caption{
-From Wikipedia talk page
-for {\em Knitting}.
-Both {\em WikiProject Technology} and
-{\em WikiProject Textile Arts}
-have assessed the article as B-class quality.
+From Wikipedia {\em Knitting} talk page.
+Two WikiProjects have assessed the article as B-class quality.
 \label{fig:knitting}
@@
 there are many ways to gauge their success.
-Two possibilities are
-1. how quickly they find a solution,
-which we call {\em efficiency}, and
-2. how good their solution is,
-which we call {\em performance}.
+One possibility is {\em efficiency}:
+how quickly they find a solution.
+Another is {\em performance}:
+how good their solution is.
 Evidence from numerical simulations
@@
 and higher performance has obvious practical importance.
-In this paper, we focus specifically on how network structure
+In this paper, we focus on how network structure
 relates to efficiency and performance within WikiProjects.
@@
 \small
+\centering
+\begin{tabular}{lll}
+Strategy & Performance & Efficiency\\
+\hline
+Best+I  & 0.722 $\pm$ 0.001 & 0.0221 $\pm$ 0.0003 \\
+Conf+I  & 0.721 $\pm$ 0.001 & 0.0174 $\pm$ 0.0002 \\
+Best+LI & 0.726 $\pm$ 0.001 & 0.0131 $\pm$ 0.0002 \\
+Conf+LI & 0.586 $\pm$ 0.001 & 0.030 $\pm$ 0.001 \\
+LMaj+LI & 0.729 $\pm$ 0.001 & 0.046 $\pm$ 0.002 \\
+\hline
+\end{tabular}
 \caption{
@@
 }
-\centering
-\bigskip
-\begin{tabular}{lll}
-Strategy & Performance & Efficiency\\
-\hline
-Best+I  & 0.722 $\pm$ 0.001 & 0.0221 $\pm$ 0.0003 \\
-Conf+I  & 0.721 $\pm$ 0.001 & 0.0174 $\pm$ 0.0002 \\
-Best+LI & 0.726 $\pm$ 0.001 & 0.0131 $\pm$ 0.0002 \\
-Conf+LI & 0.586 $\pm$ 0.001 & 0.030 $\pm$ 0.001 \\
-LMaj+LI & 0.729 $\pm$ 0.001 & 0.046 $\pm$ 0.002 \\
-\hline
-\end{tabular}
 \end{table}
@@
 \small
-\caption{
-Degree regression coefficients for simulations.
-\label{tab:sim-perf}
-}
 \centering
-\bigskip
 \begin{tabular}{lll}
@@
 \end{tablenotes}
+\caption{
+Degree regression coefficients for simulations.
+\label{tab:sim-perf}
+}
 \end{table}

### 2018-04-06 paper-content.tex
Cleans up formatting, grammar, clarity.

@@
 We analyze the relationship between the structural properties of WikiProject coeditor networks
-and the performance and efficiency of those networks.
+and the performance and efficiency of those projects.
 We confirm the existence of an overall performance-efficiency trade-off,
@@
 We find that Wikipedia exhibits an overall trade-off between performance and efficiency.
-However, some WikiProjects are higher in both efficiency and performance
-than others,
+However, some WikiProjects surpass others in both efficiency and performance,
 suggesting the existence of factors that correlate positively with both.
@@
 which editors have edited at least one article in common?
-These relationships represent possible flows of information.
+These relationships represent the possible flow of information.
 We focus specifically on mean degree, degree skewness, and path length.
@@
 Networks with shorter path lengths allow information to travel more quickly
-at the possible expense of less localized diversity
+at the possible expense of less local diversity
 \cite{mason_propagation_2008,barkoczi_social_2016}.
@@
 2. interact with others who share their concerns,
-and 3. reconcile their preferences into a single state.
+and 3. integrate their preferences into a single state.
 Our model is the first we are aware of to incorporate these assumptions,
-which are present across many real-world collaborations
+which are present across many real-world collaborations,
 including Wikipedia.
@@
 \item Despite an overall performance/efficiency trade-off,
-WikiProjects having low-degree coeditor networks tend to have both higher performance and higher efficiency;
+WikiProjects with low-degree coeditor networks tend to have both higher performance and higher efficiency;
 \item Short paths are associated with higher performance, consistent with a conformity-based learning strategy;
@@
 collaboration.
-These findings might be informative for future interventions which
+These findings might be informative for future interventions that
 recommend tasks based on how they will
 influence network structure,
-or interventions which seek to encourage the behavioral norms most
-effective for existing network structure.
+or for interventions that seek to encourage behaviors
+complementary to existing network structure.
 
@@
 {\em social learning}.
-We expand the literature with a large-scale, empirical field study.
+We contribute to this literature with a large-scale, empirical field study.
 In much of the existing literature,
@@
 agents are represented by nodes on a network
-and can only interact with their neighbors.
+and can interact only with their neighbors.
 Social learning tasks can be divided into cases where agents have {\em generated signals}
@@
 while the speed of convergence depends on the {\em spectral gap}
-between the two largest eigenvalues of the network's adjacency matrix
+between the two largest eigenvalues of the network's interaction matrix
 \cite{degroot_reaching_1974,golub_naive_2010}.
@@
 inefficient ones \cite{barkoczi_social_2016}.
+Using an agent-based model, Hong and Page \shortcite{hong_groups_2004} found that
+diverse groups can outperform groups composed of the best individual
+problem-solvers.
 
@@
 The same studies found that while human subjects tend to perform well on
-some networks, they perform worst on self-organized
-networks.
+many networks, they perform worst on self-organized
+networks, possibly due to higher structural inequality
+(degree skewness).
 Similarly, some network topologies are able to reach faster decisions in the
@@
 existence of conditional altruism,
-but concluded that altruistic
-behavior only influences first-degree neighbors.
+but concluded that altruism
+influences only first-degree neighbors.
 
@@
 in collaborative work and decision-making.
-Using an agent-based model, Hong and Page \shortcite{hong_groups_2004} found that
-diverse groups can outperform groups composed of the best individual
-problem-solvers.
 In sociology, research has focused on the relationship between
@@
 holes'' between groups \cite{granovetter_strength_1973}.
-There is some evidence that groups with higher structural inequality
-(degree skewness)
-perform worse \cite{kearns_experiments_2012}.
 
@@
 a few key themes emerge.
-The efficiency and performance of collaborations are both important considerations
-and vary depending on both network structure and type of task
+Both the efficiency and the performance of a collaboration are important
+considerations and vary depending on both network structure and type of task
 \cite{kearns_experiments_2012}.
@@
 
-Many articles on Wikipedia belong to one or more WikiProject.
+Many articles on Wikipedia belong to one or more WikiProjects.
 WikiProjects are groups of thematically-related articles
 (e.g., articles related to Philosophy).
-Information about the an article's associated WikiProjects
+Information about an article's associated WikiProjects
 can be viewed on that
@@
 Each WikiProject has its own page and talk page,
-containing information about community norms within the project
+containing information about conventions within the project
 as well as discussions about individual articles.
@@
 In addition to the above assessment classes, articles on Wikipedia can be tagged as
-"good article" (GA) or "featured article" (FA) quality.
+``good article'' (GA) or ``featured article'' (FA) quality.
 FA and GA determinations are made using a Wikipedia-wide consensus,
-in parallel to any WikiProject-based evaluations.
+independently of WikiProject-based evaluations.
 FA articles are ``the best articles Wikipedia has to offer''
@@
 {\em WikiProject Video Games}.
-This example also illustrates a quirk of Wikipedia norms:
+This example also illustrates a quirk of conventions on Wikipedia:
 very often, articles pass to GA or FA directly from B, skipping A.
@@
 We measure work by the number of revisions made.
-Quality assessments are made through consensus of the project participants themselves,
-so different projects can have different standards and practices for assessing article quality.
-So the efficiency is not a measure of how quickly some objective measure of quality improves,
+Quality assessments are made through consensus of the project participants themselves.
+Different projects can have different standards and practices for assessing article quality,
+so the efficiency is not a measure of how quickly some objective measure of quality improves,
 but rather of how quickly the project participants can reach consensus on the improvements that
@@
 \item{Strictly decreasing in the number of revisions (with transition count fixed);}
-\item{Independent of WikiProject size: not affected by adding an article with the same efficiency.}
+\item{Independent of WikiProject size: not affected by adding an article having the same efficiency.}
 \end{itemize}
@@
 from below grade $G$ to grade $G$ (or higher).
-Let $r(t)$ be the number of article revisions since its previous grade transition,
-and let $g(t)$ be the number of grade levels crossed by transition $t$.
+Given a transition $t$,
+let $r(t)$ be the number of revisions to the article
+since its previous grade transition,
+and let $g(t)$ be the number of grade levels crossed bt $t$.
 We quantify the efficiency $E(W,G)$ as the inverse of the mean number of revisions
@@
 \eeq
-Where the $g(t)$ term accounts for assessments raising article quality by several
-grades,
+where the $g(t)$ term accounts for assessments that raise article quality by
+several grades by
 dividing the revisions evenly between all grade levels achieved.
@@
 For performance, we wish to quantify how good articles tend to be when they reach a stable state.
-Measuring performance is difficult for several reasons:
+Measuring performance is difficult for two reasons:
 there is no objective measure of article quality available,
@@
 status.
-In other words, the good and featured statuses are more objective than per-project assessments.
+In other words, the good and featured statuses are less subjective than per-project assessments.
 
@@
 We would like to determine how the social network structure of
-Wikipedia--the pattern of who interacts with whom--relates to
+Wikipedia---the pattern of who interacts with whom---relates to
 efficiency and performance.
@@
 
-The {\em coeditor network} of a WikiProject consists of nodes representing editors,
-and edges connecting any editors who have edited the same article.
+The {\em coeditor network} of a WikiProject consists of nodes representing editors
+and edges connecting pairs of editors who have edited the same article.
 The edges are directed, with the direction representing
@@
 the {\em mean degree} of the network.
-In our context, the mean degree represents how many others a given editor has collaborated with.
+In our context, the mean degree represents, on average,
+how many other editors each editor has collaborated with.
 We also consider the {\em skewness} of the in-degree and out-degree distributions.
@@
 
-Our final network measure quantifies the connectivity of a project's coeditor network using
-min-cut size.
-The minimum $st$-cut between nodes $s$ and $t$ is the set of edges that must be removed in order that
-no path exists from $s$ to $t$.
+Our final network measure quantifies the connectivity of a project's coeditor
+network using min-cut size.
+The minimum $st$-cut between nodes $s$ and $t$ is the set of edges that must beremoved
+for no path exists from $s$ to $t$.
 The minimum cut (min-cut) of a graph is the smallest minimum $st$-cut over all node pairs $st$. 
@@
 The mean path and min-cut are computationally intensive,
-requiring distance and minimum $st$-cut calculations for each all node pairs.
-For larger projects, these calculations are impractical and we thus employed sampling to determine mean path length and mean
-min-cut.
+requiring distance and minimum $st$-cut calculations for all node pairs.
+For larger projects, these calculations are impractical and we thus employed
+sampling to determine mean path length and mean min-cut.
 For mean path length, source nodes were sampled, and path length was calculated to all destination nodes
@@
 so we exclude min-cut from regression models to prevent collinearity.
-The high correlation between mean degree and min-cut implies that in most cases
-the minimum $st$-cut is simply the either set of edges from $s$ or the set of edges to $t$.
-The rarity of non-trivial min-cuts suggests that WikiProject coeditor networks have very few central
+The high correlation between mean degree and min-cut implies that,
+in most cases,
+the minimum $st$-cut is simply the set of edges from $s$
+or the set of edges to $t$.
+The rarity of non-trivial min-cuts suggests that WikiProject coeditor
+networks have very few central
 bottlenecks and are thus highly decentralized.
@@
 \item[C-efficiency]
-(Performance only.)
+(performance only).
 Quantifies how quickly a WikiProject improves articles.
@@
 so we include only one.
-\item[Connected fraction]
+\item[Connected fraction.]
 Fraction of coeditor pairs connected by a path.
-\item[Talk fraction] Fraction of total revisions made to talk pages.
-\item[Mean similarity] Mean Jaccard similarity (by article) with other WikiProjects; a measure of topical complexity.
-\item[Mean editors/article] Mean number of editors collaborating on each article in a WikiProject.
-\item[Article count] Total number of articles in the WikiProject.
-\item[Editor count] Total number of editors working on articles within a WikiProject.
-\item[Revision count] Total number of revisions to articles in a WikiProject.
-\item[First assessment] Timestamp of first assessment; a measure of how long a WikiProject has been active.
-\item[Mean article age] Mean age of articles within a WikiProject.
+\item[Talk fraction.] Fraction of total revisions made to talk pages.
+\item[Mean similarity.] Mean Jaccard similarity (by article) with other WikiProjects; a measure of topical complexity.
+\item[Mean editors/article.] Mean number of editors collaborating on each article in a WikiProject.
+\item[Article count.] Total number of articles in the WikiProject.
+\item[Editor count.] Total number of editors working on articles within a WikiProject.
+\item[Revision count.] Total number of revisions to articles in a WikiProject.
+\item[First assessment.] Timestamp of first assessment; a measure of how long a WikiProject has been active.
+\item[Mean article age.] Mean age of articles within a WikiProject.
 \end{description}
@@
 so we only include out-degree skewness
-(results are similar with in-degree skewness).
+(results are similar for in-degree skewness).
 Heavy-tailed variables are log-transformed.
@@
 differently in its dependence on degree skewness and connectivity.
-The different behavior of A-efficiency is likely explained by the observation that the A-Class quality is
-infrequently used in practice, meaning that the quality level is usually achieved when an article is rated
-as a good or featured article, which involves a different consensus process than lower ratings.
+The different behavior of A-efficiency is likely explained by the
+observation that the A-Class quality is infrequently used in practice.
+The A-Class quality level is usually passed when an article reaches
+good or featured article status,
+which follow deifferent a consensus process from other ratings.
 
@@
 \begin{description}
-\item[Limited concern] Agents are concerned only with a subset of the entire
+\item[Limited concern.] Agents are concerned only with a subset of the entire
 state when making decisions and determining preferences.
 (On Wikipedia, editors typically interact with a small subset of the articles.)
-\item[Concern-based network] Agents interact with other agents who share a
+\item[Concern-based network.] Agents interact with other agents who share a
 common concern over some subset of the state.
 (On Wikipedia, editors interact with others who share interests in the same articles.)
-\item[Unknown objective] Agents rank states in order of preference,
+\item[Unknown objective.] Agents rank states in order of preference,
 but do not have access to the objective function.
 (On Wikipedia, there is no ground truth measure of quality.)
-\item[Single source of truth] At any given time, the system is in a single state
+\item[Single source of truth.] At any given time, the system is in a single state
 and agent preferences are based on local modifications to that state.
@@
 Learning strategies determine how agents update their preferences based on
-available information.
-Agents can engage in individual learning \cite{barkoczi_social_2016}
+available information \cite{barkoczi_social_2016}.
+Agents can engage in individual learning
 by applying a hill-climbing algorithm to their current solution.
@@
 To satisfy the single source of truth assumption,
-we introduce a new strategy --- {\em local majority}.
+we introduce a new strategy: {\em local majority}.
 In local majority, agents all begin with the same starting state and apply individual learning to their concern to generate
@@
 individually.
-Every agent concerned with a bit votes for its state based on their preferred
+Every agent concerned with a locus votes for its state based on their preferred
 new solution and the majority state is chosen.
-The result of this process is that all agents agree on a single improved state,
+The result of this process is that all agents integrate their solutions into
+a single state,
 which forms the basis for the next iteration.
@@
 We simulated 100 trials for rewiring values of 0.0, 0.167, 0.333, 0.5, 0.667, 0.833, and 1.0.
-For each trial we generated an NK model with $N=250$ and $K=7$ and ran each social learning strategy
-(Table \ref{tab:strat}) for 300 iterations,
-as well as a network based on that NK model and rewired.
+For each trial we generated an NK model with $N=250$ and $K=7$,
+generated a concern-based network, and ran each social learning strategy
+(Table \ref{tab:strat}) for 300 iterations.
 For conformity and best-neighbor strategy, we used a sample size of 3, following
@@
 and mean path length of 1.766 with 0.0027 standard deviation.
-The coefficient of variation of degree is approximately 10\%,
+The coefficient of variation for degree is approximately 10\%,
 while only 1\% for mean path length, confirming that the rewiring process has a stronger influence
@@
 \caption{
-Efficiency and Performance of social learning strategies vs. network degree.
+Efficiency and Performance of social learning strategies vs. mean network degree.
 Each point represents a single trial of 300 iterations.
@@
 different learning strategies and rewiring values.
-Each curve represents an average over 100 trials, each with 250 agent solutions.
+Each curve represents an average over 100 trials, each with 250 agents.
 The mean performance and efficiency are reported in Table \ref{tab:sim-eff-perf}.
@@
 at least in a simple collaboration model,
-the performance and efficiency can be simultaneously increased.
+performance and efficiency can be simultaneously increased.
 Furthermore, performance and efficiency are potentially affected by both the choice of
@@
 \cite{kearns_experiments_2012}.
-By using real-world networks, we were also able to analyze network properties independently,
-allowing us to show that while most existing work has focused on the importance of path length,
-degree distribution may be just as, or more, important.
-The association of low-degree with both high performance and efficiency is compelling,
+By using real-world networks, we were also able to analyze network properties independently.
+While most existing work has focused on the importance of path length,
+our findings suggest degree distribution may be just as, or more, important.
+The association of low degree with both high performance and high efficiency is compelling,
 as it sidesteps the usual trade-off between performance and efficiency.
@@
 Our agent-based models offer a several insights.
-We observe degree-dependent performance and efficiency dependence for both local conformity
-and local majority strategies.
+We observe degree-dependent performance and efficiency
+for both local conformity and local majority strategies.
 However, these two strategies have opposite degree dependence,
@@
 Our local majority strategy,
-designed to satisfy several properties in real-world collaborations,
+designed to satisfy several properties found in real-world collaborations,
 shows the strongest effects on performance and efficiency as network degree changes.
@@
 The relationship between network structure and learning strategy suggests that
-behavioral norms interact with network structure, which could be used to ensure that behavioral norms
-and network structure are appropriately aligned.
+behaviors interact with network structure,
+which could be used to encourage behaviors complementary to existing network
+structure.
 
@@
 In this paper, we have described the relationship between the structural properties of WikiProject
-coeditor networks and their performance and efficiency.
+coeditor networks, their performance, and their efficiency.
 As in other studies, we see a trade-off between performance and efficiency. However, 
@@
 the performance and efficiency of a collaboration can exhibit degree dependence,
-and that the direction of that dependence depends on the specific strategy being used.
-While additional work is needed to determine causal relationships and the generalizability of our results,
-we have shown evidence that several phenomena predicted by numerical and small-scale lab experiments are present in a large,
-real-world network. Our results suggest that the success of large-scale collaborations may be aided by greater decentralization,
-consensus or conformity-based decision-making, and more tightly-knit collaborations between smaller teams.
+and that the direction of that dependence varies with the specific strategy being used.
+While additional work is needed to determine causal relationships
+and the generalizability of our results,
+we have shown evidence that several phenomena predicted by numerical
+and small-scale lab experiments are present in a large,
+real-world collaboration.
+Our results suggest that the success of large-scale collaborations may be aided
+by greater decentralization,
+consensus or conformity-based decision-making,
+and more tightly-knit collaborations between smaller teams.
 
@@
 Ceren Budak, Scott E. Page, Yan Chen, Tanya Rosenblat,
-and the attendees of the May 25, 2017 MIT Center for Civic Media lab meeting and
-the Berkman-Klein Center Cooperation Working Group for helpful feedback;
+anonymous reviewers,
+and the attendees of the May 25, 2017 MIT Center for Civic Media lab meeting
+and the Berkman-Klein Center Cooperation Working Group for helpful feedback;
 and to Danielle Livneh and Karthik Ramanathan for help collecting the data.

### 2018-04-10 icwsm-cameraready/wp-eff-perf.tex
Add ICWSM camera-ready version.

--- 2018-04-06 paper-content.tex
@@
+\def\year{2018}\relax
+%File: formatting-instruction.tex
+\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
+\usepackage{aaai18}  %Required
+\usepackage{times}  %Required
+\usepackage{helvet}  %Required
+\usepackage{courier}  %Required
+\usepackage{url}  %Required
+\usepackage{graphicx}  %Required
+\frenchspacing  %Required
+\setlength{\pdfpagewidth}{8.5in}  %Required
+\setlength{\pdfpageheight}{11in}  %Required
+%PDF Info Is Required:
+  \pdfinfo{
+/Title (Network Structure, Efficiency, and Performance in WikiProjects)
+/Author Edward L. Platt and Daniel M. Romero}
+\setcounter{secnumdepth}{0}
+
+% Document-specific packages
+\usepackage{epigraph}
+\usepackage[normal]{threeparttable}
+\usepackage{graphicx}
+\usepackage{bbding}
+
+% Document-specific definitions
+\newcommand{\beq}{\begin{eqnarray}}
+\newcommand{\eeq}{\end{eqnarray}}
+\newcommand{\+}{\phantom{-}}
+
+ \begin{document}
+% The file aaai.sty is the style file for AAAI Press 
+% proceedings, working notes, and technical reports.
+%
+\title{Network Structure, Efficiency, and Performance in WikiProjects}
+%\author{Anonymized \\
+%for\\
+%blind review
+%\And
+%Anonymized \\
+%for\\
+%blind review
+\author{Edward L. Platt \\
+University of Michigan\\
+Ann Arbor, MI\\
+elplatt@umich.edu
+\And
+Daniel M. Romero\\
+University of Michigan\\
+Ann Arbor, MI\\
+drom@umich.edu
+}
+\maketitle
+
 \begin{abstract}
@@
 Our analysis combines multiple data
-sets\footnote{Data and code at https://elplatt.com/a/WikiProject-Eff-Perf}
-from the English-language Wikipedia.
+sets from the English-language Wikipedia \cite{platt_english_2018}.
 For information about edit history, we used a publicly-available data set containing
@@
 coeditor networks, their performance, and their efficiency.
-As in other studies, we see a trade-off between performance and efficiency. However, 
-some properties, such as low degree, are associated with both higher performance and efficiency.
+As in other studies, we see a trade-off between performance and efficiency.
+However, 
+some properties, such as low degree, are associated with
+both higher performance and higher efficiency.
 We also find that the correlations between path length and performance are consistent with a conformity-based
 social learning strategy, but not a greedy best-neighbor strategy.
-We observe improved performance in more decentralized projects, as has been seen in small-scale lab experiments.
-While the performance and efficiency of most previously-studied social learning strategies depend more on path length than
-degree,
-we have proposed a novel local majority learning strategy that is more realistic, more efficient, and higher performance than
-existing strategies.
-We observe that in both the local majority strategy and a localized version of
-the conformity strategy,
-the performance and efficiency of a collaboration can exhibit degree dependence,
-and that the direction of that dependence varies with the specific strategy being used.
+We observe improved performance in more decentralized projects,
+as has been seen in small-scale lab experiments.
+We have also proposed a novel local majority learning strategy that is more realistic,
+more efficient, and higher performance than existing strategies.
+While most previous social learning simulations focus on path length,
+we observe degree-dependent performance and efficiency
+in both the local majority strategy
+and a localized version of the conformity strategy.
+We find that the direction of that dependence varies with the
+specific strategy being used.
 While additional work is needed to determine causal relationships
@@
 This research was partly supported by the National Science Foundation under Grant No. IIS-1617820.
+
+\bibliographystyle{aaai}
+\bibliography{wp-eff-perf}
+\end{document}

### 2018-04-10 preprint/wp-eff-perf.tex
Add preprint.

--- 2018-04-10 icwsm-cameraready/wp-eff-perf.tex
@@
 \def\year{2018}\relax
-%File: formatting-instruction.tex
-\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
-\usepackage{aaai18}  %Required
-\usepackage{times}  %Required
-\usepackage{helvet}  %Required
-\usepackage{courier}  %Required
-\usepackage{url}  %Required
-\usepackage{graphicx}  %Required
-\frenchspacing  %Required
-\setlength{\pdfpagewidth}{8.5in}  %Required
-\setlength{\pdfpageheight}{11in}  %Required
-%PDF Info Is Required:
+\documentclass[letterpaper,twocolumn,10pt]{article}
+\usepackage{times}
+\usepackage{helvet}
+\usepackage{courier}
+\usepackage{url}
+\usepackage{graphicx}
+\frenchspacing
+\setlength{\pdfpagewidth}{8.5in}
+\setlength{\pdfpageheight}{11in}
 \pdfinfo{
 /Title (Network Structure, Efficiency, and Performance in WikiProjects)
-/Author Edward L. Platt and Daniel M. Romero}
+/Author (Edward L. Platt, Daniel M. Romero)}
 \setcounter{secnumdepth}{0}
@@
 \usepackage{bbding}
+\usepackage{natbib}
+\usepackage[letterpaper,left=0.75in,right=0.75in,top=0.75in,bottom=1.25in]{geometry}
+\usepackage{titlesec}
 
@@
 
+\setlength{\columnsep}{0.375in}
+\titleformat*{\section}{\large\bfseries}
+\titleformat*{\subsection}{\normalsize\bfseries}
+\titleformat*{\subsubsection}{\normalsize\bfseries}
+\titleformat*{\paragraph}{\normalsize\bfseries}
+\titleformat*{\subparagraph}{\normalsize\bfseries}
+\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
+\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
+
+\linespread{1.0}
+
 \begin{document}
-% The file aaai.sty is the style file for AAAI Press 
-% proceedings, working notes, and technical reports.
-%
 \title{Network Structure, Efficiency, and Performance in WikiProjects}
-%\author{Anonymized \\
-%for\\
-%blind review
-%\And
-%Anonymized \\
-%for\\
-%blind review
-\author{Edward L. Platt \\
+\author{
+Edward L. Platt \\
 University of Michigan\\
-Ann Arbor, MI\\
 elplatt@umich.edu
-\And
+\and
 Daniel M. Romero\\
 University of Michigan\\
-Ann Arbor, MI\\
 drom@umich.edu
 }
+\date{}
 \maketitle
@@
 \begin{abstract}
+\small
 The internet has enabled collaborations at a scale never before possible,
@@
 including Wikipedia.
+\pagebreak
 
@@
 \begin{itemize}
+\setlength\itemsep{0pt}
 \item Despite an overall performance/efficiency trade-off,
@@
 inefficient ones \cite{barkoczi_social_2016}.
-Using an agent-based model, Hong and Page \shortcite{hong_groups_2004} found that
+Using an agent-based model, Hong and Page \citeyear{hong_groups_2004} found that
 diverse groups can outperform groups composed of the best individual
@@
 \cite{kearns_experimental_2006}.
-Based on lab experiments, Fowler and Christakis \shortcite{fowler_cooperative_2010}
+Based on lab experiments, Fowler and Christakis \citeyear{fowler_cooperative_2010}
 suggest that individual decisions towards altruism are conditional on their
 neighbor's behavior and ``contagious'' up to three degrees away.
-Later experiments by Suri and Watts \shortcite{suri_cooperation_2011} confirmed the
+Later experiments by Suri and Watts \citeyear{suri_cooperation_2011} confirmed the
 existence of conditional altruism,
@@
 For Wikipedia specifically,
-Robert and Romero \shortcite{robert_crowd_2015} found that
+Robert and Romero \citeyear{robert_crowd_2015} found that
 larger group sizes yield higher article ratings
 when the groups are diverse and experienced. Kittur and Kraut found that different types of coordination have a complex
-effect on the quality of Wikipedia articles \shortcite{kittur_harnessing_2008}.
+effect on the quality of Wikipedia articles \citeyear{kittur_harnessing_2008}.
 Both explicit and implicit coordination result in higher quality articles,
@@
 article.
-Shaw and Hill \shortcite{shaw_laboratories_2014}
+Shaw and Hill \citeyear{shaw_laboratories_2014}
 found that behavior in online wiki communities is consistent
@@
 the good of the group \cite{michels_political_1999}.
-Similarly, Halfaker et al. \shortcite{halfaker_rise_2013} attributed decreasing
+Similarly, Halfaker et al. \citeyear{halfaker_rise_2013} attributed decreasing
 participation on Wikipedia to poor retention of new users.
 Looking specifically at Wikipedia policies determined by editor consensus,
-Keegan and Fiesler \shortcite{keegan_evolution_2017} found a trend
+Keegan and Fiesler \citeyear{keegan_evolution_2017} found a trend
 from flexible rule-making towards less flexible maintenance and deliberation.
 Using content analysis,
-Morgan et al. \shortcite{morgan_project_2013} found WikiProjects to be
+Morgan et al. \citeyear{morgan_project_2013} found WikiProjects to be
 more loosely organized than traditional teams.
@@
 
-\begin{figure}[h!]
+\begin{figure}[t!]
 \begin{center}
@@
 \begin{itemize}
+\setlength\itemsep{0pt}
 \item{Strictly increasing in the number of articles reaching grade $G$ (with revision count fixed);}
@@
 
-\subsection{Empirical Results}
-
-We find that both efficiency and performance are highly right-skewed,
-with a small number of projects having values much higher than the average.
-After log-transforming the values, both the efficiency and the performance have
-a unimodal distribution with low skew (see Figure \ref{fig:eff-perf-hist}).
-Our findings confirm the trade-off between performance and efficiency
-observed in many other settings (Figure \ref{fig:eff-perf}).
-However, when looking at specific projects, some are higher in both performance
-and efficiency,
-suggesting the existence of factors which correlate positively with both.
-
-We also find that mean min-cut is highly correlated with degree ($r=0.980$, $p<0.001$),
-so we exclude min-cut from regression models to prevent collinearity.
-The high correlation between mean degree and min-cut implies that,
-in most cases,
-the minimum $st$-cut is simply the set of edges from $s$
-or the set of edges to $t$.
-The rarity of non-trivial min-cuts suggests that WikiProject coeditor
-networks have very few central
-bottlenecks and are thus highly decentralized.
-
 \begin{figure}[t!]
@@
 
-\begin{figure}[h!]
+\subsection{Empirical Results}
+
+We find that both efficiency and performance are highly right-skewed,
+with a small number of projects having values much higher than the average.
+After log-transforming the values, both the efficiency and the performance have
+a unimodal distribution with low skew (see Figure \ref{fig:eff-perf-hist}).
+Our findings confirm the trade-off between performance and efficiency
+observed in many other settings (Figure \ref{fig:eff-perf}).
+However, when looking at specific projects, some are higher in both performance
+and efficiency,
+suggesting the existence of factors which correlate positively with both.
+
+We also find that mean min-cut is highly correlated with degree ($r=0.980$, $p<0.001$),
+so we exclude min-cut from regression models to prevent collinearity.
+The high correlation between mean degree and min-cut implies that,
+in most cases,
+the minimum $st$-cut is simply the set of edges from $s$
+or the set of edges to $t$.
+The rarity of non-trivial min-cuts suggests that WikiProject coeditor
+networks have very few central
+bottlenecks and are thus highly decentralized.
+
+\begin{figure}[t!]
 \centering
@@
 \begin{description}
+\setlength\itemsep{0pt}
 \item[C-efficiency]
@@
 \begin{description}
+\setlength\itemsep{0pt}
 \item[Limited concern.] Agents are concerned only with a subset of the entire
@@
 
-\bibliographystyle{aaai}
+\bibliographystyle{apalike}
 \bibliography{wp-eff-perf}
+
 \end{document}

### 2018-04-11 preprint/wp-eff-perf.tex
Change citation style.

@@
 inefficient ones \cite{barkoczi_social_2016}.
-Using an agent-based model, Hong and Page \citeyear{hong_groups_2004} found that
+Using an agent-based model, Hong and Page \cite{hong_groups_2004} found that
 diverse groups can outperform groups composed of the best individual
@@
 \cite{kearns_experimental_2006}.
-Based on lab experiments, Fowler and Christakis \citeyear{fowler_cooperative_2010}
+Based on lab experiments, Fowler and Christakis \cite{fowler_cooperative_2010}
 suggest that individual decisions towards altruism are conditional on their
 neighbor's behavior and ``contagious'' up to three degrees away.
-Later experiments by Suri and Watts \citeyear{suri_cooperation_2011} confirmed the
+Later experiments by Suri and Watts \cite{suri_cooperation_2011} confirmed the
 existence of conditional altruism,
@@
 For Wikipedia specifically,
-Robert and Romero \citeyear{robert_crowd_2015} found that
+Robert and Romero \cite{robert_crowd_2015} found that
 larger group sizes yield higher article ratings
 when the groups are diverse and experienced. Kittur and Kraut found that different types of coordination have a complex
-effect on the quality of Wikipedia articles \citeyear{kittur_harnessing_2008}.
+effect on the quality of Wikipedia articles \cite{kittur_harnessing_2008}.
 Both explicit and implicit coordination result in higher quality articles,
@@
 article.
-Shaw and Hill \citeyear{shaw_laboratories_2014}
+Shaw and Hill \cite{shaw_laboratories_2014}
 found that behavior in online wiki communities is consistent
@@
 the good of the group \cite{michels_political_1999}.
-Similarly, Halfaker et al. \citeyear{halfaker_rise_2013} attributed decreasing
+Similarly, Halfaker et al. \cite{halfaker_rise_2013} attributed decreasing
 participation on Wikipedia to poor retention of new users.
 Looking specifically at Wikipedia policies determined by editor consensus,
-Keegan and Fiesler \citeyear{keegan_evolution_2017} found a trend
+Keegan and Fiesler \cite{keegan_evolution_2017} found a trend
 from flexible rule-making towards less flexible maintenance and deliberation.
 Using content analysis,
-Morgan et al. \citeyear{morgan_project_2013} found WikiProjects to be
+Morgan et al. \cite{morgan_project_2013} found WikiProjects to be
 more loosely organized than traditional teams.
@@
 
-\bibliographystyle{apalike}
+\bibliographystyle{plain}
 \bibliography{wp-eff-perf}

### 2018-12-11 icwsm-2018/paper-content.tex
Move icwsm files into subfolder.

--- 2018-04-10 icwsm-cameraready/wp-eff-perf.tex
@@
-\def\year{2018}\relax
-%File: formatting-instruction.tex
-\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
-\usepackage{aaai18}  %Required
-\usepackage{times}  %Required
-\usepackage{helvet}  %Required
-\usepackage{courier}  %Required
-\usepackage{url}  %Required
-\usepackage{graphicx}  %Required
-\frenchspacing  %Required
-\setlength{\pdfpagewidth}{8.5in}  %Required
-\setlength{\pdfpageheight}{11in}  %Required
-%PDF Info Is Required:
-  \pdfinfo{
-/Title (Network Structure, Efficiency, and Performance in WikiProjects)
-/Author Edward L. Platt and Daniel M. Romero}
-\setcounter{secnumdepth}{0}
-
-% Document-specific packages
-\usepackage{epigraph}
-\usepackage[normal]{threeparttable}
-\usepackage{graphicx}
-\usepackage{bbding}
-
-% Document-specific definitions
-\newcommand{\beq}{\begin{eqnarray}}
-\newcommand{\eeq}{\end{eqnarray}}
-\newcommand{\+}{\phantom{-}}
-
- \begin{document}
-% The file aaai.sty is the style file for AAAI Press 
-% proceedings, working notes, and technical reports.
-%
-\title{Network Structure, Efficiency, and Performance in WikiProjects}
-%\author{Anonymized \\
-%for\\
-%blind review
-%\And
-%Anonymized \\
-%for\\
-%blind review
-\author{Edward L. Platt \\
-University of Michigan\\
-Ann Arbor, MI\\
-elplatt@umich.edu
-\And
-Daniel M. Romero\\
-University of Michigan\\
-Ann Arbor, MI\\
-drom@umich.edu
-}
-\maketitle
-
 \begin{abstract}
@@
 This research was partly supported by the National Science Foundation under Grant No. IIS-1617820.
-
-\bibliographystyle{aaai}
-\bibliography{wp-eff-perf}
-\end{document}

### 2021-12-01 netsci-2019/abstract.tex
Add NetSci2019.

% This is the template for submission of abstracts to NetSci 2017 in Indianapolis, IN.
% It is modified from NetSci 2016.
% The editor of the booklet reserves the right to modify your submission.

%% To process this file run LaTeX2e

%%********DO NOT EDIT****************
\documentclass[12pt]{article}
\usepackage{mathptmx}
\usepackage{graphicx}
\pagestyle{empty}

\setlength\topmargin{0pt}
\addtolength\topmargin{-\headheight}
\addtolength\topmargin{-\headsep}
\setlength\oddsidemargin{0pt}
\setlength\textwidth{\paperwidth}
\addtolength\textwidth{-2in}
\setlength\textheight{\paperheight}
\addtolength\textheight{-2in}
\usepackage{layout}

\renewcommand{\title}[1]{\noindent\textbf{#1}\bigskip\\}
\renewcommand{\author}[1]{\noindent #1\bigskip\\}
%%***********************************

\begin{document}

%**********USER DEFINED**************
%Enter title here
\title{Network Structure, Efficiency, and Performance in WikiProjects}
%Enter author(s) and address here
\author{Edward L. Platt$^1$ and Daniel M. Romero$^1$\bigskip\\
{\small
1. University of Michigan, Ann Arbor, MI, USA\\
}
}
%Enter abstract here
The internet has enabled collaborations at a scale never before possible,
but the best practices for organizing such large collaborations are still not clear.
Wikipedia is a visible and successful example of such a collaboration [1, 2] which might offer
insight into what makes large-scale, decentralized collaborations successful.
In this large-scale observational study,
we analyze the relationship between the structural properties of
2079 English-language WikiProject coeditor networks
and the success those projects.
We make a distinction between two types of success measures:
{\em performance} and {\em efficiency}.
We confirm the existence of an overall negative correlation between performance
and efficiency,
while observing that some projects are higher than others in both performance
and efficiency,
suggesting the existence factors correlating positively with both.
Namely, we find an association between low-degree coeditor networks
and both high performance and high efficiency.
We also confirm results seen in previous numerical and small-scale lab studies:
higher performance with less skewed node distributions [3],
and higher performance with shorter path lengths [4].
Our results suggest 
possible benefits to decentralized collaborations made of smaller,
more tightly-knit teams.
Our results also suggest the importance of distinguishing between efficiency and
performance when evaluating the success of collaborative outcomes.

\begin{figure}[!ht]
\begin{center}
\includegraphics[scale=0.75]{regression.pdf}
\caption{
Regression coefficients for WikiProject success and coeditor network
properties
}
\end{center}
\end{figure}

\noindent[1] Giles, J. (2005). Internet encyclopaedias go head to head. {\em Nature.com}.
\\
\noindent[2] Keegan, B., \& Fiesler, C. (2017).
The Evolution and Consequences of Peer Producing Wikipedia’s Rules. In {\em ICWSM}.
\\
\noindent[3] Kearns, M. (2012). Experiments in social computation.
{\em Communications of the ACM}, 55(10).
\\
\noindent[4] Mason, W. A., Jones, A., \& Goldstone, R. L. (2008). Propagation of innovations in networked groups.
{\em Journal of Experimental Psychology: General}, 137(3).

% Place the abstract of your talk/poster here, 250 Words maximum.
% Mathematical formulae may be set in LaTeX, but do NOT use the
% bibliography environment -- if you must have references, use an 
% enumerated list.
%
% Your abstract (plus one figure) should not exceed one page.
%
% Check carefully.

%************************************
\end{document}
